---
title: "Model Diagnostics prep - iEEG Sample"
output: html_document
date: "2024-02-02"
---

---
title: "Distributions of Permuted and True Scores"
output: html_document
date: "2024-01-03"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 5,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(JMbayes2)
library(caret)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "clean_behavioral_data.R"))
source(path(here(), "R", "create_distance_df.R"))
source(path(here(), "R", "joint_modeling_functions.R"))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)

```


# Permuted vs True Model Comparison

Compares the `standard_model` (`points_remaining` + `distance_to_ghost`) and the `permtued_model` where the timing information for each trial is preserved but the `points_remaining` and `distance_to_ghost` values are shuffled/shuffled. I look at the distriutions of the following performance metrics

 * AUC
 * ICI
 * E50
 * E90
 * Brier Score
 * Predicted vs Observed Correlations
 
 From the initial look, the `standard_model` is significantly outperforming the `permuted_model` in AUC, meaning that it is correctly ranking trials in terms of risk. However, the calibration metrics are all *worse* in the `standard_model` compared to the `permuted_model`, so the model is still pretty far off from correctly predicting the probability of turnaround at any moment. I think the reason the measures are better in the `permuted_model` is that it just uses the average time of turnaround, which is maybe less dramatically off in terms of specific probabilities, but can't differentiate the trials very well. 
 
 If I look at the calibration plots for subjects 14 and 15, I think you can see what is happening. For 14, the calibration metrics are better in the `standard_model` and the red line follows the dotted line pretty well. However, in 15, in the `standard_model` the red line is very off at the edges. However, the `permuted_model` has a red line that is defined on only a short range of the x-axis, so it is not as off, even though I think it is a worse model. 


```{r load-data, results='asis', echo=FALSE}

game_data_distance <-  read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))



```


```{r concat-perm-model-diagnostics, results='asis', echo=FALSE}

perm_sub_list <- c()
auc_perm_list <- c()
ici_perm_list <- c()
e50_perm_list <- c()
e90_perm_list <- c()
brier_perm_list <- c()
core_perm_list <- c()
dic_perm_list <- c()
rhat_dist_perm_list <- c()
rhat_points_perm_list <- c()
p_dist_perm_list <- c()
p_points_perm_list <- c()
beta_dist_perm_list <- c()
beta_points_perm_list <- c()

for(current_subject in unique(game_data_distance$subject)){
    permuted <- TRUE
    file_name <- paste0(current_subject, "_", as.character(permuted))
    
    try({
    
      ## load model ##
      jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))
      
      ## get subject list ##
      perm_sub_list <- c(perm_sub_list, current_subject)
      
      ## fit metrics ##
      dic_perm_list <- c(dic_perm_list, jm_fit$fit_stats$marginal$DIC)
      rhat_dist_perm_list <- c(rhat_dist_perm_list, summary(jm_fit)$Survival[1, 6])   
      rhat_points_perm_list <- c(rhat_points_perm_list, summary(jm_fit)$Survival[2, 6])   
      p_dist_perm_list <- c(p_dist_perm_list, summary(jm_fit)$Survival[1, 5])   
      p_points_perm_list <- c(p_points_perm_list, summary(jm_fit)$Survival[2, 5])   
      beta_dist_perm_list <- c(beta_dist_perm_list, summary(jm_fit)$Survival[1, 1])   
      beta_points_perm_list <- c(beta_points_perm_list, summary(jm_fit)$Survival[2, 1])  
      
      ## Prep DF for Joint Model Fitting and select predictor variables ##
      joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted)
      
      ## Create Test/Train ##
      split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time) %>% distinct()
      split_index <- create_test_train(split_df, 123)
      train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
      test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)
      
      ## prediction time ##
      prediction_time <- median(split_df$turnaround_time)
      
      ## Prep dfs ##
      # longitudinal dfs
      train_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% train_trials)
      test_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% test_trials)
      
      # survival dfs
      cox_df <- create_survival_df(joint_dist_df)
      train_cox_df <- cox_df %>%
        filter(trial_numeric %in% train_trials)
      test_cox_df <- cox_df %>%
        filter(trial_numeric %in% test_trials)
      
      ### Calibration/Discrimintation ###
      ## AUC ##
      auc <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = prediction_time, idVar = 'trial_numeric')
      auc_perm_list <- c(auc_perm_list, auc$auc)
      
      ### Calibration ###
      toi <- prediction_time - .5
      cal_mets <- calibration_metrics(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, idVar = 'trial_numeric')
      ici_perm_list <- c(ici_perm_list, cal_mets[1])
      e50_perm_list <- c(e50_perm_list, cal_mets[2])
      e90_perm_list <- c(e90_perm_list, cal_mets[3])
      
      ### Brier Scores ###
      brier_scores <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, integrated = F)
      brier_perm_list <- c(brier_perm_list, brier_scores$Brier)
      
      ## Custom Checks ##
      test_three_trials <- test_long_data %>% 
        filter(trial_time < .5) %>%
        select(-turnaround_time, -EVENT)
      
      test_preds <- predict(jm_fit, 
                newdata = test_three_trials, process = "event", return_newdata = TRUE, 
                idVar = "trial_numeric", times = seq(.5, 2.5, .05))
      
      test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
      test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")
      
      test_preds_true <- test_preds_true %>%
        arrange(turntime_real) %>%
        mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))
      
      # correaltions between pred and real
      scatter_pred_df <- test_preds_true %>%
        mutate(near_50 = abs(pred_CIF - .5)) %>%
        group_by(trial_numeric) %>%
        mutate(closest_to_50 = min(near_50)) %>%
        filter(closest_to_50 == near_50) %>%
        mutate(turntime_pred = trial_time) %>%
        ungroup() %>%
        select(trial_numeric, turntime_real, turntime_pred) %>%
        distinct() 
      
      cor_score <- cor(scatter_pred_df$turntime_real, scatter_pred_df$turntime_pred)
      core_perm_list <- c(core_perm_list, cor_score)
      
    }, silent = TRUE)

}
```

```{r concat-true-model-diagnostics,, results='asis', echo=FALSE}

auc_true_list <- c()
ici_true_list <- c()
e50_true_list <- c()
e90_true_list <- c()
brier_true_list <- c()
core_true_list <- c()
dic_true_list <- c()
rhat_dist_true_list <- c()
rhat_points_true_list <- c()
p_dist_true_list <- c()
p_points_true_list <- c()
beta_dist_true_list <- c()
beta_points_true_list <- c()

for(current_subject in unique(game_data_distance$subject)){
    permuted <- FALSE
    file_name <- paste0(current_subject, "_", as.character(permuted))
    
    try({
    
      ## load model ##
      jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))
      
      ## fit metrics ##
      dic_true_list <- c(dic_true_list, jm_fit$fit_stats$marginal$DIC)
      rhat_dist_true_list <- c(rhat_dist_true_list, summary(jm_fit)$Survival[1, 6])   
      rhat_points_true_list <- c(rhat_points_true_list, summary(jm_fit)$Survival[2, 6])   
      p_dist_true_list <- c(p_dist_true_list, summary(jm_fit)$Survival[1, 5])   
      p_points_true_list <- c(p_points_true_list, summary(jm_fit)$Survival[2, 5])   
      beta_dist_true_list <- c(beta_dist_true_list, summary(jm_fit)$Survival[1, 1])   
      beta_points_true_list <- c(beta_points_true_list, summary(jm_fit)$Survival[2, 1])   
      
      ## Prep DF for Joint Model Fitting and select predictor variables ##
      joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted)
      
      ## Create Test/Train ##
      split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time) %>% distinct()
      split_index <- create_test_train(split_df, 123)
      train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
      test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)
      
      ## prediction time ##
      prediction_time <- median(split_df$turnaround_time)
      
      ## Prep dfs ##
      # longitudinal dfs
      train_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% train_trials)
      test_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% test_trials)
      
      # survival dfs
      cox_df <- create_survival_df(joint_dist_df)
      train_cox_df <- cox_df %>%
        filter(trial_numeric %in% train_trials)
      test_cox_df <- cox_df %>%
        filter(trial_numeric %in% test_trials)
      
      ### Calibration/Discrimintation ###
      ## AUC ##
      auc <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = prediction_time, idVar = 'trial_numeric')
      auc_true_list <- c(auc_true_list, auc$auc)
      
      ### Calibration ###
      toi <- prediction_time - .5
      cal_mets <- calibration_metrics(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, idVar = 'trial_numeric')
      ici_true_list <- c(ici_true_list, cal_mets[1])
      e50_true_list <- c(e50_true_list, cal_mets[2])
      e90_true_list <- c(e90_true_list, cal_mets[3])
      
      ### Brier Scores ###
      brier_scores <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, integrated = F)
      brier_true_list <- c(brier_true_list, brier_scores$Brier)
      
      ## Custom Checks ##
      test_three_trials <- test_long_data %>% 
        filter(trial_time < .5) %>%
        select(-turnaround_time, -EVENT)
      
      test_preds <- predict(jm_fit, 
                newdata = test_three_trials, process = "event", return_newdata = TRUE, 
                idVar = "trial_numeric", times = seq(.5, 2.5, .05))
      
      test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
      test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")
      
      test_preds_true <- test_preds_true %>%
        arrange(turntime_real) %>%
        mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))
      
      # correaltions between pred and real
      scatter_pred_df <- test_preds_true %>%
        mutate(near_50 = abs(pred_CIF - .5)) %>%
        group_by(trial_numeric) %>%
        mutate(closest_to_50 = min(near_50)) %>%
        filter(closest_to_50 == near_50) %>%
        mutate(turntime_pred = trial_time) %>%
        ungroup() %>%
        select(trial_numeric, turntime_real, turntime_pred) %>%
        distinct() 
      
      cor_score <- cor(scatter_pred_df$turntime_real, scatter_pred_df$turntime_pred)
      core_true_list <- c(core_true_list, cor_score)
    
    }, silent = TRUE)

}
```

```{r concat-reward-model-diagnostics,, results='asis', echo=FALSE}

reward_sub_list <- c()
auc_reward_list <- c()
ici_reward_list <- c()
e50_reward_list <- c()
e90_reward_list <- c()
brier_reward_list <- c()
core_reward_list <- c()
dic_reward_list <- c()
rhat_points_reward_list <- c()
p_points_reward_list <- c()
beta_points_reward_list <- c()

for(current_subject in unique(game_data_distance$subject)){
    permuted <- FALSE
    file_name <- paste0(current_subject, "_reward-only_", as.character(permuted))
    
    try({
    
      ## load model ##
      jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))
      
      ## get subject list ##
      reward_sub_list <- c(reward_sub_list, current_subject)
      
      ## fit metrics ##
      dic_reward_list <- c(dic_reward_list, jm_fit$fit_stats$marginal$DIC)
      rhat_points_reward_list <- c(rhat_points_reward_list, summary(jm_fit)$Survival[1, 6])   
      p_points_reward_list <- c(p_points_reward_list, summary(jm_fit)$Survival[1, 5])   
      beta_points_reward_list <- c(beta_points_reward_list, summary(jm_fit)$Survival[1, 1])  
    
      ## Prep DF for Joint Model Fitting and select predictor variables ##
      joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted)
      
      ## Create Test/Train ##
      split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time) %>% distinct()
      split_index <- create_test_train(split_df, 123)
      train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
      test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)
      
      ## prediction time ##
      prediction_time <- median(split_df$turnaround_time)
      
      ## Prep dfs ##
      # longitudinal dfs
      train_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% train_trials)
      test_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% test_trials)
      
      # survival dfs
      cox_df <- create_survival_df(joint_dist_df)
      train_cox_df <- cox_df %>%
        filter(trial_numeric %in% train_trials)
      test_cox_df <- cox_df %>%
        filter(trial_numeric %in% test_trials)
      
      ### Calibration/Discrimintation ###
      ## AUC ##
      auc <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = prediction_time, idVar = 'trial_numeric')
      auc_reward_list <- c(auc_reward_list, auc$auc)
      
      ### Calibration ###
      toi <- prediction_time - .5
      cal_mets <- calibration_metrics(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, idVar = 'trial_numeric')
      ici_reward_list <- c(ici_reward_list, cal_mets[1])
      e50_reward_list <- c(e50_reward_list, cal_mets[2])
      e90_reward_list <- c(e90_reward_list, cal_mets[3])
      
      ### Brier Scores ###
      brier_scores <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, integrated = F)
      brier_reward_list <- c(brier_reward_list, brier_scores$Brier)
      
      ## Custom Checks ##
      test_three_trials <- test_long_data %>% 
        filter(trial_time < .5) %>%
        select(-turnaround_time, -EVENT)
      
      test_preds <- predict(jm_fit, 
                newdata = test_three_trials, process = "event", return_newdata = TRUE, 
                idVar = "trial_numeric", times = seq(.5, 2.5, .05))
      
      test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
      test_preds_reward <- left_join(test_preds, test_cox_df, by = "trial_numeric")
      
      test_preds_reward <- test_preds_reward %>%
        arrange(turntime_real) %>%
        mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))
      
      # correaltions between pred and real
      scatter_pred_df <- test_preds_reward %>%
        mutate(near_50 = abs(pred_CIF - .5)) %>%
        group_by(trial_numeric) %>%
        mutate(closest_to_50 = min(near_50)) %>%
        filter(closest_to_50 == near_50) %>%
        mutate(turntime_pred = trial_time) %>%
        ungroup() %>%
        select(trial_numeric, turntime_real, turntime_pred) %>%
        distinct() 
      
      cor_score <- cor(scatter_pred_df$turntime_real, scatter_pred_df$turntime_pred)
      core_reward_list <- c(core_reward_list, cor_score)
      
    }, silent = TRUE)

}
```

```{r concat-threat-model-diagnostics,, results='asis', echo=FALSE}

threat_sub_list <- c()
auc_threat_list <- c()
ici_threat_list <- c()
e50_threat_list <- c()
e90_threat_list <- c()
brier_threat_list <- c()
core_threat_list <- c()
dic_threat_list <- c()
rhat_points_threat_list <- c()
p_points_threat_list <- c()
beta_points_threat_list <- c()

for(current_subject in unique(game_data_distance$subject)){
    permuted <- FALSE
    file_name <- paste0(current_subject, "_threat-only_", as.character(permuted))
    
    try({
    
      ## load model ##
      jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))
      
      ## get subject list ##
      threat_sub_list <- c(threat_sub_list, current_subject)
      
      ## fit metrics ##
      dic_threat_list <- c(dic_threat_list, jm_fit$fit_stats$marginal$DIC)
      rhat_points_threat_list <- c(rhat_points_threat_list, summary(jm_fit)$Survival[1, 6])   
      p_points_threat_list <- c(p_points_threat_list, summary(jm_fit)$Survival[1, 5])   
      beta_points_threat_list <- c(beta_points_threat_list, summary(jm_fit)$Survival[1, 1])  
    
      ## Prep DF for Joint Model Fitting and select predictor variables ##
      joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted)
      
      ## Create Test/Train ##
      split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time) %>% distinct()
      split_index <- create_test_train(split_df, 123)
      train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
      test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)
      
      ## prediction time ##
      prediction_time <- median(split_df$turnaround_time)
      
      ## Prep dfs ##
      # longitudinal dfs
      train_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% train_trials)
      test_long_data <- joint_dist_df %>%
        filter(trial_numeric %in% test_trials)
      
      # survival dfs
      cox_df <- create_survival_df(joint_dist_df)
      train_cox_df <- cox_df %>%
        filter(trial_numeric %in% train_trials)
      test_cox_df <- cox_df %>%
        filter(trial_numeric %in% test_trials)
      
      ### Calibration/Discrimintation ###
      ## AUC ##
      auc <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = prediction_time, idVar = 'trial_numeric')
      auc_threat_list <- c(auc_threat_list, auc$auc)
      
      ### Calibration ###
      toi <- prediction_time - .5
      cal_mets <- calibration_metrics(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, idVar = 'trial_numeric')
      ici_threat_list <- c(ici_threat_list, cal_mets[1])
      e50_threat_list <- c(e50_threat_list, cal_mets[2])
      e90_threat_list <- c(e90_threat_list, cal_mets[3])
      
      ### Brier Scores ###
      brier_scores <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, integrated = F)
      brier_threat_list <- c(brier_threat_list, brier_scores$Brier)
      
      ## Custom Checks ##
      test_three_trials <- test_long_data %>% 
        filter(trial_time < .5) %>%
        select(-turnaround_time, -EVENT)
      
      test_preds <- predict(jm_fit, 
                newdata = test_three_trials, process = "event", return_newdata = TRUE, 
                idVar = "trial_numeric", times = seq(.5, 2.5, .05))
      
      test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
      test_preds_threat <- left_join(test_preds, test_cox_df, by = "trial_numeric")
      
      test_preds_threat <- test_preds_threat %>%
        arrange(turntime_real) %>%
        mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))
      
      # correaltions between pred and real
      scatter_pred_df <- test_preds_threat %>%
        mutate(near_50 = abs(pred_CIF - .5)) %>%
        group_by(trial_numeric) %>%
        mutate(closest_to_50 = min(near_50)) %>%
        filter(closest_to_50 == near_50) %>%
        mutate(turntime_pred = trial_time) %>%
        ungroup() %>%
        select(trial_numeric, turntime_real, turntime_pred) %>%
        distinct() 
      
      cor_score <- cor(scatter_pred_df$turntime_real, scatter_pred_df$turntime_pred)
      core_threat_list <- c(core_threat_list, cor_score)
      
    }, silent = TRUE)

}

```


```{r concat-theta-model-diagnostics,, results='asis', echo=FALSE}

auc_theta_list <- c()
ici_theta_list <- c()
e50_theta_list <- c()
e90_theta_list <- c()
brier_theta_list <- c()
core_theta_list <- c()
dic_theta_list <- c()
rhat_dist_theta_list <- c()
rhat_points_theta_list <- c()
rhat_power_theta_list <- c()
p_dist_theta_list <- c()
p_points_theta_list <- c()
p_power_theta_list <- c()
beta_dist_theta_list <- c()
beta_points_theta_list <- c()
beta_power_theta_list <- c()

## Load Data ##
hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))
game_data_distance <-  read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))

## Only Bob data #
game_data_distance <- game_data_distance %>%
  filter(attack_chase_bob == 'Bob') 

## Clean ieeg data ##
game_data_distance <- game_data_distance %>%
  filter(subject != "BJH026") %>% # no hc data
  filter(trial_time <= 5.10) 

## Permuted? ##
permuted <- FALSE
seed <- 123
final_sub_list <-  unique(game_data_distance$subject)

for(current_subject in final_sub_list){
    permuted <- FALSE
    file_name <- paste0(current_subject, "_hc_theta_", as.character(permuted))
    print(current_subject)
    
    ## load model ##
    jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))
    
    ## fit metrics ##
    dic_theta_list <- c(dic_theta_list, jm_fit$fit_stats$marginal$DIC)
    rhat_dist_theta_list <- c(rhat_dist_theta_list, summary(jm_fit)$Survival[1, 6])   
    rhat_points_theta_list <- c(rhat_points_theta_list, summary(jm_fit)$Survival[2, 6])  
    rhat_power_theta_list <- c(rhat_power_theta_list, summary(jm_fit)$Survival[3, 6])  
    p_dist_theta_list <- c(p_dist_theta_list, summary(jm_fit)$Survival[1, 5])   
    p_points_theta_list <- c(p_points_theta_list, summary(jm_fit)$Survival[2, 5])   
    p_power_theta_list <- c(p_power_theta_list, summary(jm_fit)$Survival[3, 5])   
    beta_dist_theta_list <- c(beta_dist_theta_list, summary(jm_fit)$Survival[1, 1])   
    beta_points_theta_list <- c(beta_points_theta_list, summary(jm_fit)$Survival[2, 1])
    beta_power_theta_list <- c(beta_power_theta_list, summary(jm_fit)$Survival[3, 1])
    
    ## Prep DF for Joint Model Fitting and select predictor variables ##
    joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)
      
    hc_sub_trials <- hc_theta_data %>%
      filter(subject == current_subject) %>%
      pull(trial_numeric) %>%
      unique()
    
    joint_dist_df <- joint_dist_df %>%
      filter(trial_numeric %in% hc_sub_trials)      
      
    ## Create Test/Train ##
    split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time) %>% distinct()
    split_index <- create_test_train(split_df, 123)
    train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
    test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)
    
    ## Merge with the neural predictors ##
    joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)    
    
    ## prediction time ##
    prediction_time <- median(split_df$turnaround_time)
    
    ## Prep dfs ##
    # longitudinal dfs
    train_long_data <- joint_theta_dist_df %>%
      filter(trial_numeric %in% train_trials)
    test_long_data <- joint_theta_dist_df %>%
      filter(trial_numeric %in% test_trials)
    
    # survival dfs
    cox_df <- create_survival_df(joint_theta_dist_df)
    train_cox_df <- cox_df %>%
      filter(trial_numeric %in% train_trials)
    test_cox_df <- cox_df %>%
      filter(trial_numeric %in% test_trials)
    
    ### Calibration/Discrimintation ###
    ## AUC ##
    auc <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = prediction_time, idVar = 'trial_numeric')
    auc_theta_list <- c(auc_theta_list, auc$auc)
    
    ### Calibration ###
    toi <- prediction_time - .5
    cal_mets <- calibration_metrics(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, idVar = 'trial_numeric')
    ici_theta_list <- c(ici_theta_list, cal_mets[1])
    e50_theta_list <- c(e50_theta_list, cal_mets[2])
    e90_theta_list <- c(e90_theta_list, cal_mets[3])
    
    ### Brier Scores ###
    brier_scores <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, integrated = F)
    brier_theta_list <- c(brier_theta_list, brier_scores$Brier)
    
    ## Custom Checks ##
    test_three_trials <- test_long_data %>% 
      filter(trial_time < .5) %>%
      select(-turnaround_time, -EVENT)
    
    test_preds <- predict(jm_fit, 
              newdata = test_three_trials, process = "event", return_newdata = TRUE, 
              idVar = "trial_numeric", times = seq(.5, 2.5, .05))
    
    test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
    test_preds_theta <- left_join(test_preds, test_cox_df, by = "trial_numeric")
    
    test_preds_theta <- test_preds_theta %>%
      arrange(turntime_real) %>%
      mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))
    
    # correaltions between pred and real
    scatter_pred_df <- test_preds_theta %>%
      mutate(near_50 = abs(pred_CIF - .5)) %>%
      group_by(trial_numeric) %>%
      mutate(closest_to_50 = min(near_50)) %>%
      filter(closest_to_50 == near_50) %>%
      mutate(turntime_pred = trial_time) %>%
      ungroup() %>%
      select(trial_numeric, turntime_real, turntime_pred) %>%
      distinct() 
    
    cor_score <- cor(scatter_pred_df$turntime_real, scatter_pred_df$turntime_pred)
    core_theta_list <- c(core_theta_list, cor_score)
    


}
```


```{r concat-theta-model-diagnostics-basic, results='asis', echo=FALSE}

auc_theta_basic_list <- c()
ici_theta_basic_list <- c()
e50_theta_basic_list <- c()
e90_theta_basic_list <- c()
brier_theta_basic_list <- c()
core_theta_basic_list <- c()
dic_theta_basic_list <- c()
rhat_dist_theta_basic_list <- c()
rhat_points_theta_basic_list <- c()
rhat_power_theta_basic_list <- c()
p_dist_theta_basic_list <- c()
p_points_theta_basic_list <- c()
p_power_theta_basic_list <- c()
beta_dist_theta_basic_list <- c()
beta_points_theta_basic_list <- c()
beta_power_theta_basic_list <- c()

## Load Data ##
hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))
game_data_distance <-  read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))


## Only Bob data #
game_data_distance <- game_data_distance %>%
  filter(attack_chase_bob == 'Bob') 

## Clean ieeg data ##
game_data_distance <- game_data_distance %>%
  filter(subject != "BJH026") %>% # no hc data
  filter(trial_time <= 5.10) 

## Permuted? ##
permuted <- FALSE
seed <- 123
final_sub_list <-  unique(game_data_distance$subject)

for(current_subject in final_sub_list){
  
    permuted <- FALSE
    file_name <- paste0(current_subject, "_hc_theta-basic_", as.character(permuted))
    print(current_subject)
  
    ## load model ##
    jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))
    
    ## fit metrics ##
    dic_theta_basic_list <- c(dic_theta_basic_list, jm_fit$fit_stats$marginal$DIC)
    rhat_dist_theta_basic_list <- c(rhat_dist_theta_basic_list, summary(jm_fit)$Survival[1, 6])   
    rhat_points_theta_basic_list <- c(rhat_points_theta_basic_list, summary(jm_fit)$Survival[2, 6])  
    rhat_power_theta_basic_list <- c(rhat_power_theta_basic_list, summary(jm_fit)$Survival[3, 6])  
    p_dist_theta_basic_list <- c(p_dist_theta_basic_list, summary(jm_fit)$Survival[1, 5])   
    p_points_theta_basic_list <- c(p_points_theta_basic_list, summary(jm_fit)$Survival[2, 5])   
    p_power_theta_basic_list <- c(p_power_theta_basic_list, summary(jm_fit)$Survival[3, 5])   
    beta_dist_theta_basic_list <- c(beta_dist_theta_basic_list, summary(jm_fit)$Survival[1, 1])   
    beta_points_theta_basic_list <- c(beta_points_theta_basic_list, summary(jm_fit)$Survival[2, 1])
    beta_power_theta_basic_list <- c(beta_power_theta_basic_list, summary(jm_fit)$Survival[3, 1])
      
    ## Prep DF for Joint Model Fitting and select predictor variables ##
    joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)
      
    hc_sub_trials <- hc_theta_data %>%
      filter(subject == current_subject) %>%
      pull(trial_numeric) %>%
      unique()
    
    joint_dist_df <- joint_dist_df %>%
      filter(trial_numeric %in% hc_sub_trials)      
      
    ## Create Test/Train ##
    split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time) %>% distinct()
    split_index <- create_test_train(split_df, 123)
    train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
    test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)
    
    ## Merge with the neural predictors ##
    joint_theta_basic_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)    
    
    ## prediction time ##
    prediction_time <- median(split_df$turnaround_time)
    
    ## Prep dfs ##
    # longitudinal dfs
    train_long_data <- joint_theta_basic_dist_df %>%
      filter(trial_numeric %in% train_trials)
    test_long_data <- joint_theta_basic_dist_df %>%
      filter(trial_numeric %in% test_trials)
    
    # survival dfs
    cox_df <- create_survival_df(joint_theta_basic_dist_df)
    train_cox_df <- cox_df %>%
      filter(trial_numeric %in% train_trials)
    test_cox_df <- cox_df %>%
      filter(trial_numeric %in% test_trials)
    
    ### Calibration/Discrimintation ###
    ## AUC ##
    auc <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = prediction_time, idVar = 'trial_numeric')
    auc_theta_basic_list <- c(auc_theta_basic_list, auc$auc)
    
    ### Calibration ###
    toi <- prediction_time - .5
    cal_mets <- calibration_metrics(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, idVar = 'trial_numeric')
    ici_theta_basic_list <- c(ici_theta_basic_list, cal_mets[1])
    e50_theta_basic_list <- c(e50_theta_basic_list, cal_mets[2])
    e90_theta_basic_list <- c(e90_theta_basic_list, cal_mets[3])
    
    ### Brier Scores ###
    brier_scores <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = toi, integrated = F)
    brier_theta_basic_list <- c(brier_theta_basic_list, brier_scores$Brier)
    
    ## Custom Checks ##
    test_three_trials <- test_long_data %>% 
      filter(trial_time < .5) %>%
      select(-turnaround_time, -EVENT)
    
    test_preds <- predict(jm_fit, 
              newdata = test_three_trials, process = "event", return_newdata = TRUE, 
              idVar = "trial_numeric", times = seq(.5, 2.5, .05))
    
    test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
    test_preds_theta <- left_join(test_preds, test_cox_df, by = "trial_numeric")
    
    test_preds_theta <- test_preds_theta %>%
      arrange(turntime_real) %>%
      mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))
    
    # correaltions between pred and real
    scatter_pred_df <- test_preds_theta %>%
      mutate(near_50 = abs(pred_CIF - .5)) %>%
      group_by(trial_numeric) %>%
      mutate(closest_to_50 = min(near_50)) %>%
      filter(closest_to_50 == near_50) %>%
      mutate(turntime_pred = trial_time) %>%
      ungroup() %>%
      select(trial_numeric, turntime_real, turntime_pred) %>%
      distinct() 
    
    cor_score <- cor(scatter_pred_df$turntime_real, scatter_pred_df$turntime_pred)
    core_theta_basic_list <- c(core_theta_basic_list, cor_score)

}
```



```{r combine-lists}

true_df <- tibble("subjects" = true_sub_list,
                  "dic"  = dic_true_list,
                  "rhat_threat"  = rhat_dist_true_list,
                  "rhat_reward"  = rhat_points_true_list,
                  "p_threat"  = p_dist_true_list,
                  "p_reward"  = p_points_true_list,
                  "beta_threat"  = beta_dist_true_list,
                  "beta_reward"  = beta_points_true_list,
                  "auc" = auc_true_list,
                  "ici" = ici_true_list,
                  "e50" = e50_true_list,
                  "e90" = e90_true_list,
                  "brier" = brier_true_list,
                  "cor" = core_true_list)

write_csv(true_df, path(here(), "data", "joint_models", "model_summaries", "true_ieeg_df.csv"))

theta_df <- tibble("subjects" = final_sub_list,
                  "dic"  = dic_theta_list,
                  "rhat_threat"  = rhat_dist_theta_list,
                  "rhat_reward"  = rhat_points_theta_list,
                  "rhat_theta"  = rhat_power_theta_list,
                  "p_threat"  = p_dist_theta_list,
                  "p_reward"  = p_points_theta_list,
                  "p_theta"  = p_power_theta_list,
                  "beta_threat"  = beta_dist_theta_list,
                  "beta_reward"  = beta_points_theta_list,
                  "beta_theta"  = beta_power_theta_list,
                  "auc" = auc_theta_list,
                  "ici" = ici_theta_list,
                  "e50" = e50_theta_list,
                  "e90" = e90_theta_list,
                  "brier" = brier_theta_list,
                  "cor" = core_theta_list)

write_csv(theta_df, path(here(), "data", "joint_models", "model_summaries", "theta_ieeg_df.csv"))

theta_basic_df <- tibble("subjects" = final_sub_list,
                  "dic"  = dic_theta_basic_list,
                  "rhat_threat"  = rhat_dist_theta_basic_list,
                  "rhat_reward"  = rhat_points_theta_basic_list,
                  "rhat_theta_basic"  = rhat_power_theta_basic_list,
                  "p_threat"  = p_dist_theta_basic_list,
                  "p_reward"  = p_points_theta_basic_list,
                  "p_theta_basic"  = p_power_theta_basic_list,
                  "beta_threat"  = beta_dist_theta_basic_list,
                  "beta_reward"  = beta_points_theta_basic_list,
                  "beta_theta_basic"  = beta_power_theta_basic_list,
                  "auc" = auc_theta_basic_list,
                  "ici" = ici_theta_basic_list,
                  "e50" = e50_theta_basic_list,
                  "e90" = e90_theta_basic_list,
                  "brier" = brier_theta_basic_list,
                  "cor" = core_theta_basic_list)

write_csv(theta_basic_df, path(here(), "data", "joint_models", "model_summaries", "theta_basic_ieeg_df.csv"))


perm_df <- tibble("subjects" = perm_sub_list,
                  "dic"  = dic_perm_list,
                  "rhat_threat"  = rhat_dist_perm_list,
                  "rhat_reward"  = rhat_points_perm_list,
                  "p_threat"  = p_dist_perm_list,
                  "p_reward"  = p_points_perm_list,
                  "beta_threat"  = beta_dist_perm_list,
                  "beta_reward"  = beta_points_perm_list,                  
                  "auc" = auc_perm_list,
                  "ici" = ici_perm_list,
                  "e50" = e50_perm_list,
                  "e90" = e90_perm_list,
                  "brier" = brier_perm_list,
                  "cor" = core_perm_list)

write_csv(perm_df, path(here(), "data", "joint_models", "model_summaries", "perm_ieeg_df.csv"))


reward_df <- tibble("subjects" = reward_sub_list,
                  "dic"  = dic_reward_list,
                  "rhat_reward"  = rhat_points_reward_list,
                  "p_reward"  = p_points_reward_list,
                  "beta_reward"  = beta_points_reward_list,                  
                  "auc" = auc_reward_list,
                  "ici" = ici_reward_list,
                  "e50" = e50_reward_list,
                  "e90" = e90_reward_list,
                  "brier" = brier_reward_list,
                  "cor" = core_reward_list)

write_csv(reward_df, path(here(), "data", "joint_models", "model_summaries", "reward_ieeg_df.csv"))


threat_df <- tibble("subjects" = threat_sub_list,
                  "dic"  = dic_threat_list,
                  "rhat_threat"  = rhat_points_threat_list,
                  "p_threat"  = p_points_threat_list,
                  "beta_threat"  = beta_points_threat_list,                  
                  "auc" = auc_threat_list,
                  "ici" = ici_threat_list,
                  "e50" = e50_threat_list,
                  "e90" = e90_threat_list,
                  "brier" = brier_threat_list,
                  "cor" = core_threat_list)

write_csv(threat_df, path(here(), "data", "joint_models", "model_summaries", "threat_ieeg_df.csv"))



```

