---
title: "iEEG Modeling Results"
output: html_document
date: "2024-02-03"
---
---
title: "Distributions of Permuted and True Scores"
output: html_document
date: "2024-01-03"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 5,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(JMbayes2)
library(caret)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "clean_behavioral_data.R"))
source(path(here(), "R", "create_distance_df.R"))
source(path(here(), "R", "joint_modeling_functions.R"))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)

```


# Permuted vs True Model Comparison

Compares the `standard_model` (`points_remaining` + `distance_to_ghost`) and the `permtued_model` where the timing information for each trial is preserved but the `points_remaining` and `distance_to_ghost` values are shuffled/shuffled. I look at the distriutions of the following performance metrics

 * AUC
 * ICI
 * E50
 * E90
 * Brier Score
 * Predicted vs Observed Correlations
 
 From the initial look, the `standard_model` is significantly outperforming the `permuted_model` in AUC, meaning that it is correctly ranking trials in terms of risk. However, the calibration metrics are all *worse* in the `standard_model` compared to the `permuted_model`, so the model is still pretty far off from correctly predicting the probability of turnaround at any moment. I think the reason the measures are better in the `permuted_model` is that it just uses the average time of turnaround, which is maybe less dramatically off in terms of specific probabilities, but can't differentiate the trials very well. 
 
 If I look at the calibration plots for subjects 14 and 15, I think you can see what is happening. For 14, the calibration metrics are better in the `standard_model` and the red line follows the dotted line pretty well. However, in 15, in the `standard_model` the red line is very off at the edges. However, the `permuted_model` has a red line that is defined on only a short range of the x-axis, so it is not as off, even though I think it is a worse model. 



```{r load-data}

theta_df <- read_csv(path(here(), "data", "joint_models", "model_summaries", "theta_ieeg_df.csv"))
theta_basic_df <- read_csv(path(here(), "data", "joint_models", "model_summaries", "theta_basic_ieeg_df.csv"))
true_df <- read_csv(path(here(), "data", "joint_models", "model_summaries", "true_ieeg_df.csv"))
perm_df <- read_csv(path(here(), "data", "joint_models", "model_summaries", "perm_ieeg_df.csv"))
# reward_df <- read_csv(path(here(), "data", "joint_models", "model_summaries", "reward_df.csv"))
# threat_df <- read_csv(path(here(), "data", "joint_models", "model_summaries", "threat_df.csv"))

theta_subsample_df <- theta_df %>% select(colnames(true_df)) %>% mutate(case = "theta") 


model_compare_df <- rbind(true_df %>% mutate(case = "true"),
                          theta_df %>% select(colnames(true_df)) %>% mutate(case = "theta") ,
                          theta_basic_df  %>% select(colnames(true_df)) %>% mutate(case = "theta_basic"),
                          perm_df %>% mutate(case = "permuted") ) #,
                          # reward_df %>% mutate(case = "reward") %>% mutate(rhat_threat = NA) %>% mutate(p_threat = NA) %>% mutate(beta_threat = NA),
                          # threat_df %>% mutate(case = "threat") %>% mutate(rhat_reward = NA) %>% mutate(p_reward = NA) %>% mutate(beta_reward = NA))

model_wide_df <- left_join(true_df, perm_df, by = "subjects", suffix = c("_true", "_perm"))
theta_model_wide_df <- left_join(theta_basic_df, theta_df, by = "subjects", suffix = c("_basic", "_theta"))


```



```{r visualizastions, fig.width = 15, fig.height = 8}

model_compare_df %>%
  pivot_longer(cols = c(auc:cor), names_to = "metric", values_to = "value") %>%
  ggplot(aes(x = metric, y = value, fill = case, color = case)) +
  geom_boxplot(notch = FALSE, color = "black") +
  geom_point(position = position_dodge(width = .75), alpha = .5) +
  facet_wrap(~metric, scales = "free") +
  theme_bw() +
  theme(legend.position = "top", 
        strip.text = element_text(size = 14),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(title = "Model Performance Comparison",
       subtitle = "True vs. Permuted",
       x = "Metric",
       y = "Value")





```

```{r conf-interval}

t.test(model_wide_df$auc_true)

t.test(x = model_wide_df$auc_true, y = model_wide_df$auc_perm, paired = TRUE)

```


```{r model-summaries, fig.width = 15, fig.height = 8}


model_compare_df %>%
  pivot_longer(cols = rhat_threat:rhat_reward, names_to = "metric", values_to = "value") %>%
  ggplot(aes(x = metric, y = value, fill = case, color = case)) +
  geom_violin() +
  # geom_point(position = position_dodge(width = .75), alpha = .5) +
  geom_hline(yintercept = 1.1, linetype = "dotted", color = "black") +
  facet_wrap(~metric, scales = "free") +
  theme_bw() +
  theme(legend.position = "top", 
        strip.text = element_text(size = 14),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(title = "Model Value Comparison",
       subtitle = "True vs. Permuted",
       x = "Metric",
       y = "Value")



model_compare_df %>%
  filter(case == "true") %>%
  pivot_longer(cols = beta_threat:beta_reward, names_to = "metric", values_to = "value") %>%
  ggplot(., aes(x = value, fill = metric)) +
  geom_density(color = "black", alpha = .5) +
  theme(panel.background = element_rect(fill = "white"))


```


```{r auc-indv-improvement, fig.width = 12, fig.height = 12}

model_wide_df %>%
  mutate(auc_dif = auc_true - auc_perm) %>%
  arrange(auc_dif) %>%
  mutate(subjects = factor(subjects, levels = unique(subjects))) %>%
  mutate(auc_true = auc_true - auc_perm) %>%
  mutate(auc_perm = 0) %>%
  ggplot(.,) +
    geom_segment( aes(x=subjects, xend=subjects, y=auc_perm, yend=auc_true), color="black") +
    geom_point( aes(x=subjects, y=auc_true), color=rgb(0.2,0.7,0.1,0.8), size=3 ) + # green true
    geom_point( aes(x=subjects, y=auc_perm), color=rgb(0.7,0.2,0.1,0.8), size=3 ) +
    geom_vline(xintercept  = "Subject_25", color = "grey") +
    coord_flip()+
    theme(
      panel.background = element_rect(fill = "white"),
      legend.position = "top",
    ) +
    labs(x = "Subject", y = "AUC Improvement", title = "AUC Improvement", subtitle = "Green = True, Red = Permuted")


```

```{r auc-indv-improvement, fig.width = 12, fig.height = 12}

theta_model_wide_df %>%
  mutate(auc_dif = auc_theta - auc_basic) %>%
  arrange(auc_dif) %>%
  mutate(subjects = factor(subjects, levels = unique(subjects))) %>%
  mutate(auc_theta = auc_theta - auc_basic) %>%
  mutate(auc_basic = 0) %>%
  ggplot(.,) +
    geom_segment( aes(x=subjects, xend=subjects, y=auc_basic, yend=auc_theta), color="black") +
    geom_point( aes(x=subjects, y=auc_theta), color=rgb(0.2,0.7,0.1,0.8), size=3 ) + # green true
    geom_point( aes(x=subjects, y=auc_basic), color=rgb(0.7,0.2,0.1,0.8), size=3 ) +
    # geom_vline(xintercept  = "Subject_25", color = "grey") +
    coord_flip()+
    theme(
      panel.background = element_rect(fill = "white"),
      legend.position = "top",
    ) +
    labs(x = "Subject", y = "AUC Improvement", title = "AUC Improvement", subtitle = "Green = True, Red = Permuted")


```


```{r cor-indv-improvement, fig.width = 12, fig.height = 12}

model_wide_df %>%
  mutate(cor_dif = cor_true - cor_perm) %>%
  arrange(cor_dif) %>%
  mutate(subjects = factor(subjects, levels = unique(subjects))) %>%
  mutate(cor_true = cor_true - cor_perm) %>%
  mutate(cor_perm = 0) %>%
  ggplot(.,) +
    geom_segment( aes(x=subjects, xend=subjects, y=cor_perm, yend=cor_true), color="black") +
    geom_point( aes(x=subjects, y=cor_true), color=rgb(0.2,0.7,0.1,0.8), size=3 ) + # green true
    geom_point( aes(x=subjects, y=cor_perm), color=rgb(0.7,0.2,0.1,0.8), size=3 ) +
    geom_vline(xintercept  = "Subject_45", color = "grey") +
    coord_flip()+
    theme(
      panel.background = element_rect(fill = "white"),
      legend.position = "top",
    ) +
    labs(x = "Subject", y = "Correlation Improvement", title = "Correlation Improvement", subtitle = "Green = True, Red = Permuted")


```



