---
title: "JMBayes"
output: html_document
date: "2023-07-26"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 5,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(JMbayes2)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "clean_behavioral_data.R"))
source(path(here(), "R", "create_distance_df.R"))
## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)

```

Okay, I need to come up with a model fitting framework. I will use DIC to compare models, but I need to figure out what my approach is for going through the different options.

First, I think we should add in Lives and possibly Score, because I know this definitely effects the players choices. Is it possible to include interactions within this framework, not sure.

Then I think I want to gather a full list of options for operationalizing reward and compare that in a couple of subjects. I think starting out with ~5 subjects is optimal because I don't have a good prior about whether or not people are solving it in the same way and if I move to a hierarcical modeling option then I have to disentangle how well the model is doing as parsing subejct variance as well as parsing the different reward options. 

Cognitive Strategies for Reward

* go out and get a certain amount of reward and then come back
* try to get as much reward as possible until the ghost gets to close and then turn around
* pay attention to how close the next reward is and how big it is

Possible quantifications of reward

* amount of dots remaining
* amount of points remaining
* discounted by distance number of points remaining 
* number of big rewards left, number of small rewards left
* 5 different variables for the distance to each reward
* 5 different variables for the amount each reward/ if it is remaining

In general variables should be mean-centered:

The Cox PH submodel can be formulated as

â„Žð‘–(ð‘¡)=â„Ž0(ð‘¡)exp(ð›¾ð‘‡ð‘¤ð‘–),

where â„Ž0(ð‘¡) is the baseline hazard function at time ð‘¡ and ð‘¤ð‘–is a vector of baseline predictors with corresponding regression coefficients ð›¾
The submodel has two distinct parts. First, â„Ž0(ð‘¡) describes the hazard (e.g., risk of the event occurring, given it has not yet occurred) when all covariates ð‘¤ð‘– have value zero. This baseline hazard function is assumed invariant across all individuals ( â„Ž0(ð‘¡) does not depend on ð‘–). 
Second, the effect parameters ð›¾ð‘‡ð‘¤ð‘–describe how the hazard varies as a function of the explanatory covariates ð‘¤ð‘–.


NOTES

Functions start to break if Thoriz is larger than the longest turn time!

Next to figure out, why does AUC, ROC chane so much with different Thoriz??

```{r load-data}

pilot_behave_data_clean <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_behavior.csv"))
pilot_game_data_clean <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_game_data.csv"))
pilot_game_data_distance <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_distance_data.csv"))
pilot_all_vars_df <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_across_trial_data.csv"))

```


```{r}

pilot_game_data_distance %>%
  # filters #
  filter(number_of_runs > 0) %>%
  # distinct #
  select(trial_numeric, subject, last_away) %>%
  distinct() %>%
  filter(subject %in% sample(subject, 5)) %>%
  ggplot(., aes(x = subject, y = last_away)) +
  # geom_point(alpha = .3) +
  # geom_violin() +
  geom_jitter(alpha = .5, color = "grey") +
  geom_boxplot(notch = T) +
  ylab("Distance to Ghost at Turnaround") + xlab("Subjects") +
  theme(panel.background = element_rect(fill = "white"), axis.ticks.x = element_blank()) +
  ggtitle("Subject Variability in Turning Distance", subtitle = "Random sample of 5 subjects shows that the within subject variability \nin turn around time is usually less than across subject variability")



```

## Random Permuted

check to make sure the shuffling works by comparing distance to ghost at turnaround in shuffled vs real


```{r random-time-series}

random_time_series <- function(n, low_val, high_val) {
  timeseries = numeric(n)
  timeseries[1] = sample(low_val:high_val, 1)
  
  for (i in 2:n) {
    change = sample(c(-2, 2), 1)
    
    # Check boundaries and adjust if necessary
    if (timeseries[i-1] + change < 0) {
      change = 2
    } else if (timeseries[i-1] + change > 100) {
      change = -2
    }
    
    timeseries[i] = timeseries[i-1] + change
  }
  return(timeseries)

}
# Plotting the timeseries
plot(random_time_series(50, 0, 100), type = 'l', ylim = c(0, 100), xlab = "Time", ylab = "Value")

```

 ## Permuted Data Subject 38
 
```{r permuted-38}

# filter to single subject and reset time to be from when they started moving #
permuted_sub_df <- pilot_game_data_distance %>%
  filter(subject == "Subject_38") %>%
  filter(Direction != "Still") %>%
  filter(dots_eaten != 0) %>%
  group_by(trial_numeric) %>%
  mutate(trial_time = trial_time - first(trial_time)) %>%
  mutate(distance_to_ghost = random_time_series(length(distance_to_ghost), 0, 100)) %>%
  mutate(points_remaining = sample(points_remaining, length(points_remaining))) %>%
  mutate(final_reward = if_else(reward_groups >2, "big", "small")) %>%
  ungroup() %>%
  select(subject, trial_numeric, distance_to_ghost, last_away, 
         away_choice, trial_time, TrialType, points_remaining) %>%
  mutate(EVENT = 1)  %>%
  mutate(points_remaining = scale(points_remaining)) %>%
  mutate(distance_to_ghost = scale(distance_to_ghost))

# get hold out trials #
# set.seed(56)
# hold_out_trials <- sample(unique(permuted_sub_df$trial_numeric), 20)

# create the survival dataframe
permuted_sub_cox_df <- permuted_sub_df %>%
  group_by(trial_numeric) %>%
  filter(away_choice == last_away & away_choice != 0) %>%
  filter(trial_time == last(trial_time)) %>%
  mutate(Time = trial_time) %>%
  ungroup() %>%
  mutate(event = 1) %>%
  select(trial_numeric, Time, event, EVENT) %>%
  filter(!trial_numeric %in% hold_out_trials)

# created longitudinal data frame #
all_permuted_sub_df <- permuted_sub_df %>%
  group_by(trial_numeric) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
  filter(trial_time <= max(turnaround_time)) %>%
  mutate(Time = last(trial_time)) %>%
  ungroup() 

# exclude hold out subjects #  
permuted_sub_df <-  all_permuted_sub_df %>%
  filter(trial_numeric %in% permuted_sub_cox_df$trial_numeric)

test_permuted_sub_df <-  all_permuted_sub_df %>%
  filter(trial_numeric %in% hold_out_trials)

# test to see permutation worked #
permuted_sub_df %>%
  filter(trial_numeric %in% sample(trial_numeric, 10)) %>%
  # filter(event == 1) %>%
  ggplot(., aes(x = distance_to_ghost)) +
  geom_histogram(binwidth = 2) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

permuted_sub_df %>%
  filter(trial_numeric %in% sample(trial_numeric, 10)) %>%
  # filter(event == 1) %>%
  ggplot(., aes(x = distance_to_ghost)) +
  geom_histogram(binwidth = 2) +
  theme(panel.background = element_rect(fill = "white")) 

```

```{r permuted-jmbayes-38}

# longitudinal model #
control = lmeControl(maxIter = 1000, niterEM = 1000)
lm_threat <- lme(distance_to_ghost ~ trial_time, data = permuted_sub_df, random = ~trial_time | trial_numeric, control = control)
lm_reward <- lme(points_remaining ~ trial_time, data = permuted_sub_df, random = ~trial_time | trial_numeric, control = control)

# summary of ml models
summary(lm_threat)
summary(lm_reward)

# survival model #
CoxFit_permuted <- coxph(Surv(Time, EVENT) ~ 1, data = permuted_sub_cox_df)

# joint model #
JMFit1_permuted <- jm(CoxFit_permuted, list(lm_threat, lm_reward), time_var = "trial_time", data_Surv = permuted_sub_cox_df, 
                      n_burnin = 1000, n_iter = 30000, n_chains =8)
summary(JMFit1_permuted)


```

```{r permuted-auc-roc-38}

### ROC/AUC ###
roc <- tvROC(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')
plot(roc)   

tvAUC(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

### Calibration ###
calibration_plot(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7, idVar = 'trial_numeric')
calibration_metrics(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7, idVar = 'trial_numeric')

### Brier Scores ###
tvBrier(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7)

tvBrier(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7, integrated = T)

```

```{r permuted-held-out-trials-38}

### Held Out Trials ###

# test_trials <- sort(sample(hold_out_trials, 13))
test_trials <- c(9, 48, 59)

test_three_trials <- test_permuted_sub_df %>% 
  filter(trial_numeric %in% test_trials) %>%
  filter(trial_time < .5) %>%
  select(-Time, -EVENT)


trial_1 <- test_permuted_sub_df %>% filter(trial_numeric == test_trials[1]) %>% filter(trial_time < .5)
trial_2 <- test_permuted_sub_df %>% filter(trial_numeric == test_trials[2]) %>% filter(trial_time < .5)
trial_3 <- test_permuted_sub_df %>% filter(trial_numeric == test_trials[3]) %>% filter(trial_time < .5)

test_three_preds <- predict(JMFit1_permuted, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))


test_three_preds_tmp <- test_three_preds %>%
  mutate(above_4 = pred_CIF > .4) %>%
  group_by(trial_numeric) %>%
  mutate(number_above_cut = sum(as.numeric(above_4)))

ggthemr("solarized")
plot_38 <- ggplot() +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5) +
  geom_point(data = test_three_preds, aes(x = trial_time, y = pred_CIF, color = factor(trial_numeric))) +
  # geom_ribbon(data = test_three_preds, aes(x = trial_time, ymin = low_CIF, ymax = upp_CIF, fill = factor(trial_numeric)), alpha = .5) +
  geom_vline(xintercept = test_permuted_sub_df %>% filter(trial_numeric == test_trials[1]) %>% pull(Time) %>% unique()) +
  geom_vline(xintercept = test_permuted_sub_df %>% filter(trial_numeric == test_trials[2]) %>% pull(Time) %>% unique(),
             color = "#E68D81") +
  geom_vline(xintercept = test_permuted_sub_df %>% filter(trial_numeric == test_trials[3]) %>% pull(Time) %>% unique()
             , color = "#5EB7AB") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.title = element_text(color = "black", size = 14),
        legend.text = element_text(color = "black", size = 12),
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle("Prediction on three held out trials") +
  labs(x = "Time", y = "Probability of Turning Around")

ggsave(path(here(), "figures", "jmbayes", "permuted_hold_out_test_trials_sub38.png"),
         plot = plot_38,
         width = 8,
         height = 5,
         units = "in",
         dpi = 300)

```

 ## Permuted Data Subject 40
 
```{r permuted-40}

# filter to single subject and reset time to be from when they started moving #
permuted_sub_df <- pilot_game_data_distance %>%
  filter(subject == "Subject_40") %>%
  filter(Direction != "Still") %>%
  filter(dots_eaten != 0) %>%
  group_by(trial_numeric) %>%
  mutate(trial_time = trial_time - first(trial_time)) %>%
  mutate(distance_to_ghost = random_time_series(length(distance_to_ghost), 0, 100)) %>%
  mutate(points_remaining = random_time_series(length(points_remaining), 0, 80)) %>%
  mutate(final_reward = if_else(reward_groups >2, "big", "small")) %>%
  ungroup() %>%
  select(subject, trial_numeric, distance_to_ghost, last_away, 
         away_choice, trial_time, TrialType, points_remaining) %>%
  mutate(EVENT = 1)  %>%
  mutate(points_remaining = scale(points_remaining)) %>%
  mutate(distance_to_ghost = scale(distance_to_ghost))

# get hold out trials #
# set.seed(56)
# hold_out_trials_40 <- sample(unique(permuted_sub_df$trial_numeric), 20)

# create the survival dataframe
permuted_sub_cox_df <- permuted_sub_df %>%
  group_by(trial_numeric) %>%
  filter(away_choice == last_away & away_choice != 0) %>%
  filter(trial_time == last(trial_time)) %>%
  mutate(Time = trial_time) %>%
  ungroup() %>%
  mutate(event = 1) %>%
  select(trial_numeric, Time, event, EVENT) %>%
  filter(!trial_numeric %in% hold_out_trials_40)

# created longitudinal data frame #
all_permuted_sub_df <- permuted_sub_df %>%
  group_by(trial_numeric) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
  filter(trial_time <= max(turnaround_time)) %>%
  mutate(Time = last(trial_time)) %>%
  ungroup() 

# exclude hold out subjects #  
permuted_sub_df <-  all_permuted_sub_df %>%
  filter(trial_numeric %in% permuted_sub_cox_df$trial_numeric)

test_permuted_sub_df <-  all_permuted_sub_df %>%
  filter(trial_numeric %in% hold_out_trials_40)

# test to see permutation worked #
permuted_sub_df %>%
  filter(trial_numeric %in% sample(trial_numeric, 10)) %>%
  # filter(event == 1) %>%
  ggplot(., aes(x = distance_to_ghost)) +
  geom_histogram(binwidth = 2) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

permuted_sub_df %>%
  filter(trial_numeric %in% sample(trial_numeric, 10)) %>%
  # filter(event == 1) %>%
  ggplot(., aes(x = distance_to_ghost)) +
  geom_histogram(binwidth = 2) +
  theme(panel.background = element_rect(fill = "white")) 

```

```{r permuted-jmbayes-40}

# longitudinal model #
control = lmeControl(maxIter = 1000, niterEM = 1000)
lm_threat <- lme(distance_to_ghost ~ trial_time, data = permuted_sub_df, random = ~trial_time | trial_numeric, control = control)
lm_reward <- lme(points_remaining ~ trial_time, data = permuted_sub_df, random = ~trial_time | trial_numeric, control = control)

# summary of ml models
summary(lm_threat)
summary(lm_reward)

# survival model #
CoxFit_permuted <- coxph(Surv(Time, EVENT) ~ 1, data = permuted_sub_cox_df)

# joint model #
JMFit1_permuted <- jm(CoxFit_permuted, list(lm_threat, lm_reward), time_var = "trial_time", data_Surv = permuted_sub_cox_df, 
                      n_burnin = 1000, n_iter = 30000, n_chains =8)
summary(JMFit1_permuted)


```

```{r permuted-auc-roc-40}

### ROC/AUC ###
roc <- tvROC(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')
plot(roc)   

tvAUC(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

### Calibration ###
calibration_plot(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7, idVar = 'trial_numeric')
calibration_metrics(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7, idVar = 'trial_numeric')

### Brier Scores ###
tvBrier(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7)

tvBrier(JMFit1_permuted, newdata = test_permuted_sub_df, Tstart = .5, Dt = .7, integrated = T)

```

```{r permuted-held-out-trials-40}

### Held Out Trials ###

# test_trials <- sort(sample(hold_out_trials_40, 3))
test_trials <- c(29,  87, 126)

test_three_trials <- test_permuted_sub_df %>% 
  filter(trial_numeric %in% test_trials) %>%
  filter(trial_time < .5) %>%
  select(-Time, -EVENT)


trial_1 <- test_permuted_sub_df %>% filter(trial_numeric == test_trials[1]) %>% filter(trial_time < .5)
trial_2 <- test_permuted_sub_df %>% filter(trial_numeric == test_trials[2]) %>% filter(trial_time < .5)
trial_3 <- test_permuted_sub_df %>% filter(trial_numeric == test_trials[3]) %>% filter(trial_time < .5)

test_three_preds <- predict(JMFit1_permuted, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))


test_three_preds_tmp <- test_three_preds %>%
  mutate(above_4 = pred_CIF > .4) %>%
  group_by(trial_numeric) %>%
  mutate(number_above_cut = sum(as.numeric(above_4)))

ggthemr("solarized")
ggplot() +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5) +
  geom_point(data = test_three_preds, aes(x = trial_time, y = pred_CIF, color = factor(trial_numeric))) +
  # geom_ribbon(data = test_three_preds, aes(x = trial_time, ymin = low_CIF, ymax = upp_CIF, fill = factor(trial_numeric)), alpha = .5) +
  geom_vline(xintercept = test_permuted_sub_df %>% filter(trial_numeric == test_trials[1]) %>% pull(Time) %>% unique()) +
  geom_vline(xintercept = test_permuted_sub_df %>% filter(trial_numeric == test_trials[2]) %>% pull(Time) %>% unique(),
             color = "#E68D81") +
  geom_vline(xintercept = test_permuted_sub_df %>% filter(trial_numeric == test_trials[3]) %>% pull(Time) %>% unique()
             , color = "#5EB7AB") +
  theme(panel.background = element_rect(fill = "white")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle("Prediction on three held out trials") +
  labs(x = "Time", y = "Probability of Turning Around") 



```


```{r}

pilot_game_data_distance %>%
  filter(subject == "Subject_38") %>%
  mutate(final_reward = if_else(reward_groups >2, "big", "small")) %>%
  select(trial_numeric, dots_eaten, subject, final_reward, reward_groups) %>%
  distinct() %>%
  ggplot(., aes(fill = factor(reward_groups), x = dots_eaten)) +
  geom_bar(position = position_dodge()) + 
  theme(panel.background = element_rect(fill = "white"))

pilot_game_data_distance %>%
  select(trial_numeric, dots_eaten, subject) %>%
  distinct() %>%
  filter(subject == "Subject_38") %>%
  ggplot(., aes(x =dots_eaten)) +
  geom_histogram(binwidth = 1) +
  theme(panel.background = element_rect(fill = "white"))


pilot_game_data_distance %>%
  filter(subject == "Subject_38") %>%
  filter(Direction != "Still") %>%
  ggplot(., aes(x = factor(Lives), y = distance_to_ghost)) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white"))


 sub_df <- pilot_game_data_distance %>%
  filter(subject == "Subject_38") %>%
  filter(Direction != "Still") %>%
  filter(dots_eaten != 0) %>%
  group_by(trial_numeric) %>%
  mutate(trial_time = trial_time - first(trial_time)) %>%
  mutate(final_reward = if_else(reward_groups >2, "big", "small")) %>%
  mutate(Bisc4_tmp = if_else(Biscuit4 == 1111, UserLocation, Biscuit4)) %>%
  mutate(Bisc4 = if_else(Biscuit4 == 1111, 1, 0)) %>%
  mutate(dist_to_dot_4 = abs(Bisc4_tmp - UserLocation)) %>%
  mutate(Eaten_rev = 5 - Eaten) %>%
  mutate(last_big_reward = if_else(reward_groups %in% c(3, 4), Biscuit5, if_else(reward_groups == 2, Biscuit4, Biscuit3))) %>%
  mutate(dist_last_big_rtmp = if_else(last_big_reward == 1111, UserLocation, last_big_reward)) %>%
  mutate(dist_last_big_r = abs(dist_last_big_rtmp - UserLocation)) %>%
  ungroup() 
 
 
 sub_df %>%
   filter(trial_numeric %in% sample(trial_numeric, 5)) %>%
   ggplot(., aes(x = trial_time, y = dist_last_big_r)) +
   geom_point() +
   geom_line() +
   theme(panel.background = element_rect(fill = "white")) +
   facet_wrap(~trial_numeric)


correlation_mat <- cor(sub_df %>% select(distance_to_ghost, trial_time, Bisc4, Eaten_rev, dist_to_dot_4, points_remaining, Eaten, discounted_reward, distance_to_next_reward, points_aquired, dist_last_big_r))

ggcorrplot(correlation_mat)

```


## Real Data


```{r joint-modeling-threat-only}


### Prep Data 

# filter to single subject and reset time to be from when they started moving #
sub_df <- pilot_game_data_distance %>%
  filter(subject == "Subject_38") %>%
  filter(Direction != "Still") %>%
  # filter(dots_eaten != 0) %>%
  group_by(trial_numeric) %>%
  mutate(trial_time = trial_time - first(trial_time)) %>%
  mutate(final_reward = if_else(reward_groups >2, "big", "small")) %>%
  mutate(Bisc4_tmp = if_else(Biscuit4 == 1111, UserLocation, Biscuit4)) %>%
  mutate(dist_to_dot_4 = abs(Bisc4_tmp - UserLocation)) %>%
  mutate(Bisc4_tmp = if_else(Biscuit4 == 1111, UserLocation, Biscuit4)) %>%
  mutate(dist_to_dot_4 = abs(Bisc4_tmp - UserLocation)) %>%
  ungroup() %>%
  select(subject, trial_numeric, distance_to_ghost, last_away, 
         away_choice, trial_time, TrialType, dist_to_dot_4) %>%
  mutate(EVENT = 1)

# get hold out trials #
set.seed(56)
hold_out_trials <- sample(unique(sub_df$trial_numeric), 20)

# create the survival dataframe
sub_cox_df <- sub_df %>%
  group_by(trial_numeric) %>%
  filter(away_choice == last_away & away_choice != 0) %>%
  filter(trial_time == last(trial_time)) %>%
  mutate(Time = trial_time) %>%
  ungroup() %>%
  mutate(event = 1) %>%
  select(trial_numeric, Time, event, EVENT) %>%
  filter(Time > 0) %>% # get rid of trials where they chose to leave from the moment they started moving
  filter(!trial_numeric %in% hold_out_trials)

# created longitudinal data frame #
all_trials_long_sub_df <- sub_df %>%
  group_by(trial_numeric) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
  filter(trial_time <= max(turnaround_time)) %>%
  mutate(Time = last(trial_time)) %>%
  ungroup() 

# exclude hold out subjects #  
trian_sub_long_df <-  all_trials_long_sub_df %>%
  filter(trial_numeric %in% sub_cox_df$trial_numeric)

test_long_sub_df <-  all_trials_long_sub_df %>%
  filter(trial_numeric %in% hold_out_trials) %>%
  filter(Time > 0)

### Fit Models ###

# longitudinal model #
MixedModelFit2 <- lme(distance_to_ghost ~ trial_time, data = trian_sub_long_df, random = ~trial_time | trial_numeric)
summary(MixedModelFit2)

# survival model #
CoxFit <- coxph(Surv(Time, EVENT) ~ 1, data = sub_cox_df)

# joint model #
JMFit1 <- jm(CoxFit, MixedModelFit2, time_var = "trial_time", data_Surv = sub_cox_df, n_burnin = 1000, n_iter = 30000, n_chains =8)
summary(JMFit1)

### traceplot ###
traceplot(JMFit1)

### densplot ###
densplot(JMFit1)

### cumuplot ###
cumuplot(JMFit1)

### gelman_diag ###
gelman_diag(JMFit1)

### AUC and ROC ###
tvAUC(JMFit1, test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

roc <- tvROC(JMFit1, newdata = test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')
plot(roc) 

### Calibration Plot ###
calibration_plot(JMFit1, newdata = test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

calibration_metrics(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = 1.2)

### Brier Scores ###
tvBrier(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7)

tvBrier(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7, integrated = T)

### Held Out Trials ###

test_trials <- sort(sample(hold_out_trials, 3))

test_three_trials <- test_long_sub_df %>% 
  filter(trial_numeric %in% test_trials) %>%
  filter(trial_time < .5) %>%
  select(-Time, -EVENT)


trial_1 <- test_long_sub_df %>% filter(trial_numeric == test_trials[1]) %>% filter(trial_time < .5)
trial_2 <- test_long_sub_df %>% filter(trial_numeric == test_trials[2]) %>% filter(trial_time < .5)
trial_3 <- test_long_sub_df %>% filter(trial_numeric == test_trials[3]) %>% filter(trial_time < .5)

test_three_preds <- predict(JMFit1, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(0, 2.5, .05))



ggthemr("solarized")
ggplot() +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5) +
  geom_rect(aes(xmin=.5, xmax=1.2, ymin=0, ymax=1), fill = "grey", alpha = .5) +
  geom_point(data = test_three_preds, aes(x = trial_time, y = pred_CIF, color = factor(trial_numeric))) +
  # geom_ribbon(data = test_three_preds, aes(x = trial_time, ymin = low_CIF, ymax = upp_CIF, fill = factor(trial_numeric)), alpha = .5) +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[1]) %>% pull(Time) %>% unique()) +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[2]) %>% pull(Time) %>% unique(),
             color = "#E68D81") +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[3]) %>% pull(Time) %>% unique()
             , color = "#5EB7AB") +
  theme(panel.background = element_rect(fill = "white")) +
  ylim(0, 1) + xlim(0, 2.5) +
  ggtitle("Prediction on three held out trials") +
  labs(x = "Time", y = "Probability of Turning Around")

```


```{r joint-modeling-threat-points-remaining-38}


### Prep Data 

# filter to single subject and reset time to be from when they started moving #
sub_df <- pilot_game_data_distance %>%
  filter(subject == "Subject_38") %>%
  filter(Direction != "Still") %>%
  # filter(dots_eaten != 0) %>%
  group_by(trial_numeric) %>%
  mutate(trial_time = trial_time - first(trial_time)) %>%
  mutate(final_reward = if_else(reward_groups >2, "big", "small")) %>%
  mutate(Bisc4_tmp = if_else(Biscuit4 == 1111, UserLocation, Biscuit4)) %>%
  mutate(dist_to_dot_4 = abs(Bisc4_tmp - UserLocation)) %>%
  mutate(Bisc4_tmp = if_else(Biscuit4 == 1111, UserLocation, Biscuit4)) %>%
  mutate(dist_to_dot_4 = abs(Bisc4_tmp - UserLocation)) %>%
  mutate(last_big_reward = if_else(reward_groups %in% c(3, 4), Biscuit5, if_else(reward_groups == 2, Biscuit4, Biscuit3))) %>%
  mutate(dist_last_big_rtmp = if_else(last_big_reward == 1111, UserLocation, last_big_reward)) %>%
  mutate(dist_last_big_r = abs(dist_last_big_rtmp - UserLocation)) %>%
  ungroup() %>%
  select(subject, trial_numeric, distance_to_ghost, last_away, final_reward, points_remaining, dist_last_big_r,
         away_choice, trial_time, TrialType, dist_to_dot_4) %>%
  mutate(EVENT = 1) %>%
  mutate(points_remaining = scale(points_remaining)) %>%
  mutate(distance_to_ghost = scale(distance_to_ghost))

# # get hold out trials #
# set.seed(56)
# hold_out_trials <- sample(unique(sub_df$trial_numeric), 20)

# create the survival dataframe
sub_cox_df <- sub_df %>%
  group_by(trial_numeric) %>%
  filter(away_choice == last_away & away_choice != 0) %>%
  filter(trial_time == last(trial_time)) %>%
  mutate(Time = trial_time) %>%
  ungroup() %>%
  mutate(event = 1) %>%
  select(trial_numeric, Time, event, EVENT) %>%
  filter(Time > 0) %>% # get rid of trials where they chose to leave from the moment they started moving
  filter(!trial_numeric %in% hold_out_trials)

# created longitudinal data frame #
all_trials_long_sub_df <- sub_df %>%
  group_by(trial_numeric) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
  filter(trial_time <= max(turnaround_time)) %>%
  mutate(Time = last(trial_time)) %>%
  ungroup() 

# exclude hold out subjects #  
trian_sub_long_df <-  all_trials_long_sub_df %>%
  filter(trial_numeric %in% sub_cox_df$trial_numeric)

test_long_sub_df <-  all_trials_long_sub_df %>%
  filter(trial_numeric %in% hold_out_trials) %>%
  filter(Time > 0)

### Fit Models ###

# longitudinal model #
distGhost_lme <- lme(distance_to_ghost ~ trial_time, data = trian_sub_long_df, random = ~trial_time | trial_numeric)
pointsR_lme <- lme(points_remaining ~ trial_time, data = trian_sub_long_df, random = ~trial_time | trial_numeric)

# survival model #
CoxFit <- coxph(Surv(Time, EVENT) ~ 1, data = sub_cox_df)

# joint model #
JMFit1 <- jm(CoxFit, list(distGhost_lme, pointsR_lme), time_var = "trial_time", data_Surv = sub_cox_df, n_burnin = 1000, n_iter = 30000, n_chains =8)
summary(JMFit1)

### traceplot ###
traceplot(JMFit1)

### densplot ###
# densplot(JMFit1)

### cumuplot ###
# cumuplot(JMFit1)

### gelman_diag ###
# gelman_diag(JMFit1)

### AUC and ROC ###
tvAUC(JMFit1, test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

roc <- tvROC(JMFit1, newdata = test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')
plot(roc) 

### Calibration Plot ###
calibration_plot(JMFit1, newdata = test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

calibration_metrics(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7)

### Brier Scores ###
tvBrier(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7)

tvBrier(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7, integrated = T)

### Held Out Trials ###

# test_trials <- sort(sample(hold_out_trials, 3))
test_trials <- c(9, 48, 59)

test_three_trials <- test_long_sub_df %>% 
  filter(trial_numeric %in% test_trials) %>%
  filter(trial_time < .5) %>%
  select(-Time, -EVENT)


trial_1 <- test_long_sub_df %>% filter(trial_numeric == test_trials[1]) %>% filter(trial_time < .5)
trial_2 <- test_long_sub_df %>% filter(trial_numeric == test_trials[2]) %>% filter(trial_time < .5)
trial_3 <- test_long_sub_df %>% filter(trial_numeric == test_trials[3]) %>% filter(trial_time < .5)

test_three_preds <- predict(JMFit1, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(0, 2.5, .05))



ggthemr("solarized")
plot_38 <- ggplot() +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5) +
  geom_point(data = test_three_preds, aes(x = trial_time, y = pred_CIF, color = factor(trial_numeric))) +
  # geom_ribbon(data = test_three_preds, aes(x = trial_time, ymin = low_CIF, ymax = upp_CIF, fill = factor(trial_numeric)), alpha = .5) +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[1]) %>% pull(Time) %>% unique()) +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[2]) %>% pull(Time) %>% unique(),
             color = "#E68D81") +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[3]) %>% pull(Time) %>% unique()
             , color = "#5EB7AB") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.title = element_text(color = "black", size = 14),
        legend.text = element_text(color = "black", size = 12),
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle("Prediction on three held out trials") +
  labs(x = "Time", y = "Probability of Turning Around")

ggsave(path(here(), "figures", "jmbayes", "hold_out_test_trials_sub38.png"),
         plot = plot_38,
         width = 8,
         height = 5,
         units = "in",
         dpi = 300)

```

```{r joint-modeling-threat-points-remaining-40}


### Prep Data 

# filter to single subject and reset time to be from when they started moving #
sub_df <- pilot_game_data_distance %>%
  filter(subject == "Subject_40") %>%
  filter(Direction != "Still") %>%
  # filter(dots_eaten != 0) %>%
  group_by(trial_numeric) %>%
  mutate(trial_time = trial_time - first(trial_time)) %>%
  mutate(final_reward = if_else(reward_groups >2, "big", "small")) %>%
  mutate(Bisc4_tmp = if_else(Biscuit4 == 1111, UserLocation, Biscuit4)) %>%
  mutate(dist_to_dot_4 = abs(Bisc4_tmp - UserLocation)) %>%
  mutate(Bisc4_tmp = if_else(Biscuit4 == 1111, UserLocation, Biscuit4)) %>%
  mutate(dist_to_dot_4 = abs(Bisc4_tmp - UserLocation)) %>%
  mutate(last_big_reward = if_else(reward_groups %in% c(3, 4), Biscuit5, if_else(reward_groups == 2, Biscuit4, Biscuit3))) %>%
  mutate(dist_last_big_rtmp = if_else(last_big_reward == 1111, UserLocation, last_big_reward)) %>%
  mutate(dist_last_big_r = abs(dist_last_big_rtmp - UserLocation)) %>%
  ungroup() %>%
  select(subject, trial_numeric, distance_to_ghost, last_away, final_reward, points_remaining, dist_last_big_r,
         away_choice, trial_time, TrialType, dist_to_dot_4) %>%
  mutate(EVENT = 1) %>%
  mutate(points_remaining = scale(points_remaining)) %>%
  mutate(distance_to_ghost = scale(distance_to_ghost))

# create the survival dataframe
sub_cox_df <- sub_df %>%
  group_by(trial_numeric) %>%
  filter(away_choice == last_away & away_choice != 0) %>%
  filter(trial_time == last(trial_time)) %>%
  mutate(Time = trial_time) %>%
  ungroup() %>%
  mutate(event = 1) %>%
  select(trial_numeric, Time, event, EVENT) %>%
  filter(Time > 0) %>% # get rid of trials where they chose to leave from the moment they started moving
  filter(!trial_numeric %in% hold_out_trials_40)

# created longitudinal data frame #
all_trials_long_sub_df <- sub_df %>%
  group_by(trial_numeric) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
  filter(trial_time <= max(turnaround_time)) %>%
  mutate(Time = last(trial_time)) %>%
  ungroup() 

# exclude hold out subjects #  
trian_sub_long_df <-  all_trials_long_sub_df %>%
  filter(trial_numeric %in% sub_cox_df$trial_numeric)

test_long_sub_df <-  all_trials_long_sub_df %>%
  filter(trial_numeric %in% hold_out_trials_40) %>%
  filter(Time > 0)

### Fit Models ###

# longitudinal model #
distGhost_lme <- lme(distance_to_ghost ~ trial_time, data = trian_sub_long_df, random = ~trial_time | trial_numeric)
pointsR_lme <- lme(points_remaining ~ trial_time, data = trian_sub_long_df, random = ~trial_time | trial_numeric)

# survival model #
CoxFit <- coxph(Surv(Time, EVENT) ~ 1, data = sub_cox_df)

# joint model #
JMFit1 <- jm(CoxFit, list(distGhost_lme, pointsR_lme), time_var = "trial_time", data_Surv = sub_cox_df, n_burnin = 1000, n_iter = 30000, n_chains =8)
summary(JMFit1)

### traceplot ###
# traceplot(JMFit1)

### densplot ###
# densplot(JMFit1)

### cumuplot ###
# cumuplot(JMFit1)

### gelman_diag ###
# gelman_diag(JMFit1)

### AUC and ROC ###
tvAUC(JMFit1, test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

roc <- tvROC(JMFit1, newdata = test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')
plot(roc) 

### Calibration Plot ###
calibration_plot(JMFit1, newdata = test_long_sub_df, Tstart = .5, Thoriz = 1.2, idVar = 'trial_numeric')

calibration_metrics(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7)

### Brier Scores ###
tvBrier(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7)

tvBrier(JMFit1, newdata = test_long_sub_df, Tstart = .5, Dt = .7, integrated = T)

### Held Out Trials ###

# test_trials <- sort(sample(hold_out_trials_40, 3))
test_trials <- c(29,  87, 126)
  
test_three_trials <- test_long_sub_df %>% 
  filter(trial_numeric %in% test_trials) %>%
  filter(trial_time < .5) %>%
  select(-Time, -EVENT)


trial_1 <- test_long_sub_df %>% filter(trial_numeric == test_trials[1]) %>% filter(trial_time < .5)
trial_2 <- test_long_sub_df %>% filter(trial_numeric == test_trials[2]) %>% filter(trial_time < .5)
trial_3 <- test_long_sub_df %>% filter(trial_numeric == test_trials[3]) %>% filter(trial_time < .5)

test_three_preds <- predict(JMFit1, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(0, 2.5, .05))



ggthemr("solarized")
plot_40 <- ggplot() +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5) +
  geom_point(data = test_three_preds, aes(x = trial_time, y = pred_CIF, color = factor(trial_numeric))) +
  # geom_ribbon(data = test_three_preds, aes(x = trial_time, ymin = low_CIF, ymax = upp_CIF, fill = factor(trial_numeric)), alpha = .5) +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[1]) %>% pull(Time) %>% unique()) +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[2]) %>% pull(Time) %>% unique(),
             color = "#E68D81") +
  geom_vline(xintercept = test_long_sub_df %>% filter(trial_numeric == test_trials[3]) %>% pull(Time) %>% unique()
             , color = "#5EB7AB") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.title = element_text(color = "black", size = 14),
        legend.text = element_text(color = "black", size = 12),
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle("Prediction on three held out trials") +
  labs(x = "Time", y = "Probability of Turning Around")

ggsave(path(here(), "figures", "jmbayes", "hold_out_test_trials_sub40.png"),
         plot = plot_40,
         width = 8,
         height = 5,
         units = "in",
         dpi = 300)

```