---
title: "Reward Modeling"
output: html_document
date: "2024-03-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 5,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(JMbayes2)
library(caret)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "clean_behavioral_data.R"))
source(path(here(), "R", "create_distance_df.R"))
source(path(here(), "R", "joint_modeling_functions.R"))
source(path(here(), "R", "jm_visualization_functions.R"))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
nCores <- 8
registerDoParallel(nCores)

```


### Including No-Ghost Trials

I had wanted to include the no ghost trials, because my assumption was that it would improve the models by providing more data, especially concerning points_remaining. Since people should turn around as soon as points_remaining hits 0, I thought this would help the model pick up on the importance of that variable. However, after trying many, many things, I think the problem stems from a lack of variation in turn time on these trials. Or at the very least they are very bad for subjects where I had not jittered the reward from the starting location! I suppose it might be different for later subjects! (It wasn't)


Printing out the standard deviation in turning times, it is just much much lower for no-ghost trials. This throws off the model and actually deflates the coefficients and makes predictions harder. So for now I think we need to pass on using these trials. 


```{r get-subject, results='asis', echo=FALSE, eval = T}

current_subject <- "Subject_66"
permuted <- FALSE
current_seed <- 17

```


```{r load-data, results='asis', echo=FALSE, eval = T}

## Load Data ##
game_data_behavior <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_game_data_2-3-24.csv"))
pilot_game_data_distance <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_distance_data_2-3-24.csv"))
ns_game_data_distance <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_distance_data_newsample_2-3-24.csv"))

## Bind Rows ##
game_data_distance <- bind_rows(pilot_game_data_distance, ns_game_data_distance)


pilot_all_vars_df <- read_csv(path(here(), "munge", "prolific", "cleaned_pilot_across_trial_data_2-3-24.csv"))

```

```{r distance-vars-for-no-ghost-trials}

game_noghost_distance_data <- game_data_behavior %>%
      filter(TrialType > 16) %>% #  ghost trials only
      mutate(distance_to_ghost = 180) %>%
      mutate(min_distance = NA) %>%
      mutate(towards_ghost = NA) %>%
      group_by(subject, trial_numeric) %>%
      # user movement and distance measures
      mutate(towards_ghost = if_else(Direction == "Left" & starting_side == "Right", "Towards",  # Left:2 Right :11
                                     if_else(Direction == "Right" & starting_side == "Left", "Towards",
                                             if_else(Direction == "Left" & starting_side == "Left", "Away",  # Left:2 Right :11
                                                     if_else(Direction == "Right" & starting_side == "Right", "Away",
                                             if_else(Direction == "Still", "Still", "Unsure")))))) %>%
      mutate(away_choice_tmp = c(0, diff(factor(towards_ghost)))) %>%
      mutate(away_choice = if_else( (away_choice_tmp == -2 & towards_ghost == "Away") |
                                      (away_choice_tmp == -1 & towards_ghost == "Away"), trial_time, 0)) %>%
      select(-away_choice_tmp) %>%
      mutate(number_of_runs = sum(away_choice > 0, na.rm = T)) %>%
      mutate(last_away = if_else(number_of_runs == 0, 0, last(away_choice[away_choice > 0]) )) %>%
      # distance to rewards
      mutate(points_remaining = if_else(reward_groups == 1 & Eaten == 0, 70, #  small	large	large	small	small, total 70
                                        if_else(reward_groups == 1 & Eaten == 1, 70 - 10,
                                                if_else(reward_groups == 1 & Eaten == 2, 70 - 10 - 20,
                                                        if_else(reward_groups == 1 & Eaten == 3, 70 - 10 - 20 - 20,
                                                                if_else(reward_groups == 1 & Eaten == 4, 70 - 10 - 20 -20 - 10,
                                                                        if_else(reward_groups == 1 & Eaten == 5, 70 - 10 - 20 -20 -10 - 10,
                                                                                if_else(reward_groups == 2 & Eaten == 0, 70, #  small	large	small	large	small, total 70
                                                                                        if_else(reward_groups == 2 & Eaten == 1, 70 - 10,
                                                                                                if_else(reward_groups == 2 & Eaten == 2, 70 - 10 -20,
                                                                                                        if_else(reward_groups == 2 & Eaten == 3, 70 - 10 -20 -10,
                                                                                                                if_else(reward_groups == 2 & Eaten == 4, 70 - 10 -20 -10 -20,
                                                                                                                        if_else(reward_groups == 2 & Eaten == 5, 70 - 10 -20 -10 -20 -10,
                                                                                                                                if_else(reward_groups == 3 & Eaten == 0, 80, #  large	small	large	small	large, total 80
                                                                                                                                        if_else(reward_groups == 3 & Eaten == 1, 80 - 20,
                                                                                                                                                if_else(reward_groups == 3 & Eaten == 2, 80 - 20 - 10,
                                                                                                                                                        if_else(reward_groups == 3 & Eaten == 3, 80 - 20 - 10 - 20,
                                                                                                                                                                if_else(reward_groups == 3 & Eaten == 4, 80 - 20 - 10 - 20 - 10,
                                                                                                                                                                        if_else(reward_groups == 3 & Eaten == 5, 80 - 20 - 10 - 20 - 10 - 20,
                                                                                                                                                                                if_else(reward_groups == 4 & Eaten == 0, 70, #  small	small	small	large	large, total 70
                                                                                                                                                                                        if_else(reward_groups == 4 & Eaten == 1, 70 - 10,
                                                                                                                                                                                                if_else(reward_groups == 4 & Eaten == 2, 70 - 10 - 10,
                                                                                                                                                                                                        if_else(reward_groups == 4 & Eaten == 3, 70 - 10 - 10 - 10,
                                                                                                                                                                                                                if_else(reward_groups == 4 & Eaten == 4, 70 - 10 - 10 - 10 - 20,
                                                                                                                                                                                                                        if_else(reward_groups == 4 & Eaten == 5, 70 - 10 - 10 - 10 - 20 - 20, 999
                                                                                                                                                                                                                        ))))))))))))))))))))))))) %>%
      mutate(points_aquired = if_else(reward_groups == 3, 80 - points_remaining, 70 - points_remaining)) %>%
      mutate(distance_to_next_reward = if_else(Eaten == 0, abs(UserLocation - Biscuit1),
                                               if_else(Eaten == 1, abs(UserLocation - Biscuit2),
                                                       if_else(Eaten == 2, abs(UserLocation - Biscuit3),
                                                               if_else(Eaten == 3, abs(UserLocation - Biscuit4),
                                                                       if_else(Eaten == 4, abs(UserLocation - Biscuit5), 0)))))) %>%
      # filter(Direction != "Unsure") %>%
      mutate(Direction = factor(Direction)) %>%
      mutate(discounted_reward = if_else(Eaten == 5, 0, points_remaining * 1/distance_to_next_reward)) %>%
      select(-GhostLocation) %>%
      ungroup()



game_comb_data_distance <- bind_rows(game_data_distance, game_noghost_distance_data)



```


```{r fit-model-ghost-only, results='asis', echo=FALSE, eval = T}

auc_list <- c()
ici_list <- c()
e50_list <- c()
e90_list <- c()
brier_list <- c()
core_list <- c()
dic_list <- c()
pred_time_list <- c()
num_test_trials <- c()
num_train_trials <- c()
seed_list <- c()
survival_df <- tibble("subject"= c(), "seed" = c(), "predictor" = c(), "Mean" = c(), "StDev" = c(), "Min2.5" = c(), "Max97.5" = c(), "P" = c(), "RHat" = c())

# seed #
seed_list <- c(seed_list, current_seed)

## Prep DF for Joint Model Fitting and select predictor variables ##
game_data_distance <- game_data_distance %>% filter(trial_numeric != 186 & trial_numeric != 174)
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
split_index <- create_test_train(split_df, current_seed)
train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

# Print train/test info
print(paste0("Train: ", length(train_trials), " Test: ", length(test_trials)))

## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% train_trials) 
test_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials) 
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials) 

## Fit Joint Model ##
file_name <- paste0(current_subject, "_", permuted, "_", current_seed)
jm_fit_reward_g <- fit_joint_reward_models(train_long_data, train_cox_df, file_name)

summary(jm_fit_reward_g)

```
```{r}

traceplot(jm_fit_reward_g)

```




```{r fit-model-ng, results='asis', echo=FALSE, eval = T}

auc_list <- c()
ici_list <- c()
e50_list <- c()
e90_list <- c()
brier_list <- c()
core_list <- c()
dic_list <- c()
pred_time_list <- c()
num_test_trials <- c()
num_train_trials <- c()
seed_list <- c()
survival_df <- tibble("subject"= c(), "seed" = c(), "predictor" = c(), "Mean" = c(), "StDev" = c(), "Min2.5" = c(), "Max97.5" = c(), "P" = c(), "RHat" = c())

# seed #
seed_list <- c(seed_list, current_seed)

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_noghost_distance_data, current_subject, permuted)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
split_index <- create_test_train(split_df, current_seed)
train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

# Print train/test info
print(paste0("Train: ", length(train_trials), " Test: ", length(test_trials)))

## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% train_trials) 
test_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials) 
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials) 

## Fit Joint Model ##
file_name <- paste0(current_subject, "_", permuted, "_", current_seed)
jm_fit_reward_ng <- fit_joint_reward_models(train_long_data, train_cox_df, file_name)

summary(jm_fit_reward_ng)

```

```{r}

traceplot(jm_fit_reward_ng)


```


```{r fit-model-all, results='asis', echo=FALSE, eval = T}

auc_list <- c()
ici_list <- c()
e50_list <- c()
e90_list <- c()
brier_list <- c()
core_list <- c()
dic_list <- c()
pred_time_list <- c()
num_test_trials <- c()
num_train_trials <- c()
seed_list <- c()
survival_df <- tibble("subject"= c(), "seed" = c(), "predictor" = c(), "Mean" = c(), "StDev" = c(), "Min2.5" = c(), "Max97.5" = c(), "P" = c(), "RHat" = c())

# seed #
seed_list <- c(seed_list, current_seed)

## Prep DF for Joint Model Fitting and select predictor variables ##
game_comb_data_distance <- game_comb_data_distance %>% filter(trial_numeric != 186 & trial_numeric != 174)
joint_dist_df <- prep_joint_df(game_comb_data_distance, current_subject, permuted)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
split_index <- create_test_train(split_df, current_seed)
train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

# Print train/test info
print(paste0("Train: ", length(train_trials), " Test: ", length(test_trials)))

## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% train_trials) 
test_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials) 
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials) 

## Fit Joint Model ##
file_name <- paste0(current_subject, "_", permuted, "_", current_seed)
jm_fit_reward_all <- fit_joint_reward_models(train_long_data, train_cox_df, file_name)

summary(jm_fit_reward_all)

```

```{r}

traceplot(jm_fit_reward_all)


```


```{r fit-model-ng, results='asis', echo=FALSE, eval = T}

auc_list <- c()
ici_list <- c()
e50_list <- c()
e90_list <- c()
brier_list <- c()
core_list <- c()
dic_list <- c()
pred_time_list <- c()
num_test_trials <- c()
num_train_trials <- c()
seed_list <- c()
survival_df <- tibble("subject"= c(), "seed" = c(), "predictor" = c(), "Mean" = c(), "StDev" = c(), "Min2.5" = c(), "Max97.5" = c(), "P" = c(), "RHat" = c())

# seed #
seed_list <- c(seed_list, current_seed)

## Prep DF for Joint Model Fitting and select predictor variables ##
game_comb_data_distance <- game_comb_data_distance %>% filter(trial_numeric != 186 & trial_numeric != 174)
joint_dist_df <- prep_joint_df(game_comb_data_distance, current_subject, permuted)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups, ghost_trial) %>% distinct()
split_index <- create_test_train(split_df, current_seed)
train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

# Print train/test info
print(paste0("Train: ", length(train_trials), " Test: ", length(test_trials)))

## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% train_trials) 
test_long_data <- joint_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials) 
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials) 

## Fit Joint Model ##
file_name <- paste0(current_subject, "_", permuted, "_", current_seed)
jm_fit_reward_all_gsurv <- fit_joint_reward_models(train_long_data, train_cox_df, file_name)

summary(jm_fit_reward_all_gsurv)

```












## EDA

```{r}
# prep
joint_dist_df_g <- prep_joint_df(game_data_distance, current_subject, permuted)
joint_dist_df_ng <- prep_joint_df(game_noghost_distance_data, current_subject, permuted)
joint_dist_df_all <- prep_joint_df(game_comb_data_distance, current_subject, permuted)


joint_df <- rbind(joint_dist_df_g %>% mutate(case = "ghost"), 
                  joint_dist_df_ng %>% mutate(case = "no ghost"),
                  joint_dist_df_all %>% mutate(case = "all"))


joint_df %>%
  ggplot(., aes(x = points_remaining, fill = case)) +
  geom_density(alpha = .7, color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~case)


tmp <- joint_df %>%
  select(subject, trial_numeric, turnaround_time, case) %>%
  distinct() %>%
  ggplot(., aes(x = turnaround_time, fill = case)) +
  geom_histogram(alpha = .7, color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~case)


sd(tmp %>% filter(case == "ghost") %>% pull(turnaround_time))
sd(tmp %>% filter(case == "all") %>% pull(turnaround_time))
sd(tmp %>% filter(case == "no ghost") %>% pull(turnaround_time)) # even in subjects with the jittered dots the variation is very low for no ghost trials

```








