---
title: "Better Split Partitions"
output: html_document
date: "2024-02-15"
---

```{r setup, include=FALSE}
### batch files for joint modeling ###

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(JMbayes2)
library(caret)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "clean_behavioral_data.R"))
source(path(here(), "R", "create_distance_df.R"))
source(path(here(), "R", "joint_modeling_functions.R"))
## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(9, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

```

### Stratified Splits


```{r}

## Load Data ##
hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))
game_data_distance <-  read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
game_data_behavior <-  read_csv(path(here(), "munge", "all_subs_complete_behavior_df.csv"))

## Only Bob data #
game_data_distance <- game_data_distance %>%
  filter(attack_chase_bob == 'Bob') 

## Clean ieeg data ##
game_data_distance <- game_data_distance %>%
  filter(subject != "BJH026") %>% # no hc data
  filter(trial_time <= 5.10) 


```

## BJH029

```{r BJH029-11}

current_subject <- "BJH029"
permuted <- FALSE
seed <- 11

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
fit_joint_models(train_long_data, train_cox_df, file_name)


```

```{r BJH029-11-model-summary}

print(jm_fit)

```

```{r BJH029-11-traceplot}

traceplot(jm_fit)

```

```{r BJH029-11-results}
# timepoints
timepoints <- seq(.9, 3, .1)

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
print(sort(auc))
print("brier")
mean(brier)
print(sort(brier))

```

```{r BJH029-11-calibration-plot}

for(pred_time in timepoints[1:20]){
  
  # calibration plot #
  cal_plot <- calibration_plot(jm_fit, newdata = test_long_data, 
                               Tstart = .5, Dt = pred_time, idVar = 'trial_numeric')
  
}

```

```{r -BJH029-11-plot}

ggthemr("solarized")
    
test_three_trials <- test_long_data %>% 
  filter(trial_time < .5) %>%
  select(-turnaround_time, -EVENT)

test_preds <- predict(jm_fit, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))

test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")

test_preds_true <- test_preds_true %>%
  arrange(turntime_real) %>%
  mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))

# Now use 'numeric_for_color' for the color aesthetic in ggplot
prediction_plot <- ggplot(test_preds_true, aes(x = trial_time, y = pred_CIF, color = trial_numeric)) +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5, color = 'lightgrey') +
  geom_vline(aes(xintercept = turntime_real, color = trial_numeric, alpha = .7)) +
  geom_point() +
  scale_color_viridis_d() +  # Using Viridis color scale
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.position =  'none',
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle(paste0("Prediction on held out trials: ", current_subject)) +
  labs(x = "Time", y = "Probability of Turning Around")

print(prediction_plot)
```

```{r BJH029-12}

current_subject <- "BJH029"
permuted <- FALSE
seed <- 12

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
fit_joint_models(train_long_data, train_cox_df, file_name)


```

```{r BJH029-12-results}
# timepoints
timepoints <- seq(.9, 3, .1)

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
sort(auc)
print("brier")
sort(brier)
mean(brier)
```

```{r BJH029-13}

current_subject <- "BJH029"
permuted <- FALSE
seed <- 13

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
fit_joint_models(train_long_data, train_cox_df, file_name)

```

```{r BJH029-13-results}
# timepoints
timepoints <- seq(.9, 3, .1)

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
sort(auc)
print("brier")
sort(brier)
mean(brier)
```

```{r BJH029-14}

current_subject <- "BJH029"
permuted <- FALSE
seed <- 14

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
fit_joint_models(train_long_data, train_cox_df, file_name)

```

```{r BJH029-14-results}
# timepoints
timepoints <- seq(1, 3, .1)

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
sort(auc)
print("brier")
sort(brier)
mean(brier)


ggthemr("solarized")
    
test_three_trials <- test_long_data %>% 
  filter(trial_time < .5) %>%
  select(-turnaround_time, -EVENT)

test_preds <- predict(jm_fit, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))

test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")

test_preds_true <- test_preds_true %>%
  arrange(turntime_real) %>%
  mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))

# Now use 'numeric_for_color' for the color aesthetic in ggplot
prediction_plot <- ggplot(test_preds_true, aes(x = trial_time, y = pred_CIF, color = trial_numeric)) +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5, color = 'lightgrey') +
  geom_vline(aes(xintercept = turntime_real, color = trial_numeric, alpha = .7)) +
  geom_point() +
  scale_color_viridis_d() +  # Using Viridis color scale
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.position =  'none',
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle(paste0("Prediction on held out trials: ", current_subject)) +
  labs(x = "Time", y = "Probability of Turning Around")

print(prediction_plot)

```

## BJH041 

This person seems to have pretty good fits in general

This person seems to have pretty bad fits in general. Here are the functions we are using to fit the models:

# linear mixed effects models #
lm_threat <- lme(distance_to_ghost ~ trial_time, data = train_long_data, 
                        random = ~trial_time | trial_numeric, control = control)
                        
lm_reward <- lme(points_remaining ~ trial_time, data = train_long_data, 
                        random = ~trial_time | trial_numeric, control = control)
  
# survival model #
cox_fit <- coxph(Surv(turnaround_time, EVENT) ~ 1, data = train_cox_df)
  
# joint model #
jm_fit <- jm(cox_fit, list(lm_threat, lm_reward), time_var = "trial_time", data_Surv = train_cox_df, 
               n_burnin = 1000, n_iter = 30000, n_chains =8, cores = 6)

```{r}

train_long_data %>%
  filter(subject == "BJH041") %>%
  filter(trial_numeric %in% sample(trial_numeric, 5)) %>%
  ggplot(aes(x = trial_time, y = distance_to_ghost, color = factor(trial_numeric))) +
  geom_point() +
  theme(panel.background = element_rect(fill = "white")) 


train_long_data %>%
  filter(subject == "BJH041") %>%
  filter(trial_numeric %in% sample(trial_numeric, 5)) %>%
  ggplot(aes(x = trial_time, y = points_remaining, color = factor(trial_numeric))) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) 

```


```{r BJH041-11}

current_subject <- "BJH041"
permuted <- FALSE
seed <- 11

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
# fit_joint_models(train_long_data, train_cox_df, file_name)


```

```{r BJH041-11-model-summary}

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

print(jm_fit)

```



```{r BJH041-11-traceplot}

traceplot(jm_fit)

```

```{r BJH041-11-results}
# timepoints
timepoints <- seq(1, 2, .1)

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
print(sort(auc))
print("brier")
mean(brier)
print(sort(brier))

```


```{r BJH041-11-calibration-plot}

for(pred_time in timepoints){
  
  # calibration plot #
  cal_plot <- calibration_plot(jm_fit, newdata = test_long_data, 
                               Tstart = .5, Dt = pred_time, idVar = 'trial_numeric')
   
}

```
  

```{r BJH041-11-plot, fig.width=12, fig.height=8}

ggthemr("solarized")
    
test_three_trials <- test_long_data %>% 
  filter(trial_time < .5) %>%
  select(-turnaround_time, -EVENT)

test_preds <- predict(jm_fit, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))

test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")

test_preds_true <- test_preds_true %>%
  arrange(turntime_real) %>%
  mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))

# Now use 'numeric_for_color' for the color aesthetic in ggplot
prediction_plot <- ggplot(test_preds_true, aes(x = trial_time, y = pred_CIF, color = trial_numeric)) +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5, color = 'lightgrey') +
  geom_vline(aes(xintercept = turntime_real, color = trial_numeric, alpha = .7)) +
  geom_point() +
  scale_color_viridis_d() +  # Using Viridis color scale
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.position =  'none',
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle(paste0("Prediction on held out trials: ", current_subject)) +
  labs(x = "Time", y = "Probability of Turning Around")

print(prediction_plot)
```








```{r BJH041-12}

current_subject <- "BJH041"
permuted <- FALSE
seed <- 12

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
fit_joint_models(train_long_data, train_cox_df, file_name)


```

```{r BJH041-12-results}
# timepoints
timepoints <- seq(1.12, 2, .1)

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
sort(auc)
print("brier")
sort(brier)
mean(brier)

    
test_three_trials <- test_long_data %>% 
  filter(trial_time < .5) %>%
  select(-turnaround_time, -EVENT)

test_preds <- predict(jm_fit, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))

test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")

test_preds_true <- test_preds_true %>%
  arrange(turntime_real) %>%
  mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))

# Now use 'numeric_for_color' for the color aesthetic in ggplot
prediction_plot <- ggplot(test_preds_true, aes(x = trial_time, y = pred_CIF, color = trial_numeric)) +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5, color = 'lightgrey') +
  geom_vline(aes(xintercept = turntime_real, color = trial_numeric, alpha = .7)) +
  geom_point() +
  scale_color_viridis_d() +  # Using Viridis color scale
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.position =  'none',
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle(paste0("Prediction on held out trials: ", current_subject)) +
  labs(x = "Time", y = "Probability of Turning Around")

print(prediction_plot)

```

```{r BJH041-13}

current_subject <- "BJH041"
permuted <- FALSE
seed <- 13

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
fit_joint_models(train_long_data, train_cox_df, file_name)

```

```{r BJH041-13-results}
# timepoints
timepoints <- seq(1.12, 2, .1)

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
sort(auc)
print("brier")
sort(brier)
mean(brier)


    
test_three_trials <- test_long_data %>% 
  filter(trial_time < .5) %>%
  select(-turnaround_time, -EVENT)

test_preds <- predict(jm_fit, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))

test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")

test_preds_true <- test_preds_true %>%
  arrange(turntime_real) %>%
  mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))

# Now use 'numeric_for_color' for the color aesthetic in ggplot
prediction_plot <- ggplot(test_preds_true, aes(x = trial_time, y = pred_CIF, color = trial_numeric)) +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5, color = 'lightgrey') +
  geom_vline(aes(xintercept = turntime_real, color = trial_numeric, alpha = .7)) +
  geom_point() +
  scale_color_viridis_d() +  # Using Viridis color scale
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.position =  'none',
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle(paste0("Prediction on held out trials: ", current_subject)) +
  labs(x = "Time", y = "Probability of Turning Around")

print(prediction_plot)

```

```{r BJH041-14}

current_subject <- "BJH041"
permuted <- FALSE
seed <- 14

## Prep DF for Joint Model Fitting and select predictor variables ##
joint_dist_df <- prep_joint_df(game_data_distance, current_subject, permuted, ieeg = FALSE)

hc_sub_trials <- hc_theta_data %>%
  filter(subject == current_subject) %>%
  pull(trial_numeric) %>%
  unique()

joint_dist_df <- joint_dist_df %>%
  filter(trial_numeric %in% hc_sub_trials)

## Create Test/Train ##
split_df <- joint_dist_df %>% select(trial_numeric, turnaround_time, reward_groups) %>% distinct()
# split_index <- create_test_train(split_df, seed)
split_df <- split_df %>%
    mutate(turnaround_time_cat = 
             cut(turnaround_time, breaks = quantile(turnaround_time, 
                                        probs = seq(0, 1, by = 0.2)), include.lowest = TRUE)) %>%
  mutate(strata = paste(reward_groups, turnaround_time_cat, sep="_"))
set.seed(seed)  # for reproducibility
split_index <- createDataPartition(split_df$strata, 
                                  p = 0.8, 
                                  list = FALSE, 
                                  times = 1)


train_trials <- split_df[split_index, 'trial_numeric'] %>% pull(trial_numeric)
test_trials <- split_df[-split_index, 'trial_numeric'] %>% pull(trial_numeric)

## Merge with the neural predictors ##
joint_theta_dist_df <- prep_for_nerual_predictors(joint_dist_df, hc_theta_data)
  
## Prep Train/Test DFs ##
# longitudinal dfs
train_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% train_trials)
test_long_data <- joint_theta_dist_df %>%
  filter(trial_numeric %in% test_trials)

# survival dfs
cox_df <- create_survival_df(joint_theta_dist_df)
train_cox_df <- cox_df %>%
  filter(trial_numeric %in% train_trials)
test_cox_df <- cox_df %>%
  filter(trial_numeric %in% test_trials)

## Fit Joint Model ##
file_name <- paste0(current_subject, "_strataSplit_", seed, "_", permuted)
fit_joint_models(train_long_data, train_cox_df, file_name)

```

```{r BJH041-14-results}
# timepoints
timepoints <- seq(1.12, 2, .1)

## Load Model ##
jm_fit <- readRDS(path(here(), "data", "joint_models", paste0(file_name, ".rds")))

## AUC - all trials  ##
auc <- c()
brier <- c()
for(pred_time in timepoints){
  # auc #
  tmp <- tvAUC(jm_fit, newdata = test_long_data, Tstart = .5, Thoriz = pred_time, idVar = 'trial_numeric')
  auc <- c(auc, tmp$auc)
  
  # brier score #
  tmp <- tvBrier(jm_fit, newdata = test_long_data, Tstart = .5, Dt = pred_time - .5, integrated = F)
  brier <- c(brier, tmp$Brier)
}

print("auc")
mean(auc)
sort(auc)
print("brier")
sort(brier)
mean(brier)


ggthemr("solarized")
    
test_three_trials <- test_long_data %>% 
  filter(trial_time < .5) %>%
  select(-turnaround_time, -EVENT)

test_preds <- predict(jm_fit, 
          newdata = test_three_trials, process = "event", return_newdata = TRUE, 
          idVar = "trial_numeric", times = seq(.5, 2.5, .05))

test_cox_df <- test_cox_df %>% rename(turntime_real = turnaround_time) %>% select(trial_numeric, turntime_real)
test_preds_true <- left_join(test_preds, test_cox_df, by = "trial_numeric")

test_preds_true <- test_preds_true %>%
  arrange(turntime_real) %>%
  mutate(trial_numeric = factor(trial_numeric, levels = unique(trial_numeric)))

# Now use 'numeric_for_color' for the color aesthetic in ggplot
prediction_plot <- ggplot(test_preds_true, aes(x = trial_time, y = pred_CIF, color = trial_numeric)) +
  geom_rect(aes(xmin=0, xmax=.5, ymin=0, ymax=1), fill = "lightgrey", alpha = .5, color = 'lightgrey') +
  geom_vline(aes(xintercept = turntime_real, color = trial_numeric, alpha = .7)) +
  geom_point() +
  scale_color_viridis_d() +  # Using Viridis color scale
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        legend.position =  'none',
        plot.title  = element_text(color = "black", size = 16, face = "plain")) +
  ylim(0, 1) + xlim(0, 2.5) + labs(color = "Test Trial") +
  ggtitle(paste0("Prediction on held out trials: ", current_subject)) +
  labs(x = "Time", y = "Probability of Turning Around")

print(prediction_plot)

```