---
title: "Elevated Hippocampal Activity at Turnaround"
output: html_document
date: "2024-03-26"
---

```{r setup, include=FALSE}
## libraries ##
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(lmtest)
library(blme)
library(scales)
library(ggthemr)
library(RColorBrewer)
library(broom.mixed)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))
source(path(here(), "R", 'separate_mfg_sfg.R'))

## plotting helpers ##
ggthemr("light")
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

```


## Testing for elevated theta power during approach compared to avoidance

This script tests for elevated theta power during approach in the hippocampus, amygdala, OFC, ACC, Insula, MFG, & SFG in both conflict and no-conflict trials. The window of interest is from 1.5 seconds before turning until 1.5 seconds after turning. I average this window within trials, electrodes, and subjects and then compare the approach vs avoiding sections using the following equation:

lmer(trial_theta ~ aac + (1 + aac|subject), data = aac_df)

I tried to first use:

lmer(trial_theta ~ aac + (1 + aac|subject/elec_id), data = aac_df)

But this resulted in singular fits for the no conflict trials. Removing the random slope drastically changed the degrees of freedom and a model with slopes was significantly better than a model without slopes as assessed by an anova.

Meanwhile, removing the nested random effect of electrode did not change the fixed effects estimate hardly at all, and there was no sig difference when I compared the models via anova. The effects in the conflict trials also hold if I include the nested effect of electrode.

Therefore, I believe the best model to assess the affecr of approaching vs avoiding (`aac`) is the one without the nested random effect of electrode, but with a random intercept and slope for subject. I will use this model for all the analyses.



```{r load-data}

hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))
ofc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_ofc_all_subs_logged_iti_onset.csv"))
cing_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_cing_all_subs_logged_iti_onset.csv"))
amyg_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_amyg_all_subs_logged_iti_onset.csv"))
dlpfc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_dlpfc_all_subs_logged_iti_onset.csv"))
insula_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_insula_all_subs_logged_iti_onset.csv"))

# crop time 
hc_theta_data <- hc_theta_data %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
ofc_theta_data <- ofc_theta_data %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
cing_theta_data <- cing_theta_data %>%
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
amyg_theta_data <- amyg_theta_data %>%
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
dlpfc_theta_data <- dlpfc_theta_data %>%
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
insula_theta_data <- insula_theta_data %>%
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)


# separate dlpfc into sfg and mfg
dlpfc_theta_data <- dlpfc_theta_data %>%
  mutate(electrode = gsub("_.*", "", electrode))
dlpfc_theta_data <- separate_mfg_sfg(dlpfc_theta_data)
sfg_theta_data <- dlpfc_theta_data %>% filter(sfg == 1) %>% select(-sfg, -mfg)
mfg_theta_data <- dlpfc_theta_data %>% filter(mfg == 1) %>% select(-sfg, -mfg)

```

```{r read-in-attack-tables}

# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))

## load and compile attack tables ##
for(sub in unique(all_subs_g_dist$subject)){
  
  tmp <- read_csv(path(here(), "data", "ieeg_behave", paste0(sub, "_attack_events.csv")))
  tmp <- tmp %>%
    mutate(subject = sub)
  
  if(exists("attack_events")){
    attack_events <- bind_rows(attack_events, tmp)
  } else {
    attack_events <- tmp
  }
  
}

## modify to get trials of interest ##
attack_events <- attack_events %>%
  mutate(trial_numeric = neural_trial_numeric + 1) %>%
  rename(ghost_attack_trial = event) %>%
  select(subject, trial_numeric, ghost_attack_trial)


all_subs_g_dist <- left_join(all_subs_g_dist, attack_events, by = c("subject", "trial_numeric"))
all_subs_g_dist <- all_subs_g_dist %>%
  mutate(ghost_attack_trial = ifelse(is.na(ghost_attack_trial), 0, ghost_attack_trial))

```

```{r load-behavioral-data}


## merge them ##
# ghost trials #
hc_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             hc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

amyg_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             amyg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

ofc_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             ofc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

cing_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             cing_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

insula_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             insula_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

mfg_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             mfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

sfg_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)),
                             sfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

# no ghost trials #
hc_ng_behave_df <- left_join(all_subs_ng_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             hc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

amyg_ng_behave_df <- left_join(all_subs_ng_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             amyg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

ofc_ng_behave_df <- left_join(all_subs_ng_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)),
                             ofc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

cing_ng_behave_df <- left_join(all_subs_ng_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)),
                             cing_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

insula_ng_behave_df <- left_join(all_subs_ng_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)),
                             insula_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

mfg_ng_behave_df <- left_join(all_subs_ng_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)),
                             mfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

sfg_ng_behave_df <- left_join(all_subs_ng_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)),
                             sfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

```




```{r sig-test-df-prep-function}

# set control values for blmer #
control <- lme4::lmerControl(optimizer = "Nelder_Mead", optCtrl = list(maxfun = 1e6))
start_values <- list("theta" = c(1, 1, 1))

create_sig_test_df <- function(behave_df){

  # create turn df, by timelocking to the turn
  turn_df <- behave_df %>%
      # round time so that we can loop over time later
      mutate(trial_time = round(trial_time, 2)) %>%
      filter(move_direction != "Still") %>%
      # exclude time before they started moving, may be good to look at not doing this as well
      # filiter out ITI
      filter(reward_groups != 99 & !is.na(electrode)) %>%
      # prep electrode variables
      mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
      mutate(electrode = gsub("_.*", "", electrode)) %>%
      # shift the time so that time 0 is the start of movement onset
      group_by(elec_id, trial_numeric, subject) %>%
      # filter time so that trials end when the person turnaround for the final time
      mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
      mutate(event = replace(event, is.na(event), 0)) %>%
      mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
      mutate(turnaround_time = max(turnaround_time)) %>%
      filter(turnaround_time != 0) %>%
      mutate(turn_time = trial_time - turnaround_time) %>%
      ungroup() %>%
      select(subject, elec_id, theta, trial_numeric, trial_time, turn_time, turnaround_time) %>%
      distinct()

  # filter between 1.5 before and after turn, and create approach, avoid condition, average across trial
  aac_df <- turn_df %>%
    filter(turn_time <= 1.5 & turn_time >= -1.5) %>%
    mutate(aac_time = if_else(turn_time <=0, abs(turn_time), turn_time)) %>%
    mutate(aac_time = round(aac_time, 2)) %>%
    mutate(aac = if_else(turn_time <=0, "Approach", "Avoid")) %>%
    group_by(elec_id, aac, trial_numeric) %>%
    mutate(trial_theta = mean(theta)) %>%
    select(-trial_time, -theta, -turn_time, -turnaround_time, -trial_time, -aac_time) %>%
    distinct()  
  
  # run model with rnadom effects of subject and electrode  
  model_tmp <- summary(lmer(trial_theta ~ aac + (1 + aac|subject), data = aac_df))
  pval <- model_tmp$coefficients[2, 5]
  coef <- model_tmp$coefficients[2, 1]
  tval <- model_tmp$coefficients[2, 4]
  df <- model_tmp$coefficients[2, 3]
  
  
  # Create visualization df, by averaging, across electrode, and subject
  acc_df <- aac_df %>%
    mutate(pvalue = pval) %>%
    mutate(beta = coef) %>%
    mutate(tvalue = tval)
    
  return(acc_df)
  
}


```


```{r plotting-functions}

plot_conflict_trials <- function(aac_test_df, roi) {
  
  
 aac_elec_test_df <- aac_test_df %>%
    group_by(elec_id, aac, case) %>%
    mutate(elec_theta = mean(trial_theta)) %>%
    select(-trial_theta, -trial_numeric) %>%
    distinct()
 
 
aac_sub_test_df <-  aac_elec_test_df %>%
    group_by(subject, aac, case) %>%
    mutate(sub_theta = mean(elec_theta)) %>%
    select(-elec_theta, -elec_id) %>%
    distinct()

pval_df <- aac_sub_test_df %>%
    ungroup() %>%
    select(case, pvalue) %>%
    distinct() %>%
    mutate(pvalue = if_else(pvalue < .05, "***", "n.s."))
  
  app_av_plot <- aac_sub_test_df %>%
    ggplot(.) +
    geom_jitter(data = aac_elec_test_df, aes(x = aac, fill = aac, y = elec_theta), width = .3, size = .75, alpha = .5, shape = 21, color = "#2D2327") +
    geom_boxplot(aes(x = aac, y = sub_theta, fill = aac), color = "#2D2327", outlier.size = .5) +
    geom_jitter(aes(x = aac, fill = aac, y = sub_theta), color = "#2D2327", alpha = .9, width = .1, size = 1, shape = 17) +
    geom_line(aes(x = aac, y = sub_theta, group = subject), size = .25, alpha = .9, width = .1, color = "#2D2327") +
    theme(panel.background = element_rect(fill = "white")) +
    scale_fill_manual(values = c("#c2383a","#2c75b3")) +
    scale_color_manual(values = c("#c2383a","#2c75b3")) +
    ggsignif::geom_signif(data = pval_df, manual = T, aes(y_position=c(2, 2), xmin= c(1, 1), xmax = c(2, 2), annotations = pvalue),
                family = "Gill Sans", color = "#2D2327", textsize = 3, vjust =-.5) +
    theme(panel.background = element_rect(fill = "white"), 
          legend.position = "none",
          axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 6),
          axis.title = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
          legend.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
          legend.text  = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
          strip.text = element_text(family = "Gill Sans", color = "#2D2327", size = 7, margin = margin()),
          panel.spacing = unit(0, "lines"),
          plot.subtitle = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
          plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 9, hjust = .5)) +
    scale_color_manual(values = c("#c2383a","#2c75b3")) +
    scale_fill_manual(values = c("#c2383a","#2c75b3")) +
    labs(y = "Average theta power (a.u.)", x = "", fill = "", color = "") +
    ggtitle(roi) +
    facet_wrap(~case, ncol = 2) +
    ylim(-1.1, 2.5)
  
  return(app_av_plot)

}


```


## Conflict Trials


## Hippocampus

```{r plot-both-hc, fig.width = 2, fig.height = 2.4, warning = F}


# create df for conflict, no conflict trials
hc_conflict_plot_df <- create_sig_test_df(hc_behave_df %>% filter(ghost_attack_trial == 0))
hc_noconflict_plot_df <- create_sig_test_df(hc_ng_behave_df)

# merge
hc_plot_df <- bind_rows(hc_conflict_plot_df %>% mutate(case = "Conflict"),
                        hc_noconflict_plot_df %>% mutate(case = "Conflict-Free"))


# create plot
hc_plot <- plot_conflict_trials(hc_plot_df, "Hippocampus")

# print plot
hc_plot

# save plot
ggsave(path(here(), "figures", "Presentation_hc_app_avoid_combined_theta_plot.png"), plot = hc_plot, width = 3, height = 2.7)

```


## Amygdala

```{r plot-amyg, fig.width = 8, fig.height = 6, warning = F}

# create df for conflict, no conflict trials
amyg_conflict_df <- create_sig_test_df(amyg_behave_df %>% filter(ghost_attack_trial == 0))
amyg_noconflict_df <- create_sig_test_df(amyg_ng_behave_df)

# merge
amyg_plot_df <- bind_rows(amyg_conflict_df %>% mutate(case = "Conflict"),
                        amyg_noconflict_df %>% mutate(case = "Conflict-Free"))

# create plot
amyg_plot <- plot_conflict_trials(amyg_plot_df, "Amygdala")

# print plot
amyg_plot

# save plot
ggsave(path(here(), "figures", "figure2_amyg_app_avoid_combined_theta_plot.png"), plot = amyg_plot, width = 2, height = 2.7)


```

## OFC

```{r plot-ofc, fig.width = 8, fig.height = 6, warning = F}

# create df for conflict, no conflict trials
ofc_conflict_df <- create_sig_test_df(ofc_behave_df %>% filter(ghost_attack_trial == 0))
ofc_noconflict_df <- create_sig_test_df(ofc_ng_behave_df)

# merge
ofc_plot_df <- bind_rows(ofc_conflict_df %>% mutate(case = "Conflict"),
                        ofc_noconflict_df %>% mutate(case = "Conflict-Free"))


# create plot
ofc_plot <- plot_conflict_trials(ofc_plot_df, "OFC")


# print plot
ofc_plot

# save plot
ggsave(path(here(), "figures", "figure2_ofc_app_avoid_combined_theta_plot.png"), plot = ofc_plot, width = 2, height = 2.7)


```


## Anterior Cingulate

```{r plot-acc, fig.width = 8, fig.height = 6, warning = F}

# create df for conflict, no conflict trials
cing_conflict_df <- create_sig_test_df(cing_behave_df %>% filter(ghost_attack_trial == 0))
cing_noconflict_df <- create_sig_test_df(cing_ng_behave_df)

# merge
cing_plot_df <- bind_rows(cing_conflict_df %>% mutate(case = "Conflict"),
                        cing_noconflict_df %>% mutate(case = "Conflict-Free"))

# create plot
cing_plot <- plot_conflict_trials(cing_plot_df, "ACC")

# print plot
cing_plot

# save plot
ggsave(path(here(), "figures", "figure2_cing_app_avoid_combined_theta_plot.png"), plot = cing_plot, width = 2, height = 2.7)


```


## Insula

```{r plot-insula, fig.width = 8, fig.height = 6, warning = F, eval = F}

# create df for conflict, no conflict trials
insula_conflict_df <- create_sig_test_df(insula_behave_df)
insula_noconflict_df <- create_sig_test_df(insula_ng_behave_df)

# merge
insula_plot_df <- bind_rows(insula_conflict_df %>% mutate(case = "Conflict Trials"),
                        insula_noconflict_df %>% mutate(case = "Conflict-Free Trials"))

# create plot
insula_plot <- plot_conflict_trials(insula_plot_df, "Insula")

# print plot
insula_plot

# save plot
ggsave(path(here(), "figures", "figure2_insula_app_avoid_combined_theta_plot.png"), plot = insula_plot, width = 5.5, height = 3)


```

## MFG

```{r plot-mfg, fig.width = 8, fig.height = 6, warning = F}

# create df for conflict, no conflict trials
mfg_conflict_df <- create_sig_test_df(mfg_behave_df %>% filter(ghost_attack_trial == 0))
mfg_noconflict_df <- create_sig_test_df(mfg_ng_behave_df)

# merge
mfg_plot_df <- bind_rows(mfg_conflict_df %>% mutate(case = "Conflict"),
                        mfg_noconflict_df %>% mutate(case = "Conflict-Free"))

# create plot
mfg_plot <- plot_conflict_trials(mfg_plot_df, "MFG")

# plot it #
mfg_plot

# save plot
ggsave(path(here(), "figures", "figure2_mfg_app_avoid_combined_theta_plot.png"), plot = mfg_plot, width = 2, height = 2.7)


```

## SFG

```{r plot-sfg, fig.width = 8, fig.height = 6, warning = F, eval = F}

# create df for conflict, no conflict trials
sfg_conflict_df <- create_sig_test_df(sfg_behave_df)
sfg_noconflict_df <- create_sig_test_df(sfg_ng_behave_df)

# merge
sfg_plot_df <- bind_rows(sfg_conflict_df %>% mutate(case = "Conflict Trials"),
                        sfg_noconflict_df %>% mutate(case = "Conflict-Free Trials"))

# create plot
sfg_plot <- plot_conflict_trials(sfg_plot_df, "SFG")

# print plot
sfg_plot

# save plot
ggsave(path(here(), "figures", "sfg_app_avoid_combined_theta_plot.png"), plot = sfg_plot, width = 8, height = 6)


```

## all conflict trials

```{r conflict-trials-model, eval = F}

library(brms)

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


## Hippocampus
# Fit the model
hc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = hc_conflict_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(hc_model)

# save full model #
save(hc_model, file = path(here(), "results", "app_avd_hc_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_hc_theta_model_brms.RData"))
summary(hc_model)

## Amygdala
# Fit the model
amyg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = amyg_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(amyg_model)

# save full model #
save(amyg_model, file = path(here(), "results", "app_avd_amyg_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_amyg_theta_model_brms.RData"))
summary(amyg_model)

## OFC
# Fit the model
ofc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = ofc_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(ofc_model)

# save full model #
save(ofc_model, file = path(here(), "results", "app_avd_ofc_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_ofc_theta_model_brms.RData"))
summary(ofc_model)

## ACC
# Fit the model
acc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = cing_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(acc_model)

# save full model #
save(acc_model, file = path(here(), "results", "app_avd_acc_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_acc_theta_model_brms.RData"))
summary(acc_model)

## MFG
# Fit the model
mfg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = mfg_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(mfg_model)

# save full model #
save(mfg_model, file = path(here(), "results", "app_avd_mfg_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_mfg_theta_model_brms.RData"))
summary(mfg_model)

# ## Insula
# # Fit the model
# insula_model <- brm(
#   formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
#   data = insula_conflict_df,
#   prior = priors,
#   family = gaussian(),
#   iter = 4000,
#   warmup = 1000,
#   chains = 4,
#   control = list(adapt_delta = 0.99),
#   seed = 1234
# )
# 
# 
# summary(insula_model)
# 
# # save full model #
# save(insula_model, file = path(here(), "results", "app_avd_insula_theta_model_brms.RData"))
# load(path(here(), "results", "app_avd_insula_theta_model_brms.RData"))
# summary(insula_model)


```

##  conflict, no attack trials

```{r conflict-noattack-trials-model, eval = F}

library(brms)

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


## Hippocampus
# Fit the model
hc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = hc_conflict_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(hc_model)

# save full model #
save(hc_model, file = path(here(), "results", "app_avd_hc_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_hc_theta_model_noattack_brms.RData"))
summary(hc_model)

## Amygdala
# Fit the model
amyg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = amyg_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(amyg_model)

# save full model #
save(amyg_model, file = path(here(), "results", "app_avd_amyg_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_amyg_theta_model_noattack_brms.RData"))
summary(amyg_model)

## OFC
# Fit the model
ofc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = ofc_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(ofc_model)

# save full model #
save(ofc_model, file = path(here(), "results", "app_avd_ofc_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_ofc_theta_model_noattack_brms.RData"))
summary(ofc_model)

## ACC
# Fit the model
acc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = cing_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(acc_model)

# save full model #
save(acc_model, file = path(here(), "results", "app_avd_acc_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_acc_theta_model_noattack_brms.RData"))
summary(acc_model)

## MFG
# Fit the model
mfg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = mfg_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(mfg_model)

# save full model #
save(mfg_model, file = path(here(), "results", "app_avd_mfg_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_mfg_theta_model_noattack_brms.RData"))
summary(mfg_model)

# ## Insula
# # Fit the model
# insula_model <- brm(
#   formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
#   data = insula_conflict_df,
#   prior = priors,
#   family = gaussian(),
#   iter = 4000,
#   warmup = 1000,
#   chains = 4,
#   control = list(adapt_delta = 0.99),
#   seed = 1234
# )
# 
# 
# summary(insula_model)
# 
# # save full model #
# save(insula_model, file = path(here(), "results", "app_avd_insula_theta_model_brms.RData"))
# load(path(here(), "results", "app_avd_insula_theta_model_brms.RData"))
# summary(insula_model)


```



```{r conflict-free-model, eval = T}

library(brms)

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


## Hippocampus
# Fit the model
hc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = hc_conflict_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(hc_model)

# save full model #
save(hc_model, file = path(here(), "results", "app_avd_hc_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_hc_conflictfree_theta_model_brms.RData"))
summary(hc_model)

## Amygdala
# Fit the model
amyg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = amyg_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(amyg_model)

# save full model #
save(amyg_model, file = path(here(), "results", "app_avd_amyg_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_amyg_conflictfree_theta_model_brms.RData"))
summary(amyg_model)

## OFC
# Fit the model
ofc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = ofc_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(ofc_model)

# save full model #
save(ofc_model, file = path(here(), "results", "app_avd_ofc_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_ofc_conflictfree_theta_model_brms.RData"))
summary(ofc_model)

## ACC
# Fit the model
acc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = cing_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(acc_model)

# save full model #
save(acc_model, file = path(here(), "results", "app_avd_acc_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_acc_conflictfree_theta_model_brms.RData"))
summary(acc_model)

## MFG
# Fit the model
mfg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = mfg_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(mfg_model)

# save full model #
save(mfg_model, file = path(here(), "results", "app_avd_mfg_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_mfg_conflictfree_theta_model_brms.RData"))
summary(mfg_model)

## Insula
# Fit the model
insula_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = insula_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(insula_model)

# save full model #
save(insula_model, file = path(here(), "results", "app_avd_insula_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_insula_conflictfree_theta_model_brms.RData"))
summary(insula_model)


```

