---
title: "Elevated Hippocampal Activity at Turnaround"
output: html_document
date: "2024-03-26"
---

```{r setup, include=FALSE}
## libraries ##
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(lmtest)
library(brms)
library(scales)
library(ggthemr)
library(RColorBrewer)
library(broom.mixed)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))
source(path(here(), "R", 'separate_mfg_sfg.R'))

## plotting helpers ##
ggthemr("light")
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

```


## Testing for elevated theta power during approach compared to avoidance

This script tests for elevated theta power during approach in the hippocampus, amygdala, OFC, ACC, Insula, MFG, & SFG in both conflict and no-conflict trials. The window of interest is from 1.5 seconds before turning until 1.5 seconds after turning. I average this window within trials, electrodes, and subjects and then compare the approach vs avoiding sections using the following equation:

lmer(trial_theta ~ aac + (1 + aac|subject), data = aac_df)

I tried to first use:

lmer(trial_theta ~ aac + (1 + aac|subject/elec_id), data = aac_df)

But this resulted in singular fits for the no conflict trials. Removing the random slope drastically changed the degrees of freedom and a model with slopes was significantly better than a model without slopes as assessed by an anova.

Meanwhile, removing the nested random effect of electrode did not change the fixed effects estimate hardly at all, and there was no sig difference when I compared the models via anova. The effects in the conflict trials also hold if I include the nested effect of electrode.

Therefore, I believe the best model to assess the affecr of approaching vs avoiding (`aac`) is the one without the nested random effect of electrode, but with a random intercept and slope for subject. I will use this model for all the analyses.



```{r load-data}

hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))
ofc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_ofc_all_subs_logged_iti_onset.csv"))
cing_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_cing_all_subs_logged_iti_onset.csv"))
amyg_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_amyg_all_subs_logged_iti_onset.csv"))
dlpfc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_dlpfc_all_subs_logged_iti_onset.csv"))

# crop time 
hc_theta_data <- hc_theta_data %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
ofc_theta_data <- ofc_theta_data %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
cing_theta_data <- cing_theta_data %>%
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
amyg_theta_data <- amyg_theta_data %>%
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)
dlpfc_theta_data <- dlpfc_theta_data %>%
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)


# separate dlpfc into sfg and mfg
dlpfc_theta_data <- dlpfc_theta_data %>%
  mutate(electrode = gsub("_.*", "", electrode))
dlpfc_theta_data <- separate_mfg_sfg(dlpfc_theta_data)
sfg_theta_data <- dlpfc_theta_data %>% filter(sfg == 1) %>% select(-sfg, -mfg)
mfg_theta_data <- dlpfc_theta_data %>% filter(mfg == 1) %>% select(-sfg, -mfg)

```

```{r read-in-attack-tables}

# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))

## load and compile attack tables ##
for(sub in unique(all_subs_g_dist$subject)){
  
  tmp <- read_csv(path(here(), "data", "ieeg_behave", paste0(sub, "_attack_events.csv")))
  tmp <- tmp %>%
    mutate(subject = sub)
  
  if(exists("attack_events")){
    attack_events <- bind_rows(attack_events, tmp)
  } else {
    attack_events <- tmp
  }
  
}

## modify to get trials of interest ##
attack_events <- attack_events %>%
  mutate(trial_numeric = neural_trial_numeric + 1) %>%
  rename(ghost_attack_trial = event) %>%
  select(subject, trial_numeric, ghost_attack_trial)


all_subs_g_dist <- left_join(all_subs_g_dist, attack_events, by = c("subject", "trial_numeric"))
all_subs_g_dist <- all_subs_g_dist %>%
  mutate(ghost_attack_trial = ifelse(is.na(ghost_attack_trial), 0, ghost_attack_trial))

```

```{r read-in-bad-trials}

# bad trials are cleaned in the neural data-- but loading here to get the mean and sd of the turn time
## load and compile attack tables ##
for(sub in unique(all_subs_g_dist$subject)){
  
  tmp <- read_csv(path(here(), "data", "ieeg_behave", paste0(sub, "_bad_trials.csv")))
  tmp <- tmp %>%
    mutate(subject = sub)
  
  if(exists("bad_trials")){
    bad_trials <- bind_rows(bad_trials, tmp)
  } else {
    bad_trials <- tmp
  }
  
}

bad_trials_clean <- bad_trials %>%
  mutate(trial_numeric = neural_trial_numeric + 1) %>%
  mutate(trial_ids = paste0(subject, "_", trial_numeric))


```

```{r load-behavioral-data}


## merge them ##
# ghost trials #
hc_behave_df <- left_join(all_subs_g_dist %>% mutate(trial_time = round(trial_time, 2)), 
                             hc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

amyg_behave_df <- left_join(all_subs_g_dist %>% mutate(trial_time = round(trial_time, 2)), 
                             amyg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

ofc_behave_df <- left_join(all_subs_g_dist %>% mutate(trial_time = round(trial_time, 2)), 
                             ofc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

cing_behave_df <- left_join(all_subs_g_dist %>% mutate(trial_time = round(trial_time, 2)), 
                             cing_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

mfg_behave_df <- left_join(all_subs_g_dist %>% mutate(trial_time = round(trial_time, 2)), 
                             mfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

sfg_behave_df <- left_join(all_subs_g_dist %>% mutate(trial_time = round(trial_time, 2)),
                             sfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

# no ghost trials #
hc_ng_behave_df <- left_join(all_subs_ng_dist %>% mutate(trial_time = round(trial_time, 2)), 
                             hc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

amyg_ng_behave_df <- left_join(all_subs_ng_dist %>% mutate(trial_time = round(trial_time, 2)), 
                             amyg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

ofc_ng_behave_df <- left_join(all_subs_ng_dist %>% mutate(trial_time = round(trial_time, 2)),
                             ofc_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

cing_ng_behave_df <- left_join(all_subs_ng_dist %>% mutate(trial_time = round(trial_time, 2)),
                             cing_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

mfg_ng_behave_df <- left_join(all_subs_ng_dist %>% mutate(trial_time = round(trial_time, 2)),
                             mfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

sfg_ng_behave_df <- left_join(all_subs_ng_dist %>% mutate(trial_time = round(trial_time, 2)),
                             sfg_theta_data  %>% mutate(trial_time = round(trial_time, 2)), by = join_by(subject, trial_numeric, trial_time))

```


```{r avg-turn-time}

# create turn df, by timelocking to the turn
turn_behave_df <- all_subs_g_dist %>%
    # remove bad trials
    mutate(trial_ids = paste(subject, trial_numeric, sep = "_") ) %>%
    filter(!trial_ids %in% bad_trials_clean$trial_ids) %>%
    # round time so that we can loop over time later
    mutate(trial_time = round(trial_time, 2)) %>%
    # filiter out ITI
    filter(reward_groups != 99 & dots_eaten > 0) %>% # dots eaten is already done elsewhere, but good to double check
    # exclude time before they started moving
    group_by(trial_numeric, subject) %>%
    mutate(first_move_tmp = c(0, diff(move_step))) %>%
    mutate(first_move_time = trial_time[min(which(first_move_tmp != 0))]) %>%
    filter(trial_time >= first_move_time) %>%
    filter(move_direction != "Still") %>%   
    # shift the time so that time 0 is the start of movement onset
    mutate(trial_time = trial_time - first(trial_time)) %>%
    # filter time so that trials end when the person turnaround for the final time
    mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
    mutate(event = replace(event, is.na(event), 0)) %>%
    mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
    mutate(turnaround_time = max(turnaround_time)) %>%
    filter(turnaround_time != 0) %>%
    mutate(turn_time = trial_time - turnaround_time) %>%
    ungroup() %>%
    select(subject, trial_numeric, turnaround_time, first_move_time) %>%
    distinct()

turn_move_summary <- turn_behave_df %>% 
  group_by(subject) %>% 
  mutate(sub_mean_turnaround_time = mean(turnaround_time)) %>% 
  mutate(sub_mean_first_move_time = mean(first_move_time)) %>% 
  ungroup() %>% 
  select(subject, sub_mean_turnaround_time, sub_mean_first_move_time) %>%
  distinct() %>%
  mutate(mean_turnaround_time = mean(sub_mean_turnaround_time)) %>%
  mutate(sd_turnaround_time = sd(sub_mean_turnaround_time)) %>%
  mutate(mean_first_move_time = mean(sub_mean_first_move_time)) %>%
  mutate(sd_first_move_time = sd(sub_mean_first_move_time)) %>%
  distinct()



```



```{r sig-test-df-prep-function}

create_sig_test_df <- function(behave_df){

  # create turn df, by timelocking to the turn
  turn_df <- behave_df %>%
    # round time so that we can loop over time later
    mutate(trial_time = round(trial_time, 2)) %>%
    # filiter out ITI
    filter(reward_groups != 99 & !is.na(electrode) & dots_eaten > 0) %>% # dots eaten is already done elsewhere, but good to double check
    # prep electrode variables
    mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
    mutate(electrode = gsub("_.*", "", electrode)) %>%
    # exclude time before they started moving
    group_by(elec_id, trial_numeric, subject) %>%
    mutate(first_move_tmp = c(0, diff(move_step))) %>%
    mutate(first_move_time = trial_time[min(which(first_move_tmp != 0), na.rm = T)]) %>%
    filter(trial_time >= first_move_time) %>%
    # shift the time so that time 0 is the start of movement onset
    mutate(trial_time = trial_time - first(trial_time)) %>%
    # filter time so that trials end when the person turnaround for the final time
    mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
    mutate(event = replace(event, is.na(event), 0)) %>%
    mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
    mutate(turnaround_time = max(turnaround_time)) %>%
    filter(turnaround_time != 0) %>%
    mutate(turn_time = trial_time - turnaround_time) %>%
    ungroup() %>%
    select(subject, elec_id, theta, trial_numeric, trial_time, turn_time, turnaround_time) %>%
    distinct()

  # filter between 1.5 before and after turn, and create approach, avoid condition, average across trial
  aac_df <- turn_df %>%
    filter(turn_time <= 1.5 & turn_time >= -1.5) %>%
    mutate(aac = if_else(turn_time <=0, "App.", "Avd.")) %>%
    group_by(elec_id, aac, trial_numeric) %>%
    mutate(trial_theta = mean(theta)) %>%
    select(-trial_time, -theta, -turn_time, -turnaround_time, -trial_time) %>%
    distinct()  
  
  return(aac_df)
  
}


```

```{r prep-roi-dfs-for-analysis}

# HC
# create df for conflict, no conflict trials
hc_conflict_df <- create_sig_test_df(hc_behave_df %>% filter(ghost_attack_trial == 0))
hc_noconflict_df <- create_sig_test_df(hc_ng_behave_df)

# Amyg
# create df for conflict, no conflict trials
amyg_conflict_df <- create_sig_test_df(amyg_behave_df %>% filter(ghost_attack_trial == 0))
amyg_noconflict_df <- create_sig_test_df(amyg_ng_behave_df)

## OFC
# create df for conflict, no conflict trials
ofc_conflict_df <- create_sig_test_df(ofc_behave_df %>% filter(ghost_attack_trial == 0))
ofc_noconflict_df <- create_sig_test_df(ofc_ng_behave_df)

## Cing
# create df for conflict, no conflict trials
cing_conflict_df <- create_sig_test_df(cing_behave_df %>% filter(ghost_attack_trial == 0))
cing_noconflict_df <- create_sig_test_df(cing_ng_behave_df)

## MFG
# create df for conflict, no conflict trials
mfg_conflict_df <- create_sig_test_df(mfg_behave_df %>% filter(ghost_attack_trial == 0))
mfg_noconflict_df <- create_sig_test_df(mfg_ng_behave_df)


```

## Bayesian Linear Mixed Effect Models

```{r conflict-noattack-trials-model, eval = T}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores(), backend = "cmdstanr")

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


## Hippocampus
# Fit the model
hc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = hc_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(hc_model)

# save full model #
save(hc_model, file = path(here(), "results", "app_avd_hc_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_hc_theta_model_noattack_brms.RData"))
summary(hc_model)

## Amygdala
# Fit the model
amyg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = amyg_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(amyg_model)

# save full model #
save(amyg_model, file = path(here(), "results", "app_avd_amyg_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_amyg_theta_model_noattack_brms.RData"))
summary(amyg_model)

## OFC
# Fit the model
ofc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = ofc_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(ofc_model)

# save full model #
save(ofc_model, file = path(here(), "results", "app_avd_ofc_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_ofc_theta_model_noattack_brms.RData"))
summary(ofc_model)

## ACC
# Fit the model
acc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = cing_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(acc_model)

# save full model #
save(acc_model, file = path(here(), "results", "app_avd_acc_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_acc_theta_model_noattack_brms.RData"))
summary(acc_model)

## MFG
# Fit the model
mfg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = mfg_conflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(mfg_model)

# save full model #
save(mfg_model, file = path(here(), "results", "app_avd_mfg_theta_model_noattack_brms.RData"))
load(path(here(), "results", "app_avd_mfg_theta_model_noattack_brms.RData"))
summary(mfg_model)

```

```{r conflict-free-model, eval = T}



# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


## Hippocampus
# Fit the model
hc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = hc_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(hc_model)

# save full model #
save(hc_model, file = path(here(), "results", "app_avd_hc_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_hc_conflictfree_theta_model_brms.RData"))
summary(hc_model)

## Amygdala
# Fit the model
amyg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = amyg_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(amyg_model)

# save full model #
save(amyg_model, file = path(here(), "results", "app_avd_amyg_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_amyg_conflictfree_theta_model_brms.RData"))
summary(amyg_model)

## OFC
# Fit the model
ofc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = ofc_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(ofc_model)

# save full model #
save(ofc_model, file = path(here(), "results", "app_avd_ofc_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_ofc_conflictfree_theta_model_brms.RData"))
summary(ofc_model)

## ACC
# Fit the model
acc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = cing_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(acc_model)

# save full model #
save(acc_model, file = path(here(), "results", "app_avd_acc_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_acc_conflictfree_theta_model_brms.RData"))
summary(acc_model)

## MFG
# Fit the model
mfg_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = mfg_noconflict_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(mfg_model)

# save full model #
save(mfg_model, file = path(here(), "results", "app_avd_mfg_conflictfree_theta_model_brms.RData"))
load(path(here(), "results", "app_avd_mfg_conflictfree_theta_model_brms.RData"))
summary(mfg_model)


```

```{r}


## MFG
## Conflict Model
load(path(here(), "results", "app_avd_mfg_theta_model_brms.RData"))
lower_ci <- summary(mfg_model)$fixed[2, 3]
upper_ci <- summary(mfg_model)$fixed[2, 4]
mfg_conflict_df <- mfg_conflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))
## No Conflict Model
load(path(here(), "results", "app_avd_mfg_conflictfree_theta_model_brms.RData"))
lower_ci <- summary(mfg_model)$fixed[2, 3]
upper_ci <- summary(mfg_model)$fixed[2, 4]
mfg_noconflict_df <- mfg_noconflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## HC
## Conflict Model
load(path(here(), "results", "app_avd_hc_theta_model_brms.RData"))
lower_ci <- summary(hc_model)$fixed[2, 3]
upper_ci <- summary(hc_model)$fixed[2, 4]
hc_conflict_df <- hc_conflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))
## No Conflict Model
load(path(here(), "results", "app_avd_hc_conflictfree_theta_model_brms.RData"))
lower_ci <- summary(hc_model)$fixed[2, 3]
upper_ci <- summary(hc_model)$fixed[2, 4]
hc_noconflict_df <- hc_noconflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## Amygdala
## Conflict Model
load(path(here(), "results", "app_avd_amyg_theta_model_brms.RData"))
lower_ci <- summary(amyg_model)$fixed[2, 3]
upper_ci <- summary(amyg_model)$fixed[2, 4]
amyg_conflict_df <- amyg_conflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))
## No Conflict Model
load(path(here(), "results", "app_avd_amyg_conflictfree_theta_model_brms.RData"))
lower_ci <- summary(amyg_model)$fixed[2, 3]
upper_ci <- summary(amyg_model)$fixed[2, 4]
amyg_noconflict_df <- amyg_noconflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## OFC
## Conflict Model
load(path(here(), "results", "app_avd_ofc_theta_model_brms.RData"))
lower_ci <- summary(ofc_model)$fixed[2, 3]
upper_ci <- summary(ofc_model)$fixed[2, 4]
ofc_conflict_df <- ofc_conflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))
## No Conflict Model
load(path(here(), "results", "app_avd_ofc_conflictfree_theta_model_brms.RData"))
lower_ci <- summary(ofc_model)$fixed[2, 3]
upper_ci <- summary(ofc_model)$fixed[2, 4]
ofc_noconflict_df <- ofc_noconflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## CING
## Conflict Model
load(path(here(), "results", "app_avd_acc_theta_model_brms.RData"))
lower_ci <- summary(acc_model)$fixed[2, 3]
upper_ci <- summary(acc_model)$fixed[2, 4]
cing_conflict_df <- cing_conflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))
## No Conflict Model
load(path(here(), "results", "app_avd_acc_conflictfree_theta_model_brms.RData"))
lower_ci <- summary(acc_model)$fixed[2, 3]
upper_ci <- summary(acc_model)$fixed[2, 4]
cing_noconflict_df <- cing_noconflict_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))


```


## Plotting Results

```{r plotting-functions}

plot_conflict_trials <- function(aac_test_df, roi) {
  
  
 aac_elec_test_df <- aac_test_df %>%
    group_by(elec_id, aac, case) %>%
    mutate(elec_theta = mean(trial_theta)) %>%
    select(-trial_theta, -trial_numeric) %>%
    distinct()
 
 
aac_sub_test_df <-  aac_elec_test_df %>%
    group_by(subject, aac, case) %>%
    mutate(sub_theta = mean(elec_theta)) %>%
    select(-elec_theta, -elec_id) %>%
    distinct()

pval_df <- aac_sub_test_df %>%
    ungroup() %>%
    select(case, pvalue) %>%
    distinct() 
  
  app_av_plot <- aac_sub_test_df %>%
    ggplot(.) +
    geom_jitter(data = aac_elec_test_df, aes(x = aac, fill = aac, y = elec_theta), width = .3, size = .75, alpha = .5, shape = 21, color = "#2D2327") +
    geom_boxplot(aes(x = aac, y = sub_theta, fill = aac), color = "#2D2327", outlier.size = .5) +
    geom_jitter(aes(x = aac, fill = aac, y = sub_theta), color = "#2D2327", alpha = .9, width = .1, size = 1, shape = 17) +
    geom_line(aes(x = aac, y = sub_theta, group = subject), size = .25, alpha = .9, width = .1, color = "#2D2327") +
    theme(panel.background = element_rect(fill = "white")) +
    scale_fill_manual(values = c("#c2383a","#2c75b3")) +
    scale_color_manual(values = c("#c2383a","#2c75b3")) +
    ggsignif::geom_signif(data = pval_df, manual = T, aes(y_position=c(2, 2), xmin= c(1, 1), xmax = c(2, 2), annotations = pvalue),
                family = "Gill Sans", color = "#2D2327", textsize = 3, vjust =-.5) +
    theme(panel.background = element_rect(fill = "white"), 
          legend.position = "none",
          axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
          axis.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
          legend.title = element_text(family = "Gill Sans", color = "#2D2327", size = 9),
          legend.text  = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
          strip.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8, margin = margin()),
          panel.spacing = unit(0, "lines"),
          plot.subtitle = element_text(family = "Gill Sans", color = "#2D2327", size = 4),
          plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 10, hjust = .5)) +
    scale_color_manual(values = c("#c2383a","#2c75b3")) +
    scale_fill_manual(values = c("#c2383a","#2c75b3")) +
    labs(y = "Average theta power (z - score)", x = "", fill = "", color = "") +
    ggtitle(roi, subtitle = "") +
    facet_wrap(~case, ncol = 2) +
    ylim(-1.1, 2.5)
  
  return(app_av_plot)

}


```

## Hippocampus

```{r plot-both-hc, fig.width = 2, fig.height = 2.4, warning = F}

# merge
hc_plot_df <- bind_rows(hc_conflict_df %>% mutate(case = "Conflict"),
                        hc_noconflict_df %>% mutate(case = "Conflict-Free"))


# create plot
hc_plot <- plot_conflict_trials(hc_plot_df, "Hippocampus")

# print plot
hc_plot

# save plot
ggsave(path(here(), "figures", "figure2_hc_app_avoid_combined_theta_plot.png"), plot = hc_plot, width = 2, height = 2.8)

```


## Amygdala

```{r plot-amyg, fig.width = 2, fig.height = 2.7, warning = F}

# merge
amyg_plot_df <- bind_rows(amyg_conflict_df %>% mutate(case = "Conflict"),
                        amyg_noconflict_df %>% mutate(case = "Conflict-Free"))

# create plot
amyg_plot <- plot_conflict_trials(amyg_plot_df, "Amygdala")

# print plot
amyg_plot

# save plot
ggsave(path(here(), "figures", "figure2_amyg_app_avoid_combined_theta_plot.png"), plot = amyg_plot, width = 2, height = 2.8)


```

## OFC


```{r plot-ofc, fig.width = 2, fig.height = 2.7, warning = F}

# merge
ofc_plot_df <- bind_rows(ofc_conflict_df %>% mutate(case = "Conflict"),
                        ofc_noconflict_df %>% mutate(case = "Conflict-Free"))


# create plot
ofc_plot <- plot_conflict_trials(ofc_plot_df, "OFC")


# print plot
ofc_plot

# save plot
ggsave(path(here(), "figures", "figure2_ofc_app_avoid_combined_theta_plot.png"), plot = ofc_plot, width = 2, height = 2.8)


```


## Anterior Cingulate

```{r plot-acc, fig.width = 2, fig.height = 2.7, warning = F}

# merge
cing_plot_df <- bind_rows(cing_conflict_df %>% mutate(case = "Conflict"),
                        cing_noconflict_df %>% mutate(case = "Conflict-Free"))

# create plot
cing_plot <- plot_conflict_trials(cing_plot_df, "ACC")

# print plot
cing_plot

# save plot
ggsave(path(here(), "figures", "figure2_cing_app_avoid_combined_theta_plot.png"), plot = cing_plot, width = 2, height = 2.8)


```


## MFG

```{r plot-mfg, fig.width = 2, fig.height = 2.7, warning = F}

# merge
mfg_plot_df <- bind_rows(mfg_conflict_df %>% mutate(case = "Conflict"),
                        mfg_noconflict_df %>% mutate(case = "Conflict-Free"))

# create plot
mfg_plot <- plot_conflict_trials(mfg_plot_df, "MFG")

# plot it #
mfg_plot

# save plot
ggsave(path(here(), "figures", "figure2_mfg_app_avoid_combined_theta_plot.png"), plot = mfg_plot, width = 2, height = 2.7)


```


