---
title: "Cingulate ~ Theta"
output: html_document
date: "2023-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 5,  # set default width of figures
  fig.height = 8,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(ggeffects)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lmerTest)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(scales)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)



```


# Linear Mixed Effects Models

### Problems with singular fit

Due to unbalanced groups, there are some singular fits. I have looked into this and it is resolved when I use a simpler model with only a random effect of subject. However, it does make sense to have a different intercept for each electrode, since I know they can vary. I looked at it both ways, and it did not change the significance or direction of the fixed effects. Plan going forward is to use the more complex model but to double check it holds in the simpler model. Another thing to checkis if the variance of elec_id:subject is regularly close to 0. That might indicate that while it makes sense each electrode would get its own intercept, it just isn't necessary.


## Data Prep and EDA

```{r load-data}

# ieeg data #
cing_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_cing_all_subs_iti_onset.csv"))

# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_distance_df.csv"))

# combine ghost and no ghost #
all_subs_dist <- all_subs_g_dist %>% 
  select(-GhostLocation, -distance_to_ghost, -min_distance, -cdf_distance)
all_subs_dist <- rbind(all_subs_dist, all_subs_ng_dist)

# add ITI to behavioral df
behavior_iti_df <- all_subs_dist %>% 
  select(subject, trial_numeric, trial_time) %>%
  filter(trial_time < 1) %>%
  mutate(trial_time = round(trial_time - 1, 2))

all_subs_dist <- full_join(all_subs_dist, behavior_iti_df)

```

```{r elec-response, fig.width=20, fig.height=40}

## plot electrode level ERPS ##

avg_cing_theta_data <- cing_theta_data %>%
  rename(theta = theta) %>%
  group_by(trial_time, electrode, subject) %>%
  mutate(mean_elec_theta = mean(theta)) %>%
  ungroup() %>%
  select(-trial_numeric, -theta) %>%
  distinct() 

avg_cing_theta_data %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  ggplot(., aes(x = trial_time, y = mean_elec_theta, color = subject)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~elec_id, ncol = 6) +
  ylim(-1.5, 1.5)

```


```{r subject-overall-response, fig.width= 12, fig.height=12}

## plot subject and combined ERPS ##

avg_cing_theta_data %>%
  group_by(trial_time, subject) %>%
  mutate(mean_theta = mean(mean_elec_theta)) %>%
  ungroup() %>%
  ggplot(., aes(x = trial_time, y = mean_theta, color = subject)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject)

avg_cing_theta_data %>%
  group_by(trial_time, subject) %>%
  mutate(mean_sub_theta = mean(mean_elec_theta)) %>%
  ungroup() %>%
  select(-mean_elec_theta, -electrode) %>%
  distinct() %>%
  group_by(trial_time) %>%
  mutate(mean_theta = mean(mean_sub_theta)) %>%
  ggplot(., aes(x = trial_time, y = mean_theta)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  theme(panel.background = element_rect(fill = "white")) 


```



```{r merge-with-behavior, fig.width= 12, fig.height=12}

# merge behavior data with ieeg data
cing_theta_behave_df <- left_join(all_subs_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               cing_theta_data %>% mutate(trial_time = round(trial_time, 2)))

# validate we get the same ieeg data by comparing with above plots
avg_cing_theta_behave_df <- cing_theta_behave_df %>%
  group_by(trial_time, electrode, subject) %>%
  mutate(mean_elec_theta = mean(theta, na.rm = T)) %>%
  ungroup() %>%
  select(-trial_numeric, -theta) %>%
  distinct() %>%
  group_by(trial_time, subject) %>%
  mutate(mean_sub_theta = mean(mean_elec_theta, na.rm = T)) %>%
  ungroup() %>%
  select(-mean_elec_theta, -electrode) %>%
  distinct() %>%
  group_by(trial_time) %>%
  mutate(mean_theta = mean(mean_sub_theta, na.rm = T))


avg_cing_theta_behave_df %>%
  ggplot(., aes(x = trial_time, y = mean_theta)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  xlim(-1, 5)


```

## Linear Effects Model Results and Plots

## Onset Before Turn

```{r onset-before-turn}


# cing and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_before_turn_model_and_plot("cing", "theta", 
                                all_subs_g_dist, cing_theta_data, 
                                y_low = -8, y_high = 8,
                                plot_title = "Theta does not encode reward and threat values in the Ant. Cingulate at trial onset",
                                rerun_model = TRUE)

# cing and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_before_turn_model_and_plot("cing", "theta", 
                                all_subs_g_dist, cing_theta_data, 
                                plot_title = "Theta does not encode reward and threat values in the Ant. Cingulate at trial onset",
                                y_low = -8, y_high = 8,
                                rerun_model = FALSE)


```


## Approach Only


```{r onset-before-turn}


# cing and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_turnaround_model_and_plot("cing", "theta", 
                                all_subs_g_dist, cing_theta_data, 
                                y_low = -8, y_high = 8,
                                plot_title = "Theta does not encode reward and threat values in the Ant. Cingulate at turnaround",
                                rerun_model = TRUE)

# cing and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_turnaround_model_and_plot("cing", "theta", 
                                all_subs_g_dist, cing_theta_data, 
                                plot_title = "Theta does not encode reward and threat values in the Ant. Cingulate at turnaround",
                                y_low = -8, y_high = 8,
                                rerun_model = FALSE)


```

## Pacman Location

```{r value-model}

# merge behavior data with ieeg data
cing_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               cing_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
cing_theta_lme_df <- cing_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, UserLocation)  %>%
  mutate(UserLocation = rescale(UserLocation))


userloc_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(cing_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- cing_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ UserLocation + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  userloc_results_only <- rbind(userloc_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_userloc <- userloc_results_only %>% mutate(move_time = sort(unique(cing_theta_lme_df$move_time)))
                       

plot <- model_results_userloc %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#65ADC1") +
  geom_line(color = "#65ADC1") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1.2, 1.2) +
  ggtitle("Cing Theta, Pacman Location")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "cing_theta_trial_pacman_location.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```

## Ghost Location

```{r value-model}

# merge behavior data with ieeg data
cing_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               cing_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
cing_theta_lme_df <- cing_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, GhostLocation)  %>%
  mutate(GhostLocation = rescale(GhostLocation))


ghostloc_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(cing_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- cing_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ GhostLocation + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  ghostloc_results_only <- rbind(ghostloc_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_ghostloc <- ghostloc_results_only %>% mutate(move_time = sort(unique(cing_theta_lme_df$move_time)))
                       

plot <- model_results_ghostloc %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#EF7474") +
  geom_line(color = "#EF7474") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 1) +
  ggtitle("Cing Theta, Ghost Location")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "cing_theta_trial_ghost_location.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```




## Combined value

```{r value-model}

# merge behavior data with ieeg data
cing_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               cing_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
cing_theta_lme_df <- cing_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, distance_to_ghost)  %>%
  rowwise() %>%
  mutate(combined_value = points_remaining * distance_to_ghost) %>%
  ungroup() %>%
  mutate(combined_value = rescale(combined_value))


value_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(cing_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- cing_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ combined_value + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  value_results_only <- rbind(value_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_value <- value_results_only %>% mutate(move_time = sort(unique(cing_theta_lme_df$move_time)))
                       

plot <- model_results_value %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#D1B5F4") +
  geom_line(color = "#D1B5F4") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 1) +
  ggtitle("cing Theta, Combined Value")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "cing_theta_trial_combined_value.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```
```{r}

combined_value_df <- all_subs_g_dist %>%
  filter(Direction != "Still") %>%
  select(subject, trial_numeric, trial_time, points_remaining, distance_to_ghost)  %>%
  rowwise() %>%
  mutate(combined_value = points_remaining * distance_to_ghost) %>%
  ungroup() %>%
  mutate(combined_value = rescale(combined_value))

combined_value_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  group_by(trial_time, subject) %>%
  mutate(mean_comb_value = mean(combined_value)) %>%
  ungroup() %>%
  select(trial_time, subject, mean_comb_value) %>%
  distinct() %>%
  ggplot(., aes(x = trial_time, y = mean_comb_value)) +
  geom_point() +
  geom_line() +
  facet_wrap(~subject) +
  xlim(0, 7)


combined_value_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(trial_numeric %in% sample(trial_numeric, 8)) %>%
  ggplot(., aes(x = trial_time, y = combined_value, color = factor(trial_numeric))) +
  geom_point() +
  geom_line() +
  facet_wrap(~subject) +
  xlim(0, 7)


```

```{r}



```




```{r save}

write_csv(model_results_whole_trial, path(here(), "results", "cing_theta_model_results_whole_trial.csv"))
write_csv(model_results, path(here(), "results", "cing_theta_model_results_turnarouns.csv"))
write_csv(model_results_value, path(here(), "results", "cing_theta_model_results_integrated_value.csv"))


```
