---
title: "Cleaning LL14"
output: html_document
date: "2023-12-06"
---

Yikes need to fix!

unique(tmp$ttype_sum)
 [1] 210 192 225 219 216 218 194 222 214 209 223 220 195 217 211 205 207 213 202 206 208 201 197 204 226

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 6,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'create_timelock_event_tables.R'))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)

```

## LL14

```{r LL14-data-load}

LL14_data <- read_csv(path(here(), './data/ieeg_behave/LL14_raw_behave.csv'), col_types = cols(`...1` = col_double(),
                                                                                              Subject = col_character(),
                                                                                              Trial = col_character(),
                                                                                              Lives = col_double(),
                                                                                              Trial_on_off = col_double(),
                                                                                              TrialType = col_double(),
                                                                                              Time = col_double(),
                                                                                              GhostLocation = col_double(),
                                                                                              UserLocation = col_double(),
                                                                                              Direction = col_double(),
                                                                                              Biscuit1 = col_logical(),
                                                                                              Biscuit2 = col_logical(),
                                                                                              Biscuit3 = col_logical(),
                                                                                              Biscuit4 = col_logical(),
                                                                                              Biscuit5 = col_logical(),
                                                                                              Attack = col_logical(),
                                                                                              Chase = col_logical(),
                                                                                              Eaten = col_double(),
                                                                                              Score = col_double()))


```

```{r LL14-data-prep}

# incorrect new trial
LL14_data <- LL14_data %>%
  mutate(Trial = as.numeric(Trial)) %>%
  mutate(Trial = if_else(Trial < 82, Trial, Trial -1)) %>%
  filter(Trial != 121) %>%
  mutate(Trial = if_else(Trial < 121, Trial, Trial -1)) %>%
  mutate(neural_trial_numeric = Trial - 1) %>%
  mutate(Trial = if_else(Trial < 338, Trial, Trial + 3)) %>% # player pressed n to start whole new game/ refreshed or something but new block begins
  mutate(Trial = if_else(Trial < 731, Trial, Trial + 9)) %>% # player pressed n to start whole new game/ refreshed or something but new block begins
  mutate(Trial = as.character(Trial))

# if we start a new block at trial 338 does it fix it?


# clean Biscuits #
LL14_data_clean <- clean_bci_data(LL14_data, 512)

# create distance df #
LL14_data_distance <- create_distance_df_bci(LL14_data_clean)

# task vars df #
LL14_all_vars_df <- get_across_task_variables_bci(LL14_data_clean)

LL14_all_vars_df <- LL14_all_vars_df %>% group_by(block) %>% mutate(ttype_sum = sum(TrialType))
```


```{r}

LL14_all_vars_df %>%
  ggplot(., aes(x = block, y = block_deaths)) +
  geom_point(size = 3) +
  theme(panel.background = element_rect(fill = "white")) +
  ggtitle("Deaths across blocks")


LL14_all_vars_df %>%
  ggplot(., aes(x = block, y = average_dots_per_block)) +
  geom_point(size = 3) +
  theme(panel.background = element_rect(fill = "white"))+
  ggtitle("Dots across blocks")


```


```{r trials-no-biscuits}


LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  group_by(trial_numeric) %>%
  mutate(total_eaten = max(Eaten)) %>%
  filter(total_eaten == 0) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

no_biscuits_trials <- LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  group_by(trial_numeric) %>%
  mutate(total_eaten = max(Eaten)) %>%
  select(trial_numeric, neural_trial_numeric, total_eaten) %>%
  distinct() %>%
  filter(total_eaten == 0) %>%
  # exclude fake trial 0 
  filter(neural_trial_numeric >= 0) %>%
  ungroup() %>%
  pull(neural_trial_numeric)

# possible paused trials


```


```{r how-long-do-trials-last}


LL14_all_vars_df %>%
  ggplot(., aes(x = trial_length)) +
  geom_histogram() +
  geom_vline(xintercept =10) +
  theme(panel.background = element_rect(fill = "white"))



## No long trials




```


```{r compile-bad-trials}


bad_trials <- c(no_biscuits_trials)


```


## all other trials look good (mostly)

It looks like movement get a little "wobbly" towards the end. I haven't seen this before in the data. Is there something happening with dirft in the time window? Could it be a BCI block size thing? Not sure yet will need to watch out for it in the future. Not sure how much it could affect or bias the analysis though, give it would be off by 2 units in position at most with 50ms variability at worst. Not great for the brain but I am not doing an fast temporal precision things as of now. Pulled out a good example of the issue and print it below.

```{r all-other-trials}

# no ghost trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_numeric != 0) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(TrialType > 16) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  ylim(0, 200) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)


# first 100 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric < 100) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  ylim(0, 200) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 100-200 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 100 & trial_numeric < 200) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)


# 200-300 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 200 & trial_numeric < 300) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 300-400 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 300 & trial_numeric < 400) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 400-500 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 400 & trial_numeric < 500) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 500-600 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 500 & trial_numeric < 600) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 600-700 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 600 & trial_numeric < 700) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 700-800 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 300 & trial_numeric < 400) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 800-900 trials
LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 800 & trial_numeric < 900) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

```

```{r more-than-240-trials}


length(unique(LL14_data_clean$trial_numeric))

# omg this poor person
```

```{r custom-time-lockfuncs}

create_last_away_events <- function(df, fname) {
  
  last_away_df <- df %>%
    filter(Trial != "ITI") %>%
    filter(trial_numeric != 0) %>%
    filter(died == 0) %>%
    group_by(neural_trial_numeric) %>%
    mutate(towards_ghost = if_else(Direction == "Left" & starting_side == "Right", "Towards",  # Left:2 Right :11
                                   if_else(Direction == "Right" & starting_side == "Left", "Towards",
                                           if_else(Direction == "Left" & starting_side == "Left", "Away",  # Left:2 Right :11
                                                   if_else(Direction == "Right" & starting_side == "Right", "Away",
                                                           if_else(Direction == "Still", "Still", "Unsure")))))) %>%
    mutate(away_choice_tmp = c(0, diff(factor(towards_ghost)))) %>%
    mutate(away_choice = if_else( (away_choice_tmp == -2 & towards_ghost == "Away") | 
                                    (away_choice_tmp == -1 & towards_ghost == "Away"), sample, 0)) %>%
    select(-away_choice_tmp) %>%
    mutate(number_of_runs = sum(away_choice > 0, na.rm = T)) %>%
    mutate(last_away = if_else(number_of_runs == 0, 0, last(away_choice[away_choice > 0]) )) %>%
    ungroup() %>%
    filter(sample == last_away)
  
  print(anyDuplicated(last_away_df$neural_trial_numeric))
  
  
  last_away_clean_df <- last_away_df %>%
    ungroup() %>%
    mutate(sample_before = 0) %>%
    mutate(event = 1) %>%
    select(neural_trial_numeric, TrialType, sample, sample_before, event)
  
  
  write_csv(last_away_clean_df, paste0(path(here(), './data/ieeg_behave/', fname)))
  
  # diagnostic plots to check it works
  test <- left_join(df, last_away_clean_df %>% select(sample, event))
  
  plot1 <- test %>%
    mutate(event = if_else(event ==1, trial_time, event)) %>%
    filter(Trial != "ITI") %>%
    filter(trial_length <= 10) %>%
    filter(trial_numeric != 0) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    filter(trial_numeric < 100) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_vline(aes(xintercept = event), color = 'black') +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric)
  
  plot2 <- test %>%
    mutate(event = if_else(event ==1, trial_time, event)) %>%
    filter(Trial != "ITI") %>%
    filter(trial_length <= 10) %>%
    filter(trial_numeric != 0) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    filter(trial_numeric > 100 & trial_numeric <=200) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_vline(aes(xintercept = event), color = 'black') +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric)
  
  plot3 <- test %>%
    mutate(event = if_else(event ==1, trial_time, event)) %>%
    filter(Trial != "ITI") %>%
    filter(trial_length <= 10) %>%
    filter(trial_numeric != 0) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    filter(trial_numeric > 200) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_vline(aes(xintercept = event), color = 'black') +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric)
  
  print(plot1)
  print(plot2)
  print(plot3)
}


create_first_dot_events <- function(df, fname) {
  
  first_dot_df <- df %>%
    filter(Trial != "ITI") %>%
    filter(trial_numeric != 0) %>%
    group_by(neural_trial_numeric) %>%
    filter(Biscuit1 == 1111) %>%
    filter(trial_time == min(trial_time)) %>%
    ungroup() %>%
    mutate(sample_before = 0) %>%
    mutate(event = 1) %>%
    select(neural_trial_numeric, TrialType, sample, sample_before, event)
 
  
  print(anyDuplicated(first_dot_df$neural_trial_numeric))
  
  
  first_dot_clean_df <- first_dot_df %>%
    ungroup() %>%
    mutate(sample_before = 0) %>%
    mutate(event = 1) %>%
    select(neural_trial_numeric, TrialType, sample, sample_before, event)
  
  
  write_csv(first_dot_clean_df, paste0(path(here(), './data/ieeg_behave/', fname)))
  
}


create_first_move_events <- function(df, fname) {
  
  first_move_df <- df %>%
    filter(Trial != "ITI") %>%
    filter(trial_numeric != 0) %>%
    group_by(neural_trial_numeric) %>%
    filter(Direction != "Still") %>%
    filter(trial_time == min(trial_time)) %>%
    ungroup() %>%
    mutate(sample_before = 0) %>%
    mutate(event = 1) %>%
    select(neural_trial_numeric, TrialType, sample, sample_before, event)
  
  
  print(anyDuplicated(first_move_df$neural_trial_numeric))
  
  
  first_move_clean_df <- first_move_df %>%
    ungroup() %>%
    mutate(sample_before = 0) %>%
    mutate(event = 1) %>%
    select(neural_trial_numeric, TrialType, sample, sample_before, event)
  
  
  write_csv(first_move_clean_df, paste0(path(here(), './data/ieeg_behave/', fname)))
  
}


create_died_events <- function(df, fname) {
  
  # for Died events, we will time lock to end trial, so we do not need to get event samples. 
  # Instead, we will create a metadata df that we can easily stratify trials where they died or not
  # if ghost last position if across midline of starting side, count as chase, this way we exclude chases that only just began
  # as the person exited the trial
  
 
  died_df <- df %>%
    filter(Trial != "ITI") %>%
    filter(trial_numeric != 0) %>%
    group_by(neural_trial_numeric) %>%
    mutate(Attack = any(Attack))%>%
    mutate(ghost_cross_tmp = if_else(starting_side == "Right" & as.numeric(GhostLocation > 100), 1,
                                     if_else(starting_side == "Left" & as.numeric(GhostLocation < 100), 1, 0))) %>%
    mutate(ghost_cross = sum(ghost_cross_tmp)) %>%
    mutate(Chase = any(Chase)) %>%
    mutate(chase_trial = if_else(TrialType <= 16 & (Chase == TRUE | Attack == TRUE) & died == 0 & ghost_cross > 3, 1, 0)) %>%
    select(neural_trial_numeric, TrialType, died, Attack, chase_trial, trial_length) %>%
    ungroup() %>%
    distinct()
  
  print(anyDuplicated(died_df$neural_trial_numeric))
  
  
  write_csv(died_df, paste0(path(here(), './data/ieeg_behave/', fname)))
  
  # diagnostic plots
  chase_trials <- died_df %>%
    filter(chase_trial == 1) %>%
    pull(neural_trial_numeric)
  attack_trials <- died_df %>%
    filter(died == 1) %>%
    pull(neural_trial_numeric)
  
  plot1 <- df %>%
    filter(Trial != "ITI") %>%
    filter(neural_trial_numeric %in% chase_trials) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric) +
    ggtitle("chase")
  
  plot2 <- df %>%
    filter(Trial != "ITI") %>%
    filter(neural_trial_numeric %in% attack_trials) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric)  +
    ggtitle("attack")
  
  print(plot1)
  print(plot2)
  
  
}



create_attack_events <- function(df, fname) {
  
  # moment of attack when the person was still approaching.
  # includes diagnostic plots to ensure it is working as expected
  
  
  attack_df <- df %>%
    filter(Trial != "ITI") %>%
    filter(trial_numeric != 0) %>%
    filter(TrialType <= 16) %>%
    group_by(neural_trial_numeric) %>%
    # mutate(towards_ghost = if_else(Direction == "Left" & starting_side == "Right", "Towards",  # Left:2 Right :11
    #                                if_else(Direction == "Right" & starting_side == "Left", "Towards",
    #                                        if_else(Direction == "Left" & starting_side == "Left", "Away",  # Left:2 Right :11
    #                                                if_else(Direction == "Right" & starting_side == "Right", "Away",
    #                                                        if_else(Direction == "Still", "Still", "Unsure")))))) %>%
    mutate(dist_to_exit = if_else(starting_side == "Left", UserLocation - 10, 170 - UserLocation)) %>%
    mutate(distance_to_ghost = abs(UserLocation - GhostLocation)) %>%
    filter(Chase == TRUE | Attack == TRUE) %>%
    filter(sample == first(sample)) %>%
    filter(distance_to_ghost <= dist_to_exit) %>%
    ungroup()
  
  print(anyDuplicated(attack_df$neural_trial_numeric))
  
  
  attack_clean_df <- attack_df %>%
    ungroup() %>%
    mutate(sample_before = 0) %>%
    mutate(event = 1) %>%
    select(neural_trial_numeric, TrialType, sample, sample_before, event)
  
  
  write_csv(attack_clean_df, paste0(path(here(), './data/ieeg_behave/', fname)))
  
  # diagnostic plots to check it works
  test <- left_join(df, attack_clean_df %>% select(sample, event))
  
  plot1 <- test %>%
    mutate(event = if_else(event ==1, trial_time, event)) %>%
    filter(Trial != "ITI") %>%
    filter(trial_length <= 10) %>%
    filter(trial_numeric != 0) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    filter(trial_numeric < 100) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_vline(aes(xintercept = event), color = 'black') +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric)
  
  plot2 <- test %>%
    mutate(event = if_else(event ==1, trial_time, event)) %>%
    filter(Trial != "ITI") %>%
    filter(trial_length <= 10) %>%
    filter(trial_numeric != 0) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    filter(trial_numeric > 100 & trial_numeric <=200) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_vline(aes(xintercept = event), color = 'black') +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric)
  
  plot3 <- test %>%
    mutate(event = if_else(event ==1, trial_time, event)) %>%
    filter(Trial != "ITI") %>%
    filter(trial_length <= 10) %>%
    filter(trial_numeric != 0) %>%
    filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
    filter(trial_numeric > 200) %>%
    pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
    ggplot(., aes(x = trial_time, y = location, color = unit)) +
    geom_hline(yintercept = 170, color = "black") +
    geom_hline(yintercept = 10, color = "black") +
    geom_vline(aes(xintercept = event), color = 'black') +
    geom_point() +
    geom_line() +
    theme(panel.background = element_rect(fill = "white")) +
    facet_wrap(~neural_trial_numeric)
  
  print(plot1)
  print(plot2)
  print(plot3)
  
  
}
   

```


```{r save-bad-trials}


bad_trials <- c(no_biscuits_trials, 80)

bad_df <- data_frame("neural_trial_numeric" = bad_trials)

write_csv(bad_df, path(here(), './data/ieeg_behave/LL14_bad_trials.csv'))

```

```{r time-lock-events, fig.width = 24, fig.height = 40}

bad_df <- read_csv(path(here(), './data/ieeg_behave/LL14_bad_trials.csv'))

create_last_away_events(LL14_data_clean, 'LL14_last_away_events.csv')
create_first_dot_events(LL14_data_clean, 'LL14_first_dot_events.csv')
create_first_move_events(LL14_data_clean, 'LL14_first_move_events.csv')
create_died_events(LL14_data_clean, 'LL14_died_events.csv')
create_attack_events(LL14_data_clean, 'LL14_attack_events.csv')



# on 239 they didn't really die
died_events <- read_csv(path(here(), './data/ieeg_behave/LL14_died_events.csv'))
died_events <- died_events %>%
  mutate(died = if_else(neural_trial_numeric == 239, 0, died))
write_csv(died_events, path(here(), './data/ieeg_behave/LL14_died_events.csv'))
```


```{r longest-trial}

# read in bad df
bad_df <- read_csv(path(here(), './data/ieeg_behave/LL14_bad_trials.csv'))


trial_times <- LL14_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_numeric != 0) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  select(trial_length, neural_trial_numeric) %>%
  mutate(tfr_length = trial_length + 3) %>%
  distinct()

write_csv(trial_times, path(here(), './data/ieeg_behave/LL14_trial_times.csv'))

max(trial_times$trial_length)
```

