

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 6,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'create_timelock_event_tables.R'))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)

```

## BJH051

```{r BJH051-data-load}

BJH051_data <- read_csv(path(here(), './data/ieeg_behave/BJH051_raw_behave.csv'), col_types = cols(`...1` = col_double(),
                                                                                              Subject = col_character(),
                                                                                              Trial = col_character(),
                                                                                              Lives = col_double(),
                                                                                              Trial_on_off = col_double(),
                                                                                              TrialType = col_double(),
                                                                                              Time = col_double(),
                                                                                              GhostLocation = col_double(),
                                                                                              UserLocation = col_double(),
                                                                                              Direction = col_double(),
                                                                                              Biscuit1 = col_logical(),
                                                                                              Biscuit2 = col_logical(),
                                                                                              Biscuit3 = col_logical(),
                                                                                              Biscuit4 = col_logical(),
                                                                                              Biscuit5 = col_logical(),
                                                                                              Attack = col_logical(),
                                                                                              Chase = col_logical(),
                                                                                              Eaten = col_double(),
                                                                                              Score = col_double()))


```

```{r BJH051-data-prep}

# clean Biscuits #
BJH051_data_clean <- clean_bci_data(BJH051_data, 2000)

# create distance df #
BJH051_data_distance <- create_distance_df_bci(BJH051_data_clean)

# task vars df #
BJH051_all_vars_df <- get_across_task_variables_bci(BJH051_data_clean)

```


```{r}

BJH051_all_vars_df %>%
  ggplot(., aes(x = block, y = block_deaths)) +
  geom_point(size = 3) +
  theme(panel.background = element_rect(fill = "white")) +
  ggtitle("Deaths across blocks")


BJH051_all_vars_df %>%
  ggplot(., aes(x = block, y = average_dots_per_block)) +
  geom_point(size = 3) +
  theme(panel.background = element_rect(fill = "white"))+
  ggtitle("Dots across blocks")


```


```{r trials-no-biscuits}


BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  group_by(trial_numeric) %>%
  mutate(total_eaten = max(Eaten)) %>%
  filter(total_eaten == 0) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric, scale = "free")

no_biscuits_trials <- BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  group_by(trial_numeric) %>%
  mutate(total_eaten = max(Eaten)) %>%
  select(trial_numeric, total_eaten) %>%
  distinct() %>%
  filter(total_eaten == 0) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  # exclude fake trial 0 
  filter(neural_trial_numeric >= 0) %>%
  ungroup() %>%
  pull(neural_trial_numeric)

# possible paused trials

```


```{r how-long-do-trials-last}


BJH051_all_vars_df %>%
  ggplot(., aes(x = trial_length)) +
  geom_histogram() +
  geom_vline(xintercept =10) +
  theme(panel.background = element_rect(fill = "white"))


long_trials <- BJH051_all_vars_df %>%
  select(trial_numeric, trial_length) %>%
  unique() %>%
  filter(trial_length > 10) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  pull(neural_trial_numeric)

  
BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_numeric != 0) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  filter(neural_trial_numeric %in% long_trials) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  ylim(0, 200) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)


## looks like long trials are no ghost trials where they just waited for a long time.... best to remove




```


```{r compile-bad-trials}


bad_trials <- c(no_biscuits_trials, long_trials)


```


## all other trials look good (mostly)

It looks like movement get a little "wobbly" towards the end. I haven't seen this before in the data. Is there something happening with dirft in the time window? Could it be a BCI block size thing? Not sure yet will need to watch out for it in the future. Not sure how much it could affect or bias the analysis though, give it would be off by 2 units in position at most with 50ms variability at worst. Not great for the brain but I am not doing an fast temporal precision things as of now. Pulled out a good example of the issue and print it below.

```{r all-other-trials, fig.width = 20, fig.height = 25}

# no ghost trials
BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_numeric != 0) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(TrialType > 16) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  ylim(0, 200) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)


# first 100 trials
BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric < 100) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  ylim(0, 200) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)

# 100-200 trials
BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 100 & trial_numeric < 200) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)


# 200-300 trials
BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_length <= 10) %>%
  filter(trial_numeric != 0) %>%
  filter(TrialType <=16) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  filter(!(neural_trial_numeric %in% bad_trials)) %>%
  filter(trial_numeric >= 200 & trial_numeric < 300) %>%
  pivot_longer(cols = c(GhostLocation, UserLocation), values_to = "location", names_to = "unit") %>%
  ggplot(., aes(x = trial_flip, y = location, color = unit)) +
  geom_hline(yintercept = 170, color = "black") +
  geom_hline(yintercept = 10, color = "black") +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~trial_numeric)


```

```{r more-than-240-trials}


length(unique(BJH051_data_clean$trial_numeric))

# nope!
```


```{r save-bad-trials}


bad_trials <- c(no_biscuits_trials, long_trials)

bad_df <- data_frame("neural_trial_numeric" = bad_trials)

write_csv(bad_df, path(here(), './data/ieeg_behave/BJH051_bad_trials.csv'))

```

```{r time-lock-events, fig.width = 16, fig.height = 16}

bad_df <- read_csv(path(here(), './data/ieeg_behave/BJH051_bad_trials.csv'))

create_last_away_events(BJH051_data_clean, 'BJH051_last_away_events.csv')
create_first_dot_events(BJH051_data_clean, 'BJH051_first_dot_events.csv')
create_first_move_events(BJH051_data_clean, 'BJH051_first_move_events.csv')
create_died_events(BJH051_data_clean, 'BJH051_died_events.csv')
create_attack_events(BJH051_data_clean, 'BJH051_attack_events.csv')

```


```{r longest-trial}

# read in bad df
bad_df <- read_csv(path(here(), './data/ieeg_behave/BJH051_bad_trials.csv'))


trial_times <- BJH051_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(trial_numeric != 0) %>%
  mutate(neural_trial_numeric = trial_numeric - 1) %>%
  filter(!(neural_trial_numeric %in% bad_df$neural_trial_numeric)) %>%
  select(trial_length, trial_numeric) %>%
  distinct()

max(trial_times$trial_length)
```

