---
title: "Pacman: LMMs & Visualisations in iEEG sample"
subtitle: "Standardized distance at last turnaround"
author: "Jules"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=F, echo=F}
knitr::opts_chunk$set(
  root.dir =
  echo <- FALSE,
  fig.width <- 8,  
  fig.height <- 4, 
  fig.align <- "center",  
  fig.pos <- "H",  
  cache <- FALSE) 

library(lmerTest)
library(car)
library(merTools) 
library(dplyr)
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr) # devtools::install_github('Mikata-Project/ggthemr')
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(devtools)
library(patchwork)
library(sjPlot)
library(lattice) 
library(Matrix)

```
```{r plotting helpers, include=F, echo=F}
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "blue1", "steelblue4", "#80B1D3", "lightblue", "skyblue2", "#5BBCD6", "dodgerblue2", "darkturquoise", "#8DD3C7",  "#1C8E7A", "#ACCDE9", "#ACCDF9", 
  
  "green1", "green4", "#50A45C", "#78C679",  "palegreen2", "#B3DE69", "#ADDD8E", "#A1D99B", "#C7E9C0","#CCEBC5", "#D9F0A3", 
  
  "gold1",  "#FFFFB3", "yellow4", "yellow3", "khaki2", "darkorange", "#FAC898", "#CC7722", "#FFAC1C", 
  
  "#FF7F00", "#FDBF6F", "#FDB462", "#F3A300", "#FB8072",  "#FB9A99", "orange", "orange3", "#FF5F1F", "#FF7518",
  
  "#E31A1C", "#FF0000", "#FD5372", "deeppink1", "orchid1", "#FCCDE5", "maroon", "pink", "orchid", 
  
  "#6A3D9A", "#BC80BD", "#9986A5", "#CAB2D6", "#BEBADA", "orchid4", "purple2", "orchid3",
  
  "darkorange4", "brown", "black", "grey70","#D9D9D9", "#CCCDE9" 
)
orange <- c("gold1", "darkorange", "#FAC898", "#CC7722", "#FFAC1C", "#FF7F00", "#FDB462", "#F3A300", "#FB8072",  "#FB9A99", "orange", "orange3", "#FF5F1F", "#FF7518", "#FF0000")

pink <- c("#E31A1C", "#FF0000", "#FD5372", "deeppink1", "orchid1", "#FCCDE5", "maroon", "pink", "orchid", 
  "#6A3D9A", "#BC80BD", "#CAB2D6", "orchid4", "purple2", "orchid3")

blue <- c("blue1", "steelblue4", "#80B1D3", "lightblue", "skyblue2", "#5BBCD6", "dodgerblue2", "darkturquoise", "steelblue", "steelblue2", "blue3", "skyblue", "steelblue3", "skyblue3", "dodgerblue", "dodgerblue4")

green <- c("green", "green4", "#50A45C", "#78C679",  "palegreen4", "#B3DE69", "#ADDD8E", "#A1D99B", "#C7E9C0", "#D9F0A3", "#1C8E7A","green3", "darkgreen", "palegreen", "yellow4", "yellow3")

my_theme <- theme_classic() +
  theme(panel.grid.major.y = element_line(colour = "grey70", linewidth = 0.1), axis.ticks = element_blank())

tt_order <- c("3","15","1","13","2","14","4","16","7","11","5","9","6","10","8","12", "17", "18", "19", "20")
color_order <- list("3","15","2","14","7","11","6","10", "17", "18", "19", "20") #numbers = trial type
distance_colors1 <- c("#FCCDE5", "#BC80BD")
distance_colors2 <- c("maroon1", "maroon4")
dot_colors1 <- c("#CCEBC5", "#8DD3C7")
dot_colors2 <- c("skyblue", "skyblue4")
time_colors <- c("khaki2", "#FB9A99")
```
```{r data, include=F, echo=F}
distance_ghost <- read.csv('all_subs_complete_distance_df.csv') 
distance_noghost <- read.csv('all_subs_noghost_complete_distance_df.csv') 
all_data <- read.csv('all_subs_complete_behavior_df.csv')
```
```{r data preparation, include=F, echo=F}
# ghost_mutated includes trials with a ghost present
ghost_mutated <- distance_ghost %>% 
  filter(Trial != 0) %>%
  group_by(subject, trial_numeric) %>%
  mutate(
    initial_score = first(Score),         # score at trial start 
    last_away_flip = ifelse(away_choice == last_away & away_choice != 0, trial_flip, 0), # flag: flip of last_away = away_choice
    last_away_flip = max(last_away_flip), # flag: flip of last_away (=flip number)
    turn_bob_flip = ifelse(last_away_flip == trial_flip & attack_chase_bob == "Bob", 1, 0), # flag: last_away while ghost is bobbing (=1). this means the participant decided to leave the trial before the ghost started chasing / attacking them
    turn_bob_trial = max(turn_bob_flip), # flag: trials with flagged flips
    
    # Recreating ghost movement variable. Necessary in IEEG due to downsampling of data.
    ghost_objective_direction_tmp = c(FALSE, diff(GhostLocation)),
    ghost_objective_direction = if_else(ghost_objective_direction_tmp >= 2, "Right", 
                                if_else(ghost_objective_direction_tmp <= -2, "Left", "still")),
    ghost_direction = if_else((base_start_location < 100 & ghost_objective_direction == "Left") |
                              (base_start_location > 100 & ghost_objective_direction == "Right") , "Towards",
                      if_else(ghost_objective_direction == "still", "still", "Away")),
    new_ghost_direction = ifelse(ghost_direction == "still", NA, ghost_direction)) %>%
  fill(new_ghost_direction, .direction = "downup") %>%
  mutate(ghost_direction = ifelse(is.na(new_ghost_direction), ghost_direction, new_ghost_direction)) %>%
  select(-new_ghost_direction) %>%
  
  mutate(
    # ghost starting direction (ghost movement direction at the beginning of the trial)
    gsd_new = ifelse(trial_flip == 2 & ghost_direction == "Towards", 1, 0), 
    gsd_new = max(gsd_new), 
    gsd_new = ifelse(gsd_new == 1, "towards", "away"),
    former_gsd = ghost_start_dir, 

    trialtype_new = case_when(
      gsd_new == "away" & base_start_location > 100 & reward_groups == 2 ~ 1,
      gsd_new == "away" & base_start_location > 100 & reward_groups == 3 ~ 2,
      gsd_new == "away" & base_start_location > 100 & reward_groups == 1 ~ 3,
      gsd_new == "away" & base_start_location > 100 & reward_groups == 4 ~ 4,
      gsd_new == "towards" & base_start_location < 100 & reward_groups == 2 ~ 5,
      gsd_new == "towards" & base_start_location < 100 & reward_groups == 3 ~ 6,
      gsd_new == "towards" & base_start_location < 100 & reward_groups == 1 ~ 7,
      gsd_new == "towards" & base_start_location < 100 & reward_groups == 4 ~ 8,
      gsd_new == "towards" & base_start_location > 100 & reward_groups == 2 ~ 9,
      gsd_new == "towards" & base_start_location > 100 & reward_groups == 3 ~ 10,
      gsd_new == "towards" & base_start_location > 100 & reward_groups == 1 ~ 11,
      gsd_new == "towards" & base_start_location > 100 & reward_groups == 4 ~ 12,
      gsd_new == "away" & base_start_location < 100 & reward_groups == 2 ~ 13,
      gsd_new == "away" & base_start_location < 100 & reward_groups == 3 ~ 14,
      gsd_new == "away" & base_start_location < 100 & reward_groups == 1 ~ 15,
      gsd_new == "away" & base_start_location < 100 & reward_groups == 4 ~ 16),
    
    tt_color = if_else(as.factor(trialtype_new) %in% color_order, 'odd', 'even')
  ) %>%
  mutate(
    # pacman movement
    first_flip = min(trial_flip),
    trial_flip = (trial_flip - first_flip + 1),
    first_movement_flip = ifelse(move_step != 0, trial_flip, 999), # flag: flips of movement
    first_movement_flip = min(first_movement_flip),                # flag: first flip of movement per trial
    first_movement_time =  ifelse(trial_flip == first_movement_flip, trial_time, 0), 
    first_movement_time = max(first_movement_time), # trial-level
    first_movement_ghost = ifelse(trial_flip == first_movement_flip, ghost_direction, NA), 
    move_step = ifelse(trial_flip == 1, 0, move_step), #repeat for former third trials
    
    # ghost movement
    current_ghost_direction = ghost_direction,
    prev_ghost_direction = lag(ghost_direction),
    ghost_turn = ifelse(is.na(prev_ghost_direction) | prev_ghost_direction == current_ghost_direction, 0, 1),
    ghost_turn_count = cumsum(ghost_turn),
    current_trial_flip = trial_flip,
    
    ghost_comeback_flip = case_when(
    turn_bob_trial == 1 & first_flip == 1 ~ (which.max(ghost_turn_count == 2)-1),
    turn_bob_trial == 1 & first_flip > 1 ~ (which.max(ghost_turn_count == 3)-1),
    turn_bob_trial != 1 ~ NA),
    ghost_comeback_flip = ifelse(ghost_comeback_flip == 0, NA, ghost_comeback_flip),
    ghost_comeback_pos = ifelse(ghost_comeback_flip == current_trial_flip, GhostLocation, 0),
    ghost_comeback_pos = max(ghost_comeback_pos),
    
    first_turnaround_flip = case_when(
    turn_bob_trial == 1 & first_flip == 1~ (which.max(ghost_turn_count == 1)-1),
    turn_bob_trial == 1 & first_flip > 1 ~ (which.max(ghost_turn_count == 2)-1),
    turn_bob_trial != 1 ~ NA),
  
    current_ghost_position = GhostLocation, # check
    first_turnaround_pos = ifelse(first_turnaround_flip == current_trial_flip, GhostLocation, 0),
    first_turnaround_pos = max(first_turnaround_pos),
    ghost_start_pos = ifelse(current_trial_flip ==1, GhostLocation, 0),
    ghost_start_pos = max(ghost_start_pos),
    first_turnaround_distance = ifelse(first_turnaround_pos != 0, abs(first_turnaround_pos - ghost_start_pos), 0),
    bobbing_distance = ifelse(ghost_comeback_pos != 0, abs(first_turnaround_pos - ghost_comeback_pos), NA),
    
    dot5_position = ifelse(current_trial_flip == 1, Biscuit5, 0),
    dot5_position = max(dot5_position),
    ghost_dot5_dis = ifelse(attack_chase_bob == "Bob", abs(current_ghost_position - dot5_position), 999),
    min_dis_ghost_dot5 = min(ghost_dot5_dis),
    min_dis_ghost_dot5 = ifelse(min_dis_ghost_dot5 == 999, NA, min_dis_ghost_dot5),
    overlap_dot5 = ifelse(GhostLocation == dot5_position, "overlap", "no overlap"),
    ) %>% 

  ungroup()

ghost_mutated$last_away.z.beginning <- as.vector(scale(ghost_mutated$last_away)) # last away variable standardized before filters are applied
```
```{r filtering, echo=F}
# mark bad trials for each participant
bad_trials_list <- list(
  participant1 = data.frame(subject = "SLCH002", Trial = c(10,30,51,57,79,92,97,101,126,133,150,167,168,223,224,225)),
  participant2 = data.frame(subject = "LL19", Trial = c(5,9,12,13,21,23,27,30,33,44,46,48,53,57,61,64,67,72,73,78,79,91,93, 110,118,120,122,126,127,131,135,157,158,160,174,187,196,206,218,14,52,151)),    
  participant3 = data.frame(subject = "LL17", Trial = c(16,17,81,83,121,128,132,147,162,173,190,191,223,227,228,235,237,243,245)),    
  participant4 = data.frame(subject = "LL14", Trial = c(3,6,25,35,48,95,179,183,193,198,206,237,255,274,289,337,382,391, 394,406,417,473,486,491,494,526,543,570,634,647,653,681,686,699,712,728,785,797,81)),    
  participant5 = data.frame(subject = "LL13", Trial = c(5,6,7,10,19,22,32,49,59,72,102,118,128,161,171,191,195,201,175,181)),    
  participant6 = data.frame(subject = "LL12", Trial = c(18,40,66,69,89,97,157,247)),    
  participant7 = data.frame(subject = "LL10", Trial = c(28,29,54,82,100,102,103,164,168,228,8)),    
  participant8 = data.frame(subject = "BJH041", Trial = c(2,50,59,73,87,89,111)),    
  participant9 = data.frame(subject = "BJH039", Trial = c(1,2,9,28,100,122,130,160,180,218,13)),    
  participant10 = data.frame(subject = "BJH029", Trial = c(5,12,32,57,136,140,164,223,230)),    
  participant11 = data.frame(subject = "BJH016", Trial = c(34,35,36,71,72,432,433,1,4,7,12,14,25,28,39,40,49,59,61,69,76,84,94, 96,103,108,115,116,118,142,169,185,202,238,248,258,310,323,342,360,366,379,382,386,387,391,407,417,451,452,8,16,32,24,66,81,102,112,392)),    
  participant12 = data.frame(subject = "BJH021", Trial = c(1,2,6,79,82,83,98,104,124,191,209,237,18)),    
  participant13 = data.frame(subject = "BJH025", Trial = c(23,49,63,80,97,99,100,106,167,170,211,232,10,13,6)),    
  participant14 = data.frame(subject = "BJH026", Trial = c(4,151,158,162,171,175,182,196,2,31)),    
  participant15 = data.frame(subject = "BJH027", Trial = c(10,28,34,71,77,78,123,124,149,172,179,180,190,209,211,225,234))
)

# convert the list to a data frame
bad_trials_df <- map_df(bad_trials_list, ~ .x %>%  
                          mutate(subject = subject)) %>%
                select(subject, Trial)

# filter out bad trials
clean_ghost_flips <- ghost_mutated %>% 
  anti_join(bad_trials_df, by = c("subject" = "subject", "Trial" = "Trial"))

rm(bad_trials_list, bad_trials_df, distance_ghost)
```
```{r clean df, echo=F}
clean_distance_data <- clean_ghost_flips %>%
  filter(turn_bob_trial == 1 & dots_eaten > 0 & last_away_flip == trial_flip) # read out at the flip where participant decides to leave the trial 
clean_distance_data$last_away.z.end <- as.vector(scale(clean_distance_data$last_away)) # last away variable standardized after filters are applied

clean_distance_data <- clean_distance_data %>%
  mutate(last_away.z = last_away.z.end)

clean_first_movement <- clean_ghost_flips %>% 
  filter(turn_bob_trial == 1 & dots_eaten > 0 & first_movement_flip == trial_flip) # read out at the flip where pacman moves for the first time
```
<!-- Trial-level variables --> 
```{r trial level variables, include=F, echo=F}
subject_id <- as.factor(gsub("\\D", "", clean_distance_data$subject))
last_away <- clean_distance_data$last_away
last_away.z <- clean_distance_data$last_away.z.end
last_away.z.end <- clean_distance_data$last_away.z.end
last_away.z.beginning <- clean_distance_data$last_away.z.beginning
initial_score <- as.numeric(clean_distance_data$initial_score)
trial <- as.numeric(gsub("\\D", "", clean_distance_data$Trial))
ghost_start_dir <- as.factor(clean_distance_data$gsd_new) 
trialtype <- clean_distance_data$trialtype_new 
dots_eaten <- as.numeric(clean_distance_data$dots_eaten)
lives <- as.numeric(clean_distance_data$Lives)
lives.num.centered <- (lives - 2)  # lives centered with 2 lives = 0 (3 = 1, 0 = -1)
rewardgroups <- clean_distance_data$reward_groups
rewardgroup <- clean_distance_data$reward_groups    # rewardgroup saved as 2 categories
rewardgroup[rewardgroup == 1 | rewardgroup == 2] <- "0"
rewardgroup[rewardgroup == 3 | rewardgroup == 4] <- "1"
last_away_ghost_direction <- as.factor(clean_distance_data$ghost_direction)
starting_side <- as.factor(clean_distance_data$starting_side)
bobbing_distance <- as.numeric(clean_distance_data$bobbing_distance)
first_movement_flip <- as.numeric(clean_first_movement$first_movement_flip)
first_movement_time <- as.numeric(clean_first_movement$first_movement_time)
first_movement_ghost <- (clean_first_movement$first_movement_ghost)
number_runs <- as.numeric(clean_first_movement$number_of_runs)
ghost_comeback_flip <- as.numeric(clean_distance_data$ghost_comeback_flip)
first_turnaround_distance <- as.numeric(clean_distance_data$first_turnaround_distance)
min_dis_ghost_dot5 <- as.numeric(clean_distance_data$min_dis_ghost_dot5)

```
<!-- New data frame with these variables. -->
```{r new data, include=F, echo=F}
new_data <- data.frame(subject_id, trial, trialtype, starting_side, rewardgroups, rewardgroup, last_away, last_away.z,  last_away.z.beginning, last_away.z.end, lives, lives.num.centered, initial_score, ghost_start_dir, dots_eaten, first_movement_flip, first_movement_time, first_movement_ghost, number_runs, ghost_comeback_flip, first_turnaround_distance, bobbing_distance,  last_away_ghost_direction, min_dis_ghost_dot5)

rm(subject_id, trial, rewardgroup, last_away, lives, initial_score, ghost_start_dir, lives.num.centered, trialtype, dots_eaten, first_movement_flip, first_movement_time, first_movement_ghost, number_runs, ghost_comeback_flip, clean_first_movement, last_away_ghost_direction, min_dis_ghost_dot5, starting_side, bobbing_distance, first_turnaround_distance, rewardgroups, last_away.z.beginning, last_away.z.end, last_away.z)

merged_ghost_trial <- new_data %>%
  mutate(
    rewardgroup = if_else(rewardgroup == "1", 'high', 'low'),
    rewardgroup = as.factor(rewardgroup),
    tt_color = if_else(trialtype %in% color_order, 'odd', 'even'))

rm(new_data)
```
<!-- Variance dataset --> 
```{r variance dataset, include=F, message=F, echo=F}
distance_variance_data <- clean_distance_data %>%
  group_by(subject, block) %>% # for each block within each subject
  summarise(dis_b_var = var(last_away.z.end), dis_b_sd = sd(last_away.z.end), dis_b_mean = mean(last_away.z.end)) %>%
  ungroup()
general_variance_data <- clean_distance_data %>%
  group_by(subject) %>% # for each subject
  summarise(dis_sub_var = var(last_away.z.end), dis_sub_mean = mean(last_away.z.end), dis_sub_sd = sd(last_away.z.end)) %>%
  ungroup()
general_variance_data$dis_sample_sd_mean <- mean(general_variance_data$dis_sub_sd) #center dis_tt_sd
general_variance_data$dis_sub_sd_centered <- general_variance_data$dis_sub_sd - general_variance_data$dis_sample_sd_mean

distance_variance_data <- left_join(distance_variance_data, general_variance_data, by = "subject")
rm(general_variance_data)

dots_variance_data <- clean_distance_data %>%
  group_by(subject, block) %>%
  summarise(dot_b_var = var(dots_eaten), dot_b_sd = sd(dots_eaten), dot_b_mean = mean(dots_eaten)) %>%
  ungroup() 
general_variance_data <- clean_distance_data %>%
  group_by(subject) %>%
  summarise(dot_sub_var = var(dots_eaten), dot_sub_mean = mean(dots_eaten), dot_sub_sd = sd(dots_eaten)) %>%
  ungroup()
general_variance_data$dot_sample_sd_mean <- mean(general_variance_data$dot_sub_sd)
general_variance_data$dot_sub_sd_centered <- general_variance_data$dot_sub_sd - general_variance_data$dot_sample_sd_mean
dots_variance_data <- left_join(dots_variance_data, general_variance_data, by = "subject")

variance_data <- left_join(dots_variance_data, distance_variance_data, by = c("subject", "block"))

rm(general_variance_data, distance_variance_data, dots_variance_data) #rm gsd towards
  
```

# Scaling  
  
```{r scaling, echo=F, warning=F, message=F, fig.width=10}
p1 <- ghost_mutated %>%
  select(subject, Trial, last_away) %>%
  distinct() %>%
  ggplot(., aes(x = last_away)) +
    geom_histogram(binwidth = 2, fill = "#FAC898", color="white") + 
    my_theme + theme(legend.position = "none") +
    labs(title = "Last Away before Filters", x = "Last Away", y = "Count")

p2 <- clean_distance_data %>%
  ggplot(., aes(x = last_away)) +
    geom_histogram(binwidth = 2, fill = "lightblue", color="white") + 
    my_theme + theme(legend.position = "none") +
    labs(title = "Last Away after Filters", x = "Last Away", y = "Count")


p3 <- clean_distance_data %>%
  ggplot(., aes(x = last_away.z.beginning)) +
    geom_histogram(binwidth = 0.1, fill = "#FAC898", color="white") + 
    my_theme + theme(legend.position = "none") +
    coord_cartesian(xlim = c(-2.5, 8)) + scale_x_continuous(breaks = seq(-2.5, 7.5, 2.5)) + 
    labs(title = "Z(last_away) calculated before Filters", x = "Z(last_away) pre filter", y = "Count")

p4 <- clean_distance_data %>%
  ggplot(., aes(x = last_away.z.end)) +
    geom_histogram(binwidth = 0.1, fill = "lightblue", color="white") + 
    my_theme + theme(legend.position = "none") +
    coord_cartesian(xlim = c(-2.5, 8)) + scale_x_continuous(breaks = seq(-2.5, 7.5, 2.5)) + 
    labs(title = "Z(last_away) calculated after Filters", x = "Z(last_away) post filter", y = "Count")

p1 + p2
p3 + p4

rm(p1, p2, p3, p4)
```
  
### From now on all z values for last away are calculated after filters
  
# LMM  
- Models perform similarly well    
- Best model: no random slopes, no interaction, lives as a predictor (score not significant)  
    
  
```{r model definitions, include=T, echo=F, warning=F, message=F}
# Extensive Model: best model in other samples 
model.extensive.L <- lmer(last_away.z ~ rewardgroup + ghost_start_dir + lives.num.centered +  (1 +  lives.num.centered|subject_id), data = merged_ghost_trial)
model.RSL <- lmer(last_away.z ~ rewardgroup + ghost_start_dir + (1 +  lives.num.centered|subject_id), data = merged_ghost_trial)
model.IA.RSRG <- lmer(last_away.z ~ rewardgroup*ghost_start_dir + (1 +  rewardgroup|subject_id), data = merged_ghost_trial)
model.IA.noRS <- lmer(last_away.z ~ rewardgroup*ghost_start_dir + (1 |subject_id), data = merged_ghost_trial)
model.noIA.noRS <- lmer(last_away.z ~ rewardgroup + ghost_start_dir + lives.num.centered + (1|subject_id), data = merged_ghost_trial)

anova(model.RSL, model.IA.RSRG, model.IA.noRS, model.extensive.L, model.noIA.noRS)

print("Best Model: no interaction, no random slopes")
summary(model.noIA.noRS)

rm(model.IA.RSRG, model.RSL, model.extensive.L, model.noIA.noRS, model.IA.noRS)
```



  
# Boxplots    
  
  
```{r comparisons across subjects, include=T, fig.width=8, fig.height=5, warning=F}
# last away ~ lives
merged_ghost_trial %>%
  select(lives.num.centered, last_away.z, subject_id, trial) %>%
  distinct() %>%
  ggplot(., aes(x = factor(lives.num.centered), y = last_away.z, fill = factor(lives.num.centered))) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(x = "Lives centered", y = "Distance to Ghost at Turnaround", fill = "lives.num.centered", title = "Turn Around Distance By Number of Lives", subtitle = "")

# last away ~ rewardgroup
merged_ghost_trial %>%
  select(rewardgroup, last_away.z, subject_id, trial) %>%
  distinct() %>%
  ggplot(., aes(x = factor(rewardgroup), y = last_away.z, fill = factor(rewardgroup))) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(x = "Rewardgroup", y = "Distance to Ghost at Turnaround", fill = "Rewardgroup", title = "Turn Around Distance By Rewardgroup", subtitle = "")

# last away ~ GSD
merged_ghost_trial %>%
  select(ghost_start_dir, last_away.z, subject_id, trial) %>%
  distinct() %>%
  ggplot(., aes(x = factor(ghost_start_dir), y = last_away.z, fill = factor(ghost_start_dir))) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(x = "GSD", y = "Distance to Ghost at Turnaround", fill = "GSD", title = "Turn Around Distance By Ghost Starting Direction", subtitle = "")

```
  
# Variability  
  
```{r variance plots, warning=F, fig.width=10, fig.height=10}
# dots eaten per block. most = for most participants, few = for 2 participants that had more trials than the rest
dots_most <- clean_distance_data %>% #using means
  select(subject, block, Trial, dots_eaten) %>%
  distinct() %>%
  filter(subject != "LL14") %>%
  filter(subject != "BJH016") %>%
  ggplot(., aes(x=factor(block), y = dots_eaten, fill=factor(block))) +
  geom_boxplot() +
    facet_wrap(~subject, nrow = 5) +
    my_theme + theme(legend.position = "none") +
    scale_fill_manual(values = orange) +
    labs(x = "Block", y = "Mean (dots)", title = "Dots Eaten by Block")

dots_few <- clean_distance_data %>% #using means
  select(subject, block, Trial, dots_eaten) %>%
  distinct() %>%
  filter(subject == "LL14" | subject == "BJH016") %>%
  ggplot(., aes(x=factor(block), y = dots_eaten, fill=factor(block))) +
  geom_boxplot() +
    facet_wrap(~subject, nrow = 2) +
    my_theme + theme(legend.position = "none") +
    scale_fill_manual(values = c25) +
    labs(x = "Block", y = "Mean (dots)", title = "Dots Eaten by Block")

# subj variability in dots_eaten using means blockwise 
dots_var <- variance_data %>%
  select(subject, block, dot_b_mean) %>%
  distinct() %>%
  ggplot(aes(x = reorder(subject, dot_b_mean), y = dot_b_mean)) + 
  geom_boxplot(fill = "#FDB462") +
    my_theme + theme(legend.position = "none") +
    labs(x = "Subject", y = "Dots Eaten", title = "Dots Eaten by Subject")

# last away per block. most = for most participants, few = for 2 participants that had more trials than the rest
distance_most <- clean_distance_data %>% #using means
  select(subject, block, Trial, last_away.z) %>%
  distinct() %>%
  filter(subject != "LL14") %>%
  filter(subject != "BJH016") %>%
  ggplot(., aes(x=factor(block), y = last_away.z, fill=factor(block))) +
  geom_boxplot() +
    facet_wrap(~subject, nrow = 5) +
    my_theme + theme(legend.position = "none") +
    scale_fill_manual(values = pink) +
    labs(x = "Block", y = "Mean (distance)", title = "Last Away by Block")

distance_few <- clean_distance_data %>% #using means
  select(subject, block, Trial, last_away.z) %>%
  distinct() %>%
  filter(subject == "LL14" | subject == "BJH016") %>%
  ggplot(., aes(x=factor(block), y = last_away.z, fill=factor(block))) +
  geom_boxplot() +
    facet_wrap(~subject, nrow = 2) +
    my_theme + theme(legend.position = "none") +
    scale_fill_manual(values = c25) +
    labs(x = "Block", y = "Mean (distance)", title = "Last Away by Block")

# subj variability in turning distance
dis_var <- clean_distance_data %>% 
  select(Trial, subject, last_away.z) %>%
  distinct() %>%
  ggplot(., aes(x = reorder(subject, last_away.z), y = last_away.z)) +
    #geom_jitter(alpha = .5, color = "grey") + 
    geom_boxplot(notch = T, fill="orchid") +
    ylab("Distance to Ghost at Turnaround") + xlab("Subjects") +
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + my_theme +
    ggtitle("Subject Variability in Turning Distance")

# no deaths. most = for most participants, few = for 2 participants that had more trials than the rest 
death_most <- clean_distance_data %>%
  select(subject, block, Trial, died) %>%
  distinct() %>%
  filter(died == 1) %>%
  filter(subject != "LL14") %>%
  filter(subject != "BJH016") %>%
  ggplot(aes(x = factor(block), fill = factor(block))) +
    facet_wrap(~subject) +
    geom_bar(alpha = 0.7) + my_theme + theme(legend.position = "none") +
    labs(title = "Number of Deaths by Block", x = "Block", y = "Deaths") +
    #scale_fill_brewer(palette = "Set3")  # Optional: customize color palette
    scale_fill_manual(values = c25)


death_few <- clean_distance_data %>% #using means
  select(subject, block, Trial, died) %>%
  distinct() %>%
  filter(died == 1) %>%
  filter(subject == "LL14" | subject == "BJH016") %>%
  ggplot(aes(x = factor(block), fill = factor(block))) +
    facet_wrap(~subject) +
    geom_bar(alpha = 0.7) + my_theme + theme(legend.position = "none") +
    labs(title = "Number of Deaths by Block", x = "Block", y = "Deaths") +
    #scale_fill_brewer(palette = "Set3")  # Optional: customize color palette
    scale_fill_manual(values = c25)
```
```{r dots most, echo=F, fig.width=10, fig.height=10}
dots_most
```
```{r dots few, echo=F, fig.width=10, fig.height=5}
dots_few
dots_var
```
```{r dis most, echo=F, fig.width=10, fig.height=14}
distance_most
```
```{r dis few, echo=F, fig.width=10, fig.height=10}
distance_few
```
```{r dis var, echo=F, fig.width=10, fig.height=5}
dis_var
```
```{r death most, echo=F, fig.width=10, fig.height=6}
death_most
```
```{r death few, echo=F, fig.width=10, fig.height=3}
death_few
rm(dots_most, dots_few, dots_var, distance_most, distance_few, dis_var, death_few, death_most)
```





# Regression    
  
Note: dotted lines = mean of entire sample  
   
``` {r model and model coefficients, echo=F, fig.height=20}
# Split data by subject
subject_data <- split(merged_ghost_trial, merged_ghost_trial$subject_id)

# Define a function to fit the model and return both the coefficients and the model object
fit_lm_and_return_model <- function(subject_df) {
  model <- lm(last_away.z ~ rewardgroup + ghost_start_dir + lives.num.centered, data = subject_df)
  coefficients <- coef(model)
  return(list(coefficients = coefficients, model = model))
}

# Apply the function to each subject's data
model_results <- lapply(subject_data, function(subject_df) {
  subject_id <- unique(subject_df$subject_id)
  result <- fit_lm_and_return_model(subject_df)
  result$subject_id <- subject_id
  return(result)
})

# Extract coefficients into a data frame
coefficients_df <- do.call(rbind, lapply(model_results, function(res) {
  data.frame(subject_id = res$subject_id, t(res$coefficients))
}))

# Rename the columns
colnames(coefficients_df) <- c("subject_id", "Intercept", "rg_low_slope", "gsd_towards_slope", "lives.num.centered_slope")

# Add to ghost trial 
merged_ghost_trial <- merge(merged_ghost_trial, coefficients_df, by = "subject_id")
```
```{r individual regression lines, message=F, include=F}
#coefficients w/o score
model_all <- lm(last_away.z ~ rewardgroup + ghost_start_dir + lives.num.centered, data = merged_ghost_trial)
model_all_coefficients <- coef(model_all)
# intercept <- model_all_coefficients[1]
# rg_low_slope <- model_all_coefficients[2]
# gsd_towards_slope <- model_all_coefficients[3]
# lives_num_centered_slope <- model_all_coefficients[4]
# initial_score <- model_all_coefficients[4]

# lives
lives_ind <- merged_ghost_trial %>%
  select(trial, subject_id, last_away.z, lives.num.centered, Intercept, lives.num.centered_slope) %>%
  distinct() %>%
  ggplot(aes(x = lives.num.centered, y = last_away.z)) + 
    facet_wrap(~subject_id, nrow = 5, scales = "free_y") +  
    geom_point(alpha = .5, color = "grey") +
    my_theme + 
    geom_line(aes(x = lives.num.centered, y = Intercept + lives.num.centered * lives.num.centered_slope),
               color = "orange", linetype = 1, size = 1) +
    # adding the line for the whole sample
    geom_line(aes(x = lives.num.centered, y = model_all_coefficients[1] + lives.num.centered * model_all_coefficients[4]),
               alpha = 0.8, linewidth = 0.4, colour= "black", linetype=2) +
    scale_x_continuous(breaks = seq(-1, 1, 1)) + 
    theme(legend.position = "none")

# rewardgroup
rg.coefficients <- coef(lm(last_away.z ~ rewardgroup, data = merged_ghost_trial))
rewardgroup_ind <- merged_ghost_trial %>%
  select(subject_id, trial, last_away.z, rewardgroup, Intercept, rg_low_slope) %>%
  distinct() %>%
  mutate(rewardgroup.num = ifelse(rewardgroup == "high", 1, 0)) %>%
  ggplot(., aes(x = rewardgroup, y = last_away.z)) +
      facet_wrap(~subject_id, nrow = 5, scales = "free_y") +
      geom_point(alpha = .5, color = "grey") +
      my_theme +
      geom_line(aes(x = (rewardgroup.num + 1), y = Intercept + rewardgroup.num * rg_low_slope),
             color = "palegreen", linetype = 1, size = 1) +
      # adding the line for the whole sample
      geom_line(aes(x = (rewardgroup.num+1), y = model_all_coefficients[1] + rewardgroup.num * model_all_coefficients[2]),
                 alpha = 0.8, linewidth = 0.4, colour= "black", linetype=2) +
      theme(legend.position = "none")

# score not included in model
# score_ind <- merged_ghost_trial %>%
#   select(trial, subject_id, last_away.z, initial_score) %>%
#   distinct() %>%
#   ggplot(., aes(x = initial_score, y = last_away.z)) +
#       facet_wrap(~subject_id, nrow=4) +
#       geom_point(alpha = .3, color = "grey") +
#       my_theme +
#       geom_smooth(linewidth = 0.5, colour= "skyblue", method='lm') +
#       geom_abline(intercept = score.coefficients[1], slope = score.coefficients[2], alpha = 0.8, linewidth = 0.4, colour= "black", linetype=2) +
#       scale_x_continuous(breaks = seq(0, 1500, 500)) +
#       theme(legend.position = "none")

# GSD
gsd_ind <- merged_ghost_trial %>%
  select(trial, subject_id, last_away.z, ghost_start_dir, Intercept, gsd_towards_slope) %>%
  distinct() %>%
  mutate(gsd.num = ifelse(ghost_start_dir == "towards", 1, 0)) %>%
  ggplot(., aes(x = ghost_start_dir, y = last_away.z)) + 
      facet_wrap(~subject_id, nrow = 5, scales = "free_y") +
      geom_point(alpha = .5, color = "grey") +
      my_theme +
      geom_line(aes(x = (gsd.num + 1), y = Intercept + gsd.num * gsd_towards_slope),
             color = "orchid1", linetype = 1, size = 1) +
      # adding the line for the whole sample
      geom_line(aes(x = (gsd.num+1), y = model_all_coefficients[1] + gsd.num * model_all_coefficients[3]),
                 alpha = 0.8, linewidth = 0.4, colour= "black", linetype=2) +
      theme(legend.position = "none")

```
```{r individual regression plots, message=F, fig.width=8, fig.height=8, include=T}
lives_ind
rewardgroup_ind
#score_ind
gsd_ind
rm(lives_ind, rewardgroup_ind, gsd_ind)
```
  
  

# Individual Models    

```{r individual models, echo=F}
# Print the summary for each model
for (result in model_results) {
  cat("Summary for Subject ID:", as.character(result$subject_id), "\n")
  print(summary(result$model))
  cat("\n")
}

```
  
### Grouping:  
  
  
#### No predictor significant:  
21  (GSD 0.085)  
25  (RG 0.052)  
29  
39  
41  (Lives 0.065)  
17  
19
  
  
#### GSD  
26  
27  
13  (Lives 0.087)  
12  (RG)  
  
  
#### RG  
14  
12  (GSD)  
  
  
#### Lives  
2  
  
  
#### All predictors significant  
16  
10  
  
# Individual Movement Plots  
```{r movement plots, echo=F, fig.height=17, fig.width=18}
no_sig <- list("021", "025", "029", "039", "041", "17", "19")

clean <- clean_ghost_flips %>%
  filter(turn_bob_trial == 1 & dots_eaten > 0) %>%
  mutate(subject_id = as.factor(gsub("\\D", "", subject)))
  
subject_data_list <- clean %>%
  filter(subject_id %in% no_sig) %>%
  group_split(subject_id)

# Define the plotting function
plot_subject <- function(subject_data) {
  subject_id <- unique(subject_data$subject_id)
  subject_data %>%
    group_by(trial_numeric) %>%
    filter(trial_numeric %in% sample(trial_numeric, 5)) %>%
    ggplot(aes(x = trial_time)) +  
      facet_wrap(~trial_numeric) +
      geom_line(aes(y = UserLocation), color = "blue") +  
      geom_line(aes(y = GhostLocation), color = "red") +    
      labs(x = "Time", y = "Position", title = paste("Pacman and Ghost Movement Over Time (Subject ID:", subject_id, ")")) +
      my_theme
}

# Create a plot for each subject and store them in a list
plots <- lapply(subject_data_list, plot_subject)

print(plots)


```