---
title: "Pacman LMM Foundation"
author: "Jules"
output: 
  html_document:
    code_folding: hide
---
<!-- Notes:
Hi Anabelle, please let me know if you have any questions regarding the script! (Jules)
-->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/Users/jollyjules/R Programming/Pacman")
library(ggplot2)
library(lmtest)
library(lme4)
library(lmerTest)
library(gridExtra)
library(car)
library(merTools)
library(dplyr)

# game_data <- read.csv('cleaned_pilot_game_data.csv')  # big one, incl. no-ghost & ITI, died 0 & 1, trial_end 0 & 1
distance_data <- read.csv('cleaned_pilot_distance_data.csv')  #cleaned; excl. no-ghost & ITI; trial_end = 0, 
# across_trials_data <- read.csv('cleaned_pilot_across_trial_data.csv') #incl. no-ghost, died 0 & 1, trial end = keine variable
behavior_data <- read.csv('cleaned_pilot_behavior.csv')
```
# Data Preparation
<!--
Create new datasets to work with.
# "small": only reads out necessary variables for specific checks 

# expanded_dataset: 
- bobbing: setting a flag for each flip where last_away occurred while ghost was bobbing (= not triggered by attack or chase), 
  then flagging each trial with a flagged flip
- initial score: adding a trial-level variable of score at the beginning of the trial
- flip of last_away: adding a flip-level variable that saves each flip with turnaround at distance of last_away (pot. multiple per trial)
  then creating a trial-level variable that saves the flip of the last turnaround (one per trial)

# clean_distance_data: 
- excluded: expanded_data: turnaround during a/c, no turns (bc away_choice != 0); distance_data: no ghost present
- exclude no dots eaten
- note: simply define read out at "away_choice == last_away" does not work bc it includes each flip with turn at same distance as last_away
- here: read out at flip of last turn
-->
```{r data preparation, include=FALSE}
#small_data <- distance_data[, c("subject", "Trial", "trial_flip", "Score", "Lives", "Eaten", "dots_eaten", "died", "away_choice", "number_of_runs", "last_away", "attack_chase_bob")]

expanded_dataset <- distance_data %>%
  # flag: last_away while ghost is bobbing (=1)
  mutate(turn_bob_flip = ifelse(away_choice == last_away & away_choice != 0 & attack_chase_bob == "Bob", 1, 0)) %>%
  group_by(subject, trial_numeric) %>%
  mutate(turn_bob_trial = max(turn_bob_flip)) %>% 
  # new variable: score at trial start 
  mutate(initial_score = first(Score)) %>%
  # flag: flip of last_away (=flip number)
  mutate(last_away_flag = ifelse(away_choice == last_away & away_choice != 0, trial_flip, 0)) %>% 
  mutate(last_away_flip = max(last_away_flag)) %>% # 
  ungroup()

# small_expanded <- expanded_dataset[, c("subject", "Trial", "turn_bob_flip", "turn_bob_trial", "last_away_flag","last_away_flip","away_choice", "number_of_runs", "last_away","Score", "initial_score","Lives", "Eaten", "dots_eaten", "died",  "attack_chase_bob")]

clean_distance_data <- expanded_dataset %>%
  filter(turn_bob_trial == 1 & dots_eaten > 0 & last_away_flip == trial_flip) 
```
<!--
## Trial-level variables
Extract the variables of interest for our LMMs.
--> 
```{r trial level variables, include=FALSE}
subject_id <- as.factor(gsub("\\D", "", clean_distance_data$subject)) #changed to factor instead of numeric
last_away <- clean_distance_data$last_away
initial_score <- as.numeric(clean_distance_data$initial_score)
trial <- as.numeric(gsub("\\D", "", clean_distance_data$Trial)) # trials saved as numbers
ghost_start_dir <- as.factor(clean_distance_data$ghost_start_dir)

lives <- as.numeric(clean_distance_data$Lives)
lives.num.centered <- (lives - 2)  # lives centered with 2 lives = 0 (3 = 1, 0 = -1)

rewardgroup <- clean_distance_data$reward_groups    # rewardgroup saved as 2 categories
rewardgroup[rewardgroup == 1 | rewardgroup == 2] <- "0"
rewardgroup[rewardgroup == 3 | rewardgroup == 4] <- "1"

```
<!--
Create new data frame with these variables. Cleanup after.
-->
```{r new data, include=FALSE}
new_data <- data.frame(subject_id, trial, rewardgroup, last_away, lives, lives.num.centered, initial_score, ghost_start_dir)
rm(subject_id, trial, rewardgroup, last_away, lives, lives.num.centered, initial_score, ghost_start_dir)
```
<!-- 
## Subject-level variables
Compute + save anxiety score. Center anxiety variable. Adapt ID name + type and merge anxiety measures with new_data. Remove old data sets.
-->
```{r subject level variables, include=FALSE}
anxiety_data <- behavior_data %>%
  rowwise() %>%
  select(subject, starts_with("O")) %>%
  mutate(across(starts_with("O"), function(x) as.numeric(gsub(" =.*", "", x)))) %>%
  mutate(anxiety_score = O1 + O2 + O3 + O4 + O5) %>%
  ungroup() %>%
  select(subject, anxiety_score) %>%
  distinct()

anxiety_data$anxiety_mean <- mean(anxiety_data$anxiety_score)
anxiety_data$anxiety_centered <- anxiety_data$anxiety_score - mean(anxiety_data$anxiety_score)

names(anxiety_data)[names(anxiety_data) == "subject"] <- "subject_id" 
anxiety_data$subject_id <- as.factor(gsub("\\D", "", anxiety_data$subject_id))

merged_data <- left_join(new_data, anxiety_data, by = "subject_id")
merged_data <- merged_data %>%
  mutate(rewardgroup = if_else(rewardgroup == "1", 'high', 'low')) %>% #merged data 
  mutate(rewardgroup = as.factor(rewardgroup))
rm(anxiety_data, new_data, expanded_dataset, clean_distance_data)
```
    
# Reward Sensitivity  
What's the relationship between distance at last turnaround, reward group (RG), and ghost starting direction (GSD)?   
  
Best reward model: model with ghost, w/o anxiety, w/o interaction RG:GSD, with random slopes for GSD  
  
Learning from this + other reward model versions:  
- anxiety impact v small (0.04), not significant (0.75)  
- GSD: highly significant, larger effect size than RG (2.27 vs 1.19) + random effects explain more variance (1.68 vs 1.32)  
- interaction GSD & RG: significant (p = .0284), effect size 0.8  


```{r reward sensitivity model, include=T}
model.reward <- lmer(last_away ~ rewardgroup + ghost_start_dir + (1 + ghost_start_dir|subject_id), data = merged_data) # best model: 
summary(model.reward)
```
  
# Loss Adaptation   
What's the relationship between distance at last turnaround, score at the beginning of the trial, and number of remaining lives?   
  
Best loss model: model w/o anxiety, w/o score, with RS for lives  
  
Learning from this + other reward model versions:  
- Intercept and lives always show significant, meaningful effect sizes   
- Score, anxiety, interaction effects: never reach significance, effect sizes always close to 0  
- Note: Warning message: predictor variables on different scales    
  
```{r loss adaptation model}
model.loss <- lmer(last_away ~ lives.num.centered + (1 + lives.num.centered|subject_id), data = merged_data)
summary(model.loss)
```
  
## Comparison: Reward vs Loss model  
Note: Models aren't nested.  
  
Results:  
- the reward model shows lower AIC & BIC values (AIC ∆24, BIC ∆17) 
--> the reward model fits better  
  
```{r comparison reward sensitivity vs loss adaptation}
anova(model.reward, model.loss)
```

# Extensive Model: Merging Loss & Reward Models
  
Model Comparison:  
- model improves by including random slopes for GSD or Lives (not for RG, slightly for GSD, more for Lives, RS for both fails to converge)  
- best model: with GSD, with RS for lives
- adding anxiety to best model: fails to converge. w/o random slopes: slightly worse (AIC ∆24, BIC ∆17)  
  
  
```{r extensive model}
model.extensive <- lmer(last_away ~ rewardgroup + lives.num.centered + ghost_start_dir + (1 +  lives.num.centered|subject_id), data = merged_data)
summary(model.extensive)
```
