---
title: "Aalen Modeling"
output: html_document
date: '2022-07-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 5,  # set default width of figures
  fig.height <- 8,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(lubridate)
library(ranger)
library(ggfortify)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))

## plotting helpers ##
ggthemr("solarized")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)

```

## Load Pacman data ##

```{r load-data}
# game data #
pilot_game_data <- read_csv(path(here(), '../behavioral_parsing/prolific_data_clean/cleaned_pacman_200_trial_n69.csv'), col_types = cols(X1 = col_double(),
                                                                                              subject = col_character(),
                                                                                              Trial = col_character(),
                                                                                              Lives = col_double(),
                                                                                              TrialType = col_double(),
                                                                                              Time = col_double(),
                                                                                              GhostLocation = col_double(),
                                                                                              UserLocation = col_double(),
                                                                                              Direction = col_double(),
                                                                                              Biscuit1 = col_logical(),
                                                                                              Biscuit2 = col_logical(),
                                                                                              Biscuit3 = col_logical(),
                                                                                              Biscuit4 = col_logical(),
                                                                                              Biscuit5 = col_logical(),
                                                                                              Attack = col_logical(),
                                                                                              Chase = col_logical(),
                                                                                              Eaten = col_double(),
                                                                                              Score = col_double(),
                                                                                              final_score = col_double()))

# behavioral data#
pilot_behave_data <- read_csv(path(here(), '../behavioral_parsing/prolific_data_clean/cleaned_behave_data_200_trial_n69.csv'), col_types = cols())

# metadata / IDs #
pacman_ids <- read_csv(path(here(), '../behavioral_parsing/prolific_data_clean/cleaned_ids_200_trial_n69.csv'))

# merge with ids to confirm parsing worked #
pilot_behave_data_clean <- merge.data.frame(pilot_behave_data, pacman_ids, by = c("subject", "ID"))

```

## Prep behavioral data


```{r beahvioral-prep, echo = F}


## IMPORTANT NOTES ##
# subject 84 and trial 48 somehow managed to press before trial began-- manually need to change startlocation to 63 and starting direction
# subject 70 on trial 127 also pressed, true start was 57


## 11 is to the right
## 2 is to the left

# clean data #
pilot_game_data_clean <- clean_data_for_aalen(pilot_game_data)


# create distance df #
pilot_game_data_distance <- create_distance_prolific(pilot_game_data_clean)




```


```{r prep-df-surival}

survival_df_49_downsampled <- pilot_game_data_distance %>%
  filter(last_away != 0) %>% # filter out times person ran into the ghost
  filter(subject == "Subject_49") %>%
  group_by(trial_numeric) %>%
  filter(trial_time <= trial_time[away_choice == last_away]) %>%
  mutate(trial_time = round(trial_time/.25)*.25) %>%
  mutate(survival_time = max(trial_time)) %>%
  mutate(time1 = round(trial_time, digits = 2)) %>%
  mutate(time2 = c(time1[2:n()], time1[n()] + .25)) %>%
  mutate(dif = time2 - time1) %>%
  mutate(status = if_else(survival_time ==trial_time, 1, 0 )) %>%
  mutate(censor = 1)  %>%
  select(subject, trial_numeric, survival_time, min_distance, status, reward_groups, censor,
         distance_to_ghost, jittered_start_location, Eaten, Score, Lives, Direction, time1, time2, dif, number_of_runs) %>%
  distinct()


survival_df_49 <- create_subject_survival_aalen(pilot_game_data_distance, "Subject_49")
survival_df_52 <- create_subject_survival_aalen(pilot_game_data_distance, "Subject_52")
survival_df_12 <- create_subject_survival_aalen(pilot_game_data_distance, "Subject_12")


```


```{r general-surv-curve}
# sanity check survival curve
survival_df_49 %>%
  ggplot(., aes(x= time1)) +
  geom_histogram(alpha = .5, binwidth = .05, aes(y = 100 *(..count..)/length(unique(survival_df_49$trial_numeric)))) +
  ylab("Percent of Trials") +
  theme(panel.background = element_rect(fill = "white")) 


# also using aalen models
basic_aalen_fit_49 <- survfit(Surv(time1, time2, status) ~  1, data=survival_df_49, type = "fleming-harrington")
basic_aalen_fit_52 <- survfit(Surv(time1, time2, status) ~  1, data=survival_df_52, type = "fleming-harrington")
basic_aalen_fit_12 <- survfit(Surv(time1, time2, status) ~  1, data=survival_df_12, type = "fleming-harrington")

ggsurvplot(basic_aalen_fit_49)
ggsurvplot(basic_aalen_fit_52)
ggsurvplot(basic_aalen_fit_12)

```


```{r aalen-regression}
library(timereg)

aalen_null_model_49 <- aareg(Surv( time1, time2, status) ~ Direction,
              data=survival_df_49)

aalen_timereg_model_49 <- timereg::aalen(Surv( time1, time2, status) ~  
              distance_to_ghost + Eaten + const(reward_groups) + const(Score) + const(Lives) +
              const(jittered_start_location) + const(Direction),
              data=survival_df_49)

aareg_full_model_49 <- aareg(Surv( time1, time2, status) ~  
              distance_to_ghost + discounted_reward + Score + Lives +
              jittered_start_location + Direction,
              data=survival_df_49)

aalen_full_model_52 <- aareg(Surv( time1, time2, status) ~  
              distance_to_ghost + discounted_reward + Score + Lives +
              jittered_start_location + Direction,
              data=survival_df_52)


aalen_full_model_12 <- aareg(Surv( time1, time2, status) ~  
              distance_to_ghost + discounted_reward + Score + Lives +
              jittered_start_location + Direction,
              data=survival_df_12)




# regression table
aalen_null_model_49 %>%
  broom::tidy() %>%
  mutate(p_sig = p.value < .05) %>%
  kable() %>%
  kable_styling()

aareg_full_model_49 %>%
  broom::tidy() %>%
  mutate(p_sig = p.value < .05) %>%
  kable() %>%
  kable_styling()

aalen_full_model_52 %>%
  broom::tidy() %>%
  mutate(p_sig = p.value < .05) %>%
  kable() %>%
  kable_styling()

aalen_full_model_12 %>%
  broom::tidy() %>%
  mutate(p_sig = p.value < .05) %>%
  kable() %>%
  kable_styling()

# plot beta coefficients
autoplot(aalen_null_model_49) +
  theme(panel.background = element_rect(fill = "white"))

autoplot(aareg_full_model_49) +
  theme(panel.background = element_rect(fill = "white"))

autoplot(aalen_full_model_12) +
  theme(panel.background = element_rect(fill = "white"))

# plot beta coefficients
autoplot(aalen_full_model_52) +
  theme(panel.background = element_rect(fill = "white"))

# plot beta coefficients
autoplot(aalen_full_model_12) +
  theme(panel.background = element_rect(fill = "white"))





```

```{r prediction}

survival_df_49_short <- survival_df_49 %>%
  select(trial_numeric, time1, time2, status, cdf_distance, Direction, Eaten, points_remaining, jittered_start_location, Lives, reward_groups, Score) %>%
  mutate(points_remaining_alt = scale(points_remaining)) %>%
  ungroup()

survival_df <- survival_df_49_short

aalen_model_49 <- timereg::aalen(Surv( time1, time2, status) ~  
                                cdf_distance + 
                                jittered_start_location + points_remaining_alt,
                                residuals = 1, data=survival_df,resample.iid=1, max.time = 4.2)

summary(aalen_model_49)

pred <- timereg::predict.timereg(object = aalen_model_49, newdata = survival_df)

plot(pred,multiple=1,se=1,uniform=0)

df <- data_frame(pred$S0)

dim(pred$S0)

# for loop across df to predict everything at each time point 
# count everyone who has turned before each point
# here look at predicted vs not



aalen_model_49
```



```{r aalen-model-assumptions}

plot(aalen_model_49)

resids<-cum.residuals(aalen_model_49,survival_df,cum.resid=1)

plot(resids, score=2, robust =1, conf.band = T)

summary(resids)


```

```{r alt-approach}

survival_df_49_short <- survival_df_49_downsampled %>%
  select(trial_numeric, time1, time2, status, cdf_distance, Direction, Eaten, points_aquired,
         points_remaining, jittered_start_location, Lives, reward_groups, Score) %>%
  mutate(points_remaining_alt = c(scale(points_remaining))) %>%
  ungroup() %>%
  group_by(time1, time2) %>%
  mutate(num_events = sum(status))

aareg_full_model_49 <- aareg(Surv( time1, time2, status) ~  
              distance_to_ghost_bin + points_aquired + reward_groups + Score + Lives +
              jittered_start_location + Direction,
              data=survival_df_49_downsampled)

aareg_full_model_49 %>%
  broom::tidy() %>%
  mutate(p_sig = p.value < .05) %>%
  kable() %>%
  kable_styling()

survival_df_49_short %>%
  ggplot(., aes(x = time2, y = num_events)) +
  geom_jitter(alpha = .5) +
  theme(panel.background = element_rect(fill = "white")) +
  scale_x_continuous(breaks = seq(0, 6, .25))


single_time_point <- survival_df_49_short %>%
  filter(time2 == 2.75)


model1 <- glm(status ~ cdf_distance  + Direction + jittered_start_location + reward_groups + Lives, data = single_time_point, family = 'binomial')
summary(model1)


```



## Meeting

I have data that looks like it should be appropriate for survival analysis. Time to turn around in a game of pacman. There is no censoring. 

I want to know, are the variables that I think are important actually important. And can I tell if some subjects care less about some aspects than others, ie some are more motivated by reward, others are very sensitive to how close they are to the ghost. 

Ming suggest survival analysis, but doesn't have much experience. I started with cox-proportional hazard models, but my data don't meet the proportional hazard assumption. 

I looked next looked at Aalen models, but struggled to find many practical walk throughs. I have played around with both the timereg package, and the aareg function from the survival package. Basically, I can fit the models okay, but I am not 100% sure if I am meeting model assumptions. With timereg, I can't re predict my data, because it the prediction function doesn't accept data in the interval format. Also, the martingale residuals look funky for at least some of the variables. I can keep playing with the form of my predictors, but I want to make sure I am on the right track... Meanwhile, the survival package seems to be all about cox proportional hazard models, with aalen mostly as checks for the cox proportional hazard. 

I signed up for the course to basically try to find any resources and as an excuse to talk to you about it. 



glmnet

discerete super learners

helen rijtgaard survival , time depdent vars gerds helen is first author

highly depth of lasso

intensity of a counting process can still be modeled to e the power link function

cox.ph

hal9001 , poision link in the right way





