---
title: "Approach vs Avoidance Synchrony"
output: html_document
date: "2024-05-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 5,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(JMbayes2)
library(caret)
library(rmarkdown)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "clean_behavioral_data.R"))
source(path(here(), "R", "create_distance_df.R"))
source(path(here(), "R", "joint_modeling_functions.R"))
source(path(here(), "R", "jm_visualization_functions.R"))
source(path(here(), "R", "connectivity_prep_functions.R"))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# # ## parallelization ##
# nCores <- 8
# registerDoParallel(nCores)


```

## Approach vs Avoidance Synchrony

The rodent literature predicts that exposure to anxiogenic environments enhances vHPC-mPFC theta synchrony. One possible way of testing this is whether or not synchrony changes when they are approaching vs avoiding. However, this is not an ideal test, because close tot he ghost while they are turned around may still count as anxiogenic. Still, we see some limited evidence that synchrony is higher during approach near the ghost, particularly when they are around 700ms away from the ghost-- where you would expect to see the biggest difference. 

However, we do a difference when we only look at the succesful escape. In that context, there is higher synchrony during approach than avoidance.


### All Connectivity Data

```{r load-data}
## load data ##
conn_df <- read_csv(path(here(), "data_mount", "remote", "pacman", "connectivity", "ieeg", "imcoh_ppc_pli", "combined_escape_connectivity.csv"))


## FDr correct/make symmetric
conn_clean_df <- prep_conn_allsubs_plot_df(conn_df)


## set colors ##
roi_colors <-  c("Amygdala" = "#DE4A4D", "Hippocampus" = "#FFA602", "OFC" =  "#88D1A3", "Ant. Cingulate"=  "#3D99BA", "Insula" =  "#876194", "dlPFC" = "#FB6087")

```


```{r create-sig-df, fig.width=20, fig.height=15}

sig_electrodes <- conn_clean_df %>%
  filter(time >= -2 & time <= 2) %>%
  group_by(subject, pairs, roi_pair, metric) %>%
  mutate(sig_time_bins = sum(sig)) %>%
  ungroup %>%
  filter(sig_time_bins > 10) %>%
  select(subject, pairs, roi_pair, metric) %>%
  distinct() %>%
  mutate(sig_key = paste0(subject, pairs, roi_pair, metric)) %>%
  pull(sig_key)


conn_clean_sig_elec_df <- conn_clean_df %>%
  filter(time >= -2 & time <= 2) %>%
  mutate(key = paste0(subject, pairs, roi_pair, metric)) %>%
  filter(key %in% sig_electrodes) %>%
  mutate(time = round(time, 1)) %>%
  group_by(metric, time, pairs, roi_pair, subject) %>%
  mutate(connectivity = mean(abs(connectivity))) %>%
  ungroup() %>%
  select(-pairs, -pval, -p_frd, -sig, -percent_sig, -count_sig, -number_of_region_pairs) %>%
  distinct()


```


```{r hc-ofc-model}

hc_ofc_avg_conn_df <- conn_clean_sig_elec_df %>%
  filter(first_region == "Hippocampus") %>%
  filter(second_region == "OFC") %>%
  filter(time >= -1 & time <= 1) %>%
  mutate(case = if_else(time <= 0, "approach", "avoidance")) %>%
  distinct() %>%
  group_by(key, case) %>%
  mutate(average_conn = mean(connectivity)) %>%
  select(key, subject, roi_pair, metric, case, average_conn) %>%
  distinct()


hc_ofc_avg_conn_df %>%
  ggplot(., aes(x = case, y = log(average_conn))) +
  geom_boxplot() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject)


```


## Successgul Escape Only



### All Connectivity Data

```{r load-data}
## load data ##
conn_df <- read_csv(path(here(), "data_mount", "remote", "pacman", "connectivity", "ieeg", "imcoh_ppc_pli", "combined_connectivity.csv"))


## FDr correct/make symmetric
conn_clean_df <- prep_conn_allsubs_plot_df(conn_df)


## set colors ##
roi_colors <-  c("Amygdala" = "#DE4A4D", "Hippocampus" = "#FFA602", "OFC" =  "#88D1A3", "Ant. Cingulate"=  "#3D99BA", "Insula" =  "#876194", "dlPFC" = "#FB6087")

```


```{r create-sig-df, fig.width=20, fig.height=15}

sig_electrodes <- conn_clean_df %>%
  filter(time >= -2 & time <= 2) %>%
  group_by(subject, pairs, roi_pair, metric) %>%
  mutate(sig_time_bins = sum(sig)) %>%
  ungroup %>%
  filter(sig_time_bins > 10) %>%
  select(subject, pairs, roi_pair, metric) %>%
  distinct() %>%
  mutate(sig_key = paste0(subject, pairs, roi_pair, metric)) %>%
  pull(sig_key)


conn_clean_sig_elec_df <- conn_clean_df %>%
  filter(time >= -2 & time <= 2) %>%
  mutate(key = paste0(subject, pairs, roi_pair, metric)) %>%
  filter(key %in% sig_electrodes) %>%
  mutate(time = round(time, 1)) %>%
  group_by(metric, time, pairs, roi_pair, subject) %>%
  mutate(connectivity = mean(abs(connectivity))) %>%
  ungroup() %>%
  select(-pairs, -pval, -p_frd, -sig, -percent_sig, -count_sig, -number_of_region_pairs) %>%
  distinct()


```


```{r hc-ofc-model}

hc_ofc_avg_conn_df <- conn_clean_sig_elec_df %>%
  filter(first_region == "Hippocampus") %>%
  filter(second_region == "OFC") %>%
  filter(time >= -1 & time <= 1) %>%
  mutate(case = if_else(time <= 0, "approach", "avoidance")) %>%
  distinct() %>%
  group_by(key, case) %>%
  mutate(average_conn = mean(connectivity)) %>%
  select(key, subject, roi_pair, metric, case, average_conn) %>%
  distinct()


hc_ofc_avg_conn_df %>%
  ggplot(., aes(x = case, y = log(average_conn))) +
  geom_boxplot() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject)


```



```{r run-models}

## Imaginary Coherence
hc_ofc_imcoh_conn_df <- hc_ofc_avg_conn_df %>%
  filter(metric == "Imaginary Coherence") %>%
  select(-metric) %>%
  mutate(imcoh = log(average_conn))

imcoh_model <- lmer(imcoh ~ case + (1|subject:key), data = hc_ofc_imcoh_conn_df)
summary(imcoh_model)

## PPC
hc_ofc_ppc_conn_df <- hc_ofc_avg_conn_df %>%
  filter(metric == "Pairwise Phase Consistency") %>%
  select(-metric) %>%
  mutate(ppc = log(average_conn))

ppc_model <- lmer(ppc ~ case + (1|subject:key), data = hc_ofc_ppc_conn_df)
summary(ppc_model)


## PLI
hc_ofc_pli_conn_df <- hc_ofc_avg_conn_df %>%
  filter(metric == "Phase Lag Index") %>%
  select(-metric) %>%
  mutate(pli = log(average_conn))

pli_model <- lmer(pli ~ case + (1|subject:key), data = hc_ofc_pli_conn_df)
summary(pli_model)

```

```{r hc-ofc-time-model}


hc_ofc_conn_df <- conn_clean_sig_elec_df %>%
  filter(first_region == "Hippocampus") %>%
  filter(second_region == "OFC") %>%
  mutate(case = if_else(time <= 0, "approach", "avoidance")) %>%
  distinct()

for(time_step in unique(abs(hc_ofc_conn_df$time))){
  print(time_step)
  time_df <- hc_ofc_conn_df %>%
    mutate(time = abs(time)) %>%
    filter(time == time_step) %>%
    filter(metric == "Imaginary Coherence") %>%
    select(-metric) %>%
    mutate(imcoh = log(connectivity))
  
  imcoh_model <- lmer(imcoh ~ case + (1|subject), data = time_df)
  print(summary(imcoh_model))


}

```

```{r hc-ofc-time-model}


for(time_step in unique(abs(hc_ofc_conn_df$time))){
  print(time_step)
  time_df <- hc_ofc_conn_df %>%
    mutate(time = abs(time)) %>%
    filter(time == time_step) %>%
    filter(metric == "Pairwise Phase Consistency") %>%
    select(-metric) %>%
    mutate(ppc = log(connectivity))
  
  ppc_model <- lmer(ppc ~ case + (1|subject), data = time_df)
  print(summary(ppc_model))


}

```


```{r hc-ofc-time-model}


for(time_step in unique(abs(hc_ofc_conn_df$time))){
  print(time_step)
  time_df <- hc_ofc_conn_df %>%
    mutate(time = abs(time)) %>%
    filter(time == time_step) %>%
    filter(metric == "Phase Lag Index") %>%
    select(-metric) %>%
    mutate(pli = log(connectivity))
  
  pli_model <- lmer(pli ~ case + (1|subject), data = time_df)
  print(summary(pli_model))


}

```