---
title: "Rising Connectivity - Imaginary Coherence"
output: html_document
date: "2024-06-02"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 8,  # set default width of figures
  fig.height = 5,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)
library(JMbayes2)
library(caret)
library(rmarkdown)
library(blme)
library(brms)
library(bayesplot)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", "clean_behavioral_data.R"))
source(path(here(), "R", "create_distance_df.R"))
source(path(here(), "R", "joint_modeling_functions.R"))
source(path(here(), "R", "jm_visualization_functions.R"))
source(path(here(), "R", "connectivity_prep_functions.R"))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# # ## parallelization ##
# nCores <- 8
# registerDoParallel(nCores)


```

## Theta Coherence Dynamics During Approach & Avoidnance (Imaginary Coherence)


This script tests two hypotheses and visualizes the results. The first hypothesis is that theta coherence increases during the approach period, specifically during the 1.5 seconds before the turnaround. The second hypothesis is that theta coherence falls during avoidance, specifically in the 1.5 seconds after the turnaround. 

I use brms to fit these models because of the detailed random effect structure. The general model for both periods is:

`scaled_log_connectivity ~ time+ (1 + time | subject/key)`

Finally, I visualize both these results for SFN 2024. 


```{r load-data}
## load data ##
conn_df <- read_csv(path(here(), "data_mount", "remote", "pacman", "connectivity", "ieeg", "imcoh_ppc_pli", "combined_ghost_connectivity_newsubs.csv"))


## set colors ##
roi_colors <-  c("Amygdala" = "#DE4A4D", "Hippocampus" = "#FFA602", "OFC" =  "#88D1A3", "Ant. Cingulate"=  "#3D99BA", "Insula" =  "#876194", "MFG" = "#FB6087", "SFG" = "#FB9A99")

```


```{r split-mfg-sfg}

## split the dlpfc electrodes into MFG and SFG ##

regions_df <- read_csv(path(here(), "munge", "mni_coordinates_all_subs_with_detailed_regions.csv"))

mfg_df <- regions_df %>%
  filter(region == "mfg") %>%
  mutate(elec_id = paste0(subject, "_", Electrode))

sfg_df <- regions_df %>%
  filter(region == "sfg") %>%
  mutate(elec_id = paste0(subject, "_", Electrode))

conn_detailed_df <- conn_df %>%
  mutate(
    first_pair = gsub("_to_.*", "", pairs),
    second_pair = gsub(".*_to_", "", pairs),
    first_pair_1 = gsub("-.*", "", first_pair),
    first_pair_2 = gsub(".*-", "", first_pair),
    second_pair_1 = gsub("-.*", "", second_pair),
    second_pair_2 = gsub(".*-", "", second_pair),
  ) %>%
  mutate(
    detailed_first_region = if_else(
        first_region == "dlpfc" &
        paste0(subject, "_", first_pair_1) %in% mfg_df$elec_id |
        paste0(subject, "_", first_pair_2) %in%  mfg_df$elec_id,
      "mfg",
      if_else(
          first_region == "dlpfc" &
          paste0(subject, "_", first_pair_1) %in% sfg_df$elec_id |
          paste0(subject, "_", first_pair_2) %in%  sfg_df$elec_id,
      "sfg",
      first_region
      )),
    detailed_second_region = if_else(
          second_region == "dlpfc" &
          paste0(subject, "_", second_pair_1) %in% mfg_df$elec_id |
          paste0(subject, "_", second_pair_2) %in%  mfg_df$elec_id,
      "mfg",
      if_else(
          second_region == "dlpfc" &
          paste0(subject, "_", second_pair_1) %in% sfg_df$elec_id |
          paste0(subject, "_", second_pair_2) %in%  sfg_df$elec_id,
      "sfg",
      second_region
      )
     )
    )


## Check that everything worked correctly
table(conn_detailed_df$detailed_first_region)
table(conn_detailed_df$detailed_second_region)

# final rename
conn_detailed_df <- conn_detailed_df %>%
  mutate(first_region = detailed_first_region, 
         second_region = detailed_second_region)

```




```{r load-behvaioral-data}

## load the behavioral data to see the min and average turn times ##

# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))

# combine ghost and no ghost #
all_subs_dist <- all_subs_g_dist %>% 
  select(colnames(all_subs_ng_dist))
all_subs_dist <- rbind(all_subs_dist, all_subs_ng_dist)

# read in data already merged with ieeg to get the good ieeg trials
hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))
used_trials <- hc_theta_data %>%
  mutate(subject_trial = paste0(subject, "_", trial_numeric)) %>%
  pull(subject_trial) %>%
  unique()

## create turn df ##
turn_df <- all_subs_dist %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # exclude time before they started moving, may be good to look at not doing this as well
  # filiter out ITI & trials with 0 dots
  filter(reward_groups != 99 & dots_eaten > 0) %>%
  group_by(trial_numeric, subject) %>%
  # filter time so that trials end when the person turnaround for the final time
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  mutate(turnaround_time = if_else(event == 1 & Eaten != 0, trial_time, 0)) %>%
  mutate(turnaround_time = max(turnaround_time)) %>%
  filter(turnaround_time != 0) %>%
  mutate(turn_time = trial_time - turnaround_time) %>%
  ungroup() %>%
  select(subject, trial_numeric, turnaround_time, turn_time) %>%
  distinct() %>%
  mutate(time = round(turn_time, 1)) %>%
  select(-turn_time) %>%
  mutate(subject_trial = paste0(subject, "_", trial_numeric)) %>%
  filter(subject_trial %in% used_trials)

print(min(turn_df$turnaround_time))
print(mean(turn_df$turnaround_time))

```



### Approach Dynamics

```{r create-sig-df, fig.width=20, fig.height=15}

# only use sig electrodes based on full dataset
sig_df <- read_csv(path(here(), "results", "sig_theta_pairs.csv"))

# pull the sig electrode key ##
sig_electrodes <- sig_df %>%
  mutate(sig_key = paste0(subject, pairs, metric)) %>%
  pull(sig_key)

```


```{r create-approach-df}

## create the approach df ##

avd_time_window <- 2
app_time_window <- -2

app_sig_elec_df <- conn_detailed_df %>%
  mutate(roi_pair = paste0(first_region, "_", second_region)) %>%
  filter(time >= app_time_window & time <= 0) %>%
  mutate(key = paste0(subject, pairs, metric)) %>%
  filter(key %in% sig_electrodes) %>%
  mutate(time = round(time, 1)) %>%
  group_by(key, time) %>%
  mutate(connectivity = mean(abs(connectivity))) %>%
  select(-percent_sig) %>%
  distinct() %>%
  # get rid of unused regions
  filter(!grepl("sfg", roi_pair)) %>%
  filter(!grepl("insula", roi_pair)) %>%
  filter(first_region != second_region) %>%
  ## unify roi names
  mutate(
    roi_pair = case_when(
      grepl("ofc", roi_pair) & grepl("hc", roi_pair) ~ "ofc_hc",
      grepl("ofc", roi_pair) & grepl("amyg", roi_pair) ~ "ofc_amyg",
      grepl("ofc", roi_pair) & grepl("mfg", roi_pair) ~ "ofc_mfg",
      grepl("ofc", roi_pair) & grepl("cing", roi_pair) ~ "ofc_cing",
      grepl("hc", roi_pair) & grepl("amyg", roi_pair) ~ "hc_amyg",
      grepl("hc", roi_pair) & grepl("mfg", roi_pair) ~ "hc_mfg",
      grepl("hc", roi_pair) & grepl("cing", roi_pair) ~ "hc_cing",
      grepl("amyg", roi_pair) & grepl("mfg", roi_pair) ~ "amyg_mfg",
      grepl("amyg", roi_pair) & grepl("cing", roi_pair) ~ "amyg_cing",
      grepl("mfg", roi_pair) & grepl("cing", roi_pair) ~ "mfg_cing"
    ))

app_sig_avg_elec_df <- app_sig_elec_df %>%
  group_by(metric, time, roi_pair, subject) %>%
  mutate(average_sub_conn = mean(abs(connectivity))) %>%
  ungroup() %>%
  select(-pairs, -connectivity) %>%
  distinct()

imcoh_app_sig_df <- app_sig_elec_df %>%
  ungroup() %>%
  filter(metric == "Imaginary Coherence") %>%
  mutate(scaled_log_connectivity = scale(log(connectivity))[,1]) %>%
  select(subject, time, scaled_log_connectivity, connectivity, pairs, first_pair, second_pair, roi_pair, first_region, second_region, key) %>%
  distinct()


```

```{r imcoh-app-eda, fig.width = 10, fig.height = 5, eval = F}

## do some basic approach df EDA ##




```

```{r approach-model}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


# Fit the model
rising_model <- brm(
  formula = scaled_log_connectivity ~ time+ (1 + time | subject/key),
  data = imcoh_app_sig_df,
  prior = priors,
  family = gaussian(),
  iter = 7000,
  warmup = 3000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


# save rising model #
save(rising_model, file = path(here(), "results", paste0(avd_time_window, "_rising_model_brms.RData")))

# load rising model #
load(path(here(), "results", paste0(avd_time_window, "_rising_model_brms.RData")))

# summary #
summary(rising_model)

```
```{r}

plot(rising_model)


```

```{r approach-model}

## create the approach df ##

avd_time_window <- 1.7
app_time_window <- -1.7

app_sig_elec_df <- conn_detailed_df %>%
  mutate(roi_pair = paste0(first_region, "_", second_region)) %>%
  filter(time >= app_time_window & time <= 0) %>%
  mutate(key = paste0(subject, pairs, metric)) %>%
  filter(key %in% sig_electrodes) %>%
  mutate(time = round(time, 1)) %>%
  group_by(key, time) %>%
  mutate(connectivity = mean(abs(connectivity))) %>%
  select(-percent_sig) %>%
  distinct() %>%
  # get rid of unused regions
  filter(!grepl("sfg", roi_pair)) %>%
  filter(!grepl("insula", roi_pair)) %>%
  filter(first_region != second_region) %>%
  ## unify roi names
  mutate(
    roi_pair = case_when(
      grepl("ofc", roi_pair) & grepl("hc", roi_pair) ~ "ofc_hc",
      grepl("ofc", roi_pair) & grepl("amyg", roi_pair) ~ "ofc_amyg",
      grepl("ofc", roi_pair) & grepl("mfg", roi_pair) ~ "ofc_mfg",
      grepl("ofc", roi_pair) & grepl("cing", roi_pair) ~ "ofc_cing",
      grepl("hc", roi_pair) & grepl("amyg", roi_pair) ~ "hc_amyg",
      grepl("hc", roi_pair) & grepl("mfg", roi_pair) ~ "hc_mfg",
      grepl("hc", roi_pair) & grepl("cing", roi_pair) ~ "hc_cing",
      grepl("amyg", roi_pair) & grepl("mfg", roi_pair) ~ "amyg_mfg",
      grepl("amyg", roi_pair) & grepl("cing", roi_pair) ~ "amyg_cing",
      grepl("mfg", roi_pair) & grepl("cing", roi_pair) ~ "mfg_cing"
    ))

app_sig_avg_elec_df <- app_sig_elec_df %>%
  group_by(metric, time, roi_pair, subject) %>%
  mutate(average_sub_conn = mean(abs(connectivity))) %>%
  ungroup() %>%
  select(-pairs, -connectivity) %>%
  distinct()

imcoh_app_sig_df <- app_sig_elec_df %>%
  ungroup() %>%
  filter(metric == "Imaginary Coherence") %>%
  mutate(scaled_log_connectivity = scale(log(connectivity))[,1]) %>%
  select(subject, time, scaled_log_connectivity, connectivity, pairs, first_pair, second_pair, roi_pair, first_region, second_region, key) %>%
  distinct()



# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


# Fit the model
rising_model <- brm(
  formula = scaled_log_connectivity ~ time+ (1 + time | subject/key),
  data = imcoh_app_sig_df,
  prior = priors,
  family = gaussian(),
  iter = 7000,
  warmup = 3000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


# save rising model #
save(rising_model, file = path(here(), "results", paste0(avd_time_window, "_rising_model_brms.RData")))

# load rising model #
load(path(here(), "results", paste0(avd_time_window, "_rising_model_brms.RData")))

# summary #
summary(rising_model)

```

```{r app-model-posterior, fig.width = 8, fig.height = 5}


mcmc_areas(rising_model, regex_pars = c("b_")) + theme(panel.background = element_rect(fill = "white"))


```


#### Region Specific

```{r rising-model-roi, eval = F}


# Fit the model
roi_rising_model <- brm(
  formula = scaled_log_connectivity ~ time*roi_pair + (1 + time | subject/key),
  data = imcoh_app_sig_df,
  prior = priors,
  family = gaussian(),
  iter = 5000,
  warmup = 2000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


# save rising model #
save(roi_rising_model, file = path(here(), "results", "roirising_model_brms.RData"))

# load rising model #
load(path(here(), "results", "roirising_model_brms.RData"))

# summary #
summary(roi_rising_model)

```

```{r rising-roi-posterior-summary, eval = F}

# For each region pair
roi_pairs <- unique(roi_rising_model$data$roi_pair)

# values to find CI intervals in the density function
closest_value <- function(x, v) {
  # Calculate the absolute differences between each element in v and x
  differences <- abs(v - x)
  
  # Find the index of the minimum difference
  index_of_min <- which.min(differences)
  
  # Return the value in v at the index of the minimum difference
  closest <- v[index_of_min]
  return(closest)
}

# Function to summarize posterior samples
summarize_posterior <- function(samples) {
  mean_val <- mean(samples)
  sd_val <- sd(samples)
  ci_lower <- quantile(samples, 0.025)
  ci_upper <- quantile(samples, 0.975)
  max_density = max(density(samples)$y)
  ci_lower_dens = density(samples)$y[density(samples)$x == closest_value(ci_lower, density(samples)$x)]
  ci_upper_dens = density(samples)$y[density(samples)$x == closest_value(ci_upper, density(samples)$x)]
  prob_positive <- mean(samples > 0)
  tibble(
    Mean = mean_val,
    SD = sd_val,
    CI_Lower = ci_lower,
    CI_Upper = ci_upper,
    Max_Density = max_density,
    CI_Lower_Density = ci_lower_dens,
    CI_Upper_Density = ci_upper_dens,
    Prob_Positive = prob_positive
  )
}

# Function to extract sample for each region pair
get_samples_for_region <- function(region) {
  if (region == "amyg_cing") {
    slope <- as_draws_df(roi_rising_model)$b_time
  } else {
    interaction_term <- paste0("b_time:roi_pair", region)
    slope <- as_draws_df(roi_rising_model)$b_time + as_draws_df(roi_rising_model)[[interaction_term]]
  }
}

# Function to extract slopes for each region pair
get_slope_for_region <- function(region) {
  if (region == "amyg_cing") {
    slope <- as_draws_df(roi_rising_model)$b_time
  } else {
    interaction_term <- paste0("b_time:roi_pair", region)
    slope <- as_draws_df(roi_rising_model)$b_time + as_draws_df(roi_rising_model)[[interaction_term]]
  }
  summarize_posterior(slope)
}

# get all samples #
full_sample <-  lapply(roi_pairs, get_samples_for_region)
names(full_sample) <- roi_pairs
full_sample_df <- as_tibble(full_sample)

# Summarize slopes for all region pairs
slopes_summary <- lapply(roi_pairs, get_slope_for_region)
names(slopes_summary) <- roi_pairs

# Combine summaries into a data frame
slopes_summary_df <- bind_rows(slopes_summary, .id = "roi_pair")

```


### Avoidance Dynamics

```{r create-sig-df, fig.width=20, fig.height=15}


 avd_sig_elec_df <- conn_detailed_df %>%
   mutate(roi_pair = paste0(first_region, "_", second_region)) %>%
  filter(time >= 0 & time <= avd_time_window) %>%
  mutate(key = paste0(subject, pairs, metric)) %>%
  filter(key %in% sig_electrodes) %>%
  mutate(time = round(time, 1)) %>%
  group_by(key, time) %>%
  mutate(connectivity = mean(abs(connectivity))) %>%
  select(-percent_sig) %>%
  distinct() %>%
  # get rid of unused regions
  filter(!grepl("sfg", roi_pair)) %>%
  filter(!grepl("insula", roi_pair)) %>%
  filter(first_region != second_region) %>%
  ## unify roi names
  mutate(
    roi_pair = case_when(
      grepl("ofc", roi_pair) & grepl("hc", roi_pair) ~ "ofc_hc",
      grepl("ofc", roi_pair) & grepl("amyg", roi_pair) ~ "ofc_amyg",
      grepl("ofc", roi_pair) & grepl("mfg", roi_pair) ~ "ofc_mfg",
      grepl("ofc", roi_pair) & grepl("cing", roi_pair) ~ "ofc_cing",
      grepl("hc", roi_pair) & grepl("amyg", roi_pair) ~ "hc_amyg",
      grepl("hc", roi_pair) & grepl("mfg", roi_pair) ~ "hc_mfg",
      grepl("hc", roi_pair) & grepl("cing", roi_pair) ~ "hc_cing",
      grepl("amyg", roi_pair) & grepl("mfg", roi_pair) ~ "amyg_mfg",
      grepl("amyg", roi_pair) & grepl("cing", roi_pair) ~ "amyg_cing",
      grepl("mfg", roi_pair) & grepl("cing", roi_pair) ~ "mfg_cing"
    ))


avd_sig_avg_elec_df <- avd_sig_elec_df %>%
  group_by(metric, time, roi_pair, subject) %>%
  mutate(average_sub_conn = mean(abs(connectivity))) %>%
  ungroup() %>%
  select(-pairs, -connectivity) %>%
  distinct()

```




```{r svg-sub-roi, fig.width = 10, fig.height = 8}

imcoh_avd_sig_df <- avd_sig_elec_df %>%
  ungroup() %>%
  filter(metric == "Imaginary Coherence") %>%
  mutate(scaled_log_connectivity = scale(log(connectivity))[,1]) %>%
  select(subject, time, scaled_log_connectivity, connectivity, pairs, first_pair, second_pair, roi_pair, first_region, second_region, key) %>%
  distinct()

imcoh_avd_sig_df %>%
  ggplot(., aes(x = scaled_log_connectivity)) +
  geom_density() +
  theme(panel.background = element_rect(fill = "white")) 

imcoh_avd_sig_df %>%
  ggplot(., aes(x = time, y = scaled_log_connectivity)) +
  geom_point(alpha = .1) +
  geom_smooth(method = "lm", color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject, scales = "free_y") 


imcoh_avd_sig_df %>%
  ggplot(., aes(x = time, y = scaled_log_connectivity)) +
  geom_point(alpha = .1) +
  geom_smooth(method = "lm", color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~roi_pair, scales = "free_y") 


```

```{r avoidance-model}


# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


# Fit the model
falling_model <- brm(
  formula = scaled_log_connectivity ~ time+ (1 + time | subject/key),
  data = imcoh_avd_sig_df,
  prior = priors,
  family = gaussian(),
  iter = 5000,
  warmup = 2000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


# save falling model #
save(falling_model, file = path(here(), "results",  
                                paste0(avd_time_window, "_falling_model_brms.RData")))

# load rising model #
load(path(here(), "results",  paste0(avd_time_window, "_falling_model_brms.RData")))

# summary #
summary(falling_model)

```


```{r app-model-posterior, fig.width = 8, fig.height = 5, eval = F}


mcmc_areas(falling_model, regex_pars = c("b_")) + theme(panel.background = element_rect(fill = "white"))


```


```{r app-model-posterior, fig.width = 8, fig.height = 5, eval = F}


ppc_dens_overlay(y = imcoh_app_sig_df$scaled_log_connectivity,
                 yrep =  posterior_predict(rising_model, draws = 50))


```

```{r app-model-diagnostics, fig.width = 20, fig.height = 5, eval = F}


mcmc_trace(rising_model, regex_pars = c("b_"), facet_args = list(ncol = 1))


```


#### Region Specific -- falling

```{r falling-model-roi}

# Fit the model
roi_falling_model <- brm(
  formula = scaled_log_connectivity ~ time*roi_pair + (1 + time | subject/key),
  data = imcoh_avd_sig_df,
  prior = priors,
  family = gaussian(),
  iter = 6000,
  warmup = 3000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


# save falling model #
save(roi_falling_model, file = path(here(), "results", "roifalling_model_brms.RData"))

# load falling model #
load(path(here(), "results", "roifalling_model_brms.RData"))

# summary #
summary(roi_falling_model)

```

```{r summarize-posterior-roi-falling}

# For each region pair
roi_pairs <- unique(roi_rising_model$data$roi_pair)

# values to find CI intervals in the density function
closest_value <- function(x, v) {
  # Calculate the absolute differences between each element in v and x
  differences <- abs(v - x)
  
  # Find the index of the minimum difference
  index_of_min <- which.min(differences)
  
  # Return the value in v at the index of the minimum difference
  closest <- v[index_of_min]
  return(closest)
}

# Function to summarize posterior samples
summarize_posterior <- function(samples) {
  mean_val <- mean(samples)
  sd_val <- sd(samples)
  ci_lower <- quantile(samples, 0.025)
  ci_upper <- quantile(samples, 0.975)
  max_density = max(density(samples)$y)
  ci_lower_dens = density(samples)$y[density(samples)$x == closest_value(ci_lower, density(samples)$x)]
  ci_upper_dens = density(samples)$y[density(samples)$x == closest_value(ci_upper, density(samples)$x)]
  prob_positive <- mean(samples > 0)
  tibble(
    Mean = mean_val,
    SD = sd_val,
    CI_Lower = ci_lower,
    CI_Upper = ci_upper,
    Max_Density = max_density,
    CI_Lower_Density = ci_lower_dens,
    CI_Upper_Density = ci_upper_dens,
    Prob_Positive = prob_positive
  )
}

# Function to extract sample for each region pair
get_samples_for_region <- function(region) {
  if (region == "amyg_cing") {
    slope <- as_draws_df(roi_rising_model)$b_time
  } else {
    interaction_term <- paste0("b_time:roi_pair", region)
    slope <- as_draws_df(roi_rising_model)$b_time + as_draws_df(roi_rising_model)[[interaction_term]]
  }
}

# Function to extract slopes for each region pair
get_slope_for_region <- function(region) {
  if (region == "amyg_cing") {
    slope <- as_draws_df(roi_rising_model)$b_time
  } else {
    interaction_term <- paste0("b_time:roi_pair", region)
    slope <- as_draws_df(roi_rising_model)$b_time + as_draws_df(roi_rising_model)[[interaction_term]]
  }
  summarize_posterior(slope)
}

# get all samples #
full_sample <-  lapply(roi_pairs, get_samples_for_region)
names(full_sample) <- roi_pairs
full_sample_df <- as_tibble(full_sample)

# Summarize slopes for all region pairs
slopes_summary <- lapply(roi_pairs, get_slope_for_region)
names(slopes_summary) <- roi_pairs

# Combine summaries into a data frame
slopes_summary_df <- bind_rows(slopes_summary, .id = "roi_pair")

```

## Plotting Results


```{r plots, fig.width = 20, fig.height = 5, eval = F}

# prep dfs averaged across electrodes within subejcts and roi pairs
imcoh_app_sig_avg_df <- app_sig_avg_elec_df %>%
  filter(metric == "Imaginary Coherence") %>%
  select(subject, time, average_sub_conn, roi_pair, first_region, second_region) %>%
  distinct()

imcoh_avd_sig_avg_df <- avd_sig_avg_elec_df %>%
  filter(metric == "Imaginary Coherence") %>%
  select(subject, time, average_sub_conn, roi_pair, first_region, second_region) %>%
  distinct()


# plot #
imcoh_app_sig_avg_df %>%
  ggplot(., aes(x = time, y = log(average_sub_conn))) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject, scales = "free_y", nrow = 1) +
  ggtitle("Approach")


imcoh_avd_sig_avg_df %>%
  ggplot(., aes(x = time, y = log(average_sub_conn))) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject, scales = "free_y", nrow = 1) +
  ggtitle("Avoid")



```


```{r paper-plot, fig.width = 1.5, fig.height = 2.75, eval = F}

# merge app and avd dfs #
imcoh_sig_avg_df <- bind_rows(imcoh_avd_sig_avg_df %>% mutate(case = "Avoid"), 
                              imcoh_app_sig_avg_df %>% mutate(case = "Approach"))

# take the absolute value of time #
indv_imcoh_sig_avg_plot_df <- imcoh_sig_avg_df %>%
  mutate(plot_time = abs(time))


# plot #
imcoh_sig_ex_app_plot <- indv_imcoh_sig_avg_plot_df %>%
  filter(case == "Approach" & subject == "BJH016") %>%
  ggplot(., aes(x = time, y = log(average_sub_conn))) +
  geom_jitter(alpha = .5, size = 2, color = "#D75356") +
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  theme(panel.background = element_rect(fill = "white"), 
    legend.position = "none",
    axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
    axis.title =  element_text(family = "Gill Sans", color = "#2D2327", size = 11),
    plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 11, hjust = .5, face = 'plain')) +
  labs(color = "", fill = "", y = "Imaginary Coherence, log-scaled", x = "App. Time (s)") +
  ggtitle("Approach")

imcoh_sig_ex_app_plot

# save #
ggsave(path(here(), "figures", "connectivity", "fig3_example_sub_approach.png"), 
       plot = imcoh_sig_ex_app_plot, 
       width = 1.5, height = 3, units = "in", dpi = 600)


```


```{r paper-plot, fig.width = 1, fig.height = 3, eval = F}

# plot #
imcoh_sig_ex_avd_plot <- indv_imcoh_sig_avg_plot_df %>%
  filter(case == "Avoid" & subject == "BJH016") %>%
  ggplot(., aes(x = time, y = log(average_sub_conn))) +
  geom_jitter(alpha = .5, size = 2, color = "#6390C8") +
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  scale_y_continuous(position = 'right') +
  theme(panel.background = element_rect(fill = "white"), 
    legend.position = "none",
    axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
    axis.title =  element_text(family = "Gill Sans", color = "#2D2327", size = 11),
    plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 11, hjust = .5, face = 'plain')) +
  labs(color = "", fill = "", y = "Imaginary Coherence, log-scaled", x = " Avd. Time (s)") +
  ggtitle("Avoid")

imcoh_sig_ex_avd_plot

# save #
ggsave(path(here(), "figures", "connectivity", "fig3_example_sub_avoid.png"), 
       plot = imcoh_sig_ex_avd_plot, 
       width = 1.5, height = 3, units = "in", dpi = 600)


```



## SFN PLots

```{r sfn-plot-indv, fig.width = 12, fig.height = 15, eval = F}
ggthemr("solarized")

# merge app and avd dfs #
imcoh_sig_avg_df <- bind_rows(imcoh_avd_sig_avg_df %>% mutate(case = "Avoid"), 
                              imcoh_app_sig_avg_df %>% mutate(case = "Approach"))

# take the absolute value of time #
indv_imcoh_sig_avg_plot_df <- imcoh_sig_avg_df %>%
  mutate(plot_time = abs(time))

# plot #
indv_imcoh_sig_avg_plot <- indv_imcoh_sig_avg_plot_df %>%
  ggplot(., aes(x = time, y = log(average_sub_conn), color = case, fill = case)) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", color = "black") +
    theme(panel.background = element_rect(fill = "white"), 
      legend.position = "top",
      axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 16),
      axis.title = element_text(family = "Gill Sans", color = "#2D2327", size = 19),
      legend.title = element_text(family = "Gill Sans", color = "#2D2327", size = 18),
      legend.text  = element_text(family = "Gill Sans", color = "#2D2327", size = 17),
      strip.text = element_text(family = "Gill Sans", color = "#2D2327", size = 18),
      plot.subtitle = element_text(family = "Gill Sans", color = "#2D2327", size = 18),
      plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 20)) +
  labs(color = "", fill = "", y = "Subject and Region Pair Average Connectivity, Logged ", x = "Time from Turnaround") +
  facet_wrap(~subject, scales = "free_y", nrow = 3) +
  ggtitle("Theta Coherence Rises During Approach and Falls During Avoidance", subtitle = "Signficiance assessed using bayesian linear mixed effects models of imaginary coherence")

# save #
ggsave(path(here(), "figures", "connectivity", "rising_falling_indv_plot.png"), 
       plot = indv_imcoh_sig_avg_plot, 
       width = 12, height = 13, units = "in", dpi = 300)


```


```{r sfn-plot, fig.width =4.75, fig.height = 7.5, eval = F}
ggthemr("solarized")

# take the absolute value of time #
imcoh_sig_avg_plot_df <- imcoh_sig_avg_df %>%
  filter(!grepl("insula", roi_pair)) %>%
  mutate(plot_time = abs(time)) %>%
  group_by(time, roi_pair) %>%
  mutate(average_conn = mean(average_sub_conn)) 

# plot #
imcoh_sig_avg_plot <- imcoh_sig_avg_df %>%
  ggplot(., aes(x = time, y = log(average_sub_conn), color = case, fill = case)) +
  geom_jitter(alpha = .5) +
  geom_smooth(method = "lm", color = "black") +
  geom_text(aes(x = -.8, y = -1.2), label = "App. Coherence ~ Time:\n0.13 95%CI [0.08 - 0.18]", color = "#2D2327", size = 5, family = "Gill Sans", check_overlap = T) +
  geom_text(aes(x = .8, y = -5.7), label = "Avd. Coherence ~ Time:\n-0.14 95%CI [-0.23 - -0.04]", color = "#2D2327", size = 5, family = "Gill Sans", check_overlap = T) +
    theme(panel.background = element_rect(fill = "white"), 
      legend.position = "right",
      axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 16),
      axis.title =  element_blank(),
      plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 20, hjust = .5, face = 'plain')) +
  labs(color = "", fill = "", y = "", x = "") +
  ggtitle("Across All Subjects")

imcoh_sig_avg_plot

# save #
ggsave(path(here(), "figures", "connectivity", "rising_falling_plot.png"), 
       plot = imcoh_sig_avg_plot, 
       width = 4.75, height = 7.5, units = "in", dpi = 300)


```

