---
title: "Normative Gameplay on the Pacman Task from Pilot Data"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo <- FALSE,  # don't print the code chunk
  warning <- FALSE,  # don't print warnings
  message <- FALSE,  # don't print messages
  fig.width <- 5,  # set default width of figures
  fig.height <- 8,  # set default height of figures
  fig.align <- "center",  # always align figure in center
  fig.pos <- "H",  # always plot figure at the exact location of the code chunk
  cache <- FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lme4)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(effectsize)
library(scales)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)

```


## Exploratory Data Analysis

```{r load-data, echo = F, warning = F}
# game data #
pilot_game_data <- read_csv(path(here(), '../behavioral_parsing/prolific_data_clean/cleaned_pacman_200_trial_n69.csv'), 
                            col_types = cols(X1 = col_double(),
                                                                                              subject = col_character(),
                                                                                              Trial = col_character(),
                                                                                              Lives = col_double(),
                                                                                              TrialType = col_double(),
                                                                                              Time = col_double(),
                                                                                              GhostLocation = col_double(),
                                                                                              UserLocation = col_double(),
                                                                                              Direction = col_double(),
                                                                                              Biscuit1 = col_logical(),
                                                                                              Biscuit2 = col_logical(),
                                                                                              Biscuit3 = col_logical(),
                                                                                              Biscuit4 = col_logical(),
                                                                                              Biscuit5 = col_logical(),
                                                                                              Attack = col_logical(),
                                                                                              Chase = col_logical(),
                                                                                              Eaten = col_double(),
                                                                                              Score = col_double(),
                                                                                              final_score = col_double()))

# behavioral data#
pilot_behave_data <- read_csv(path(here(), '../behavioral_parsing/prolific_data_clean/cleaned_behave_data_200_trial_n69.csv'), col_types = cols())

# metadata / IDs #
pacman_ids <- read_csv(path(here(), '../behavioral_parsing/prolific_data_clean/cleaned_ids_200_trial_n69.csv'), col_types = cols())

# merge with ids to confirm parsing worked #
pilot_behave_data_clean <- merge.data.frame(pilot_behave_data, pacman_ids, by = c("subject", "ID"))

```

```{r beahvioral-prep, echo = F}

# clean Biscuits #
pilot_game_data_clean <- pilot_game_data %>%
  # ungrouped timing variables
  mutate(time_step = c(FALSE, diff(Time))) %>%
  mutate(trial_numeric = as.numeric(gsub("Trial_", "", Trial))) %>%
  ## grouped by trial variables
  group_by(subject, Trial) %>%
  mutate(start_location = first(UserLocation))


## IMPORTANT NOTES ##
# subject 84 and trial 48 somehow managed to press before trial began-- manually need to change startlocation to 63 and starting direction
# subject 70 on trial 127 also pressed, true start was 57


## 11 is to the right
## 2 is to the left

# clean Biscuits #
pilot_game_data_clean <- pilot_game_data %>%
  # ungrouped timing variables
  mutate(time_step = c(FALSE, diff(Time))) %>%
  mutate(trial_numeric = as.numeric(gsub("Trial_", "", Trial))) %>%
  ## grouped by trial variables
  group_by(subject, Trial) %>%
  mutate(jittered_start_location = first(UserLocation)) %>%
  mutate(base_start_location = if_else(TrialType %in% c(16, 8), 30,
                                       if_else(TrialType %in% c(19, 15, 14, 7, 6), 50,
                                               if_else(TrialType %in% c(20, 13, 5), 70,
                                                   if_else(TrialType %in% c(17, 12, 4), 110,
                                                       if_else(TrialType %in% c(18, 11, 10, 3, 2), 130,
                                                               if_else(TrialType %in% c(9, 1), 150, 999))))))) %>%
  # biscuit location
  mutate(Biscuit1 = if_else(Biscuit1 == FALSE & base_start_location <= 80,  base_start_location + 12, 
                            if_else(Biscuit1 == FALSE & base_start_location > 80, base_start_location -12, 1111)))  %>%
  mutate(Biscuit2 = if_else(Biscuit2 == FALSE & base_start_location <= 80,  base_start_location + 22, 
                            if_else(Biscuit2 == FALSE & base_start_location > 80, base_start_location -22, 1111)))  %>%
  mutate(Biscuit3 = if_else(Biscuit3 == FALSE & base_start_location <= 80,  base_start_location + 32, 
                            if_else(Biscuit3 == FALSE & base_start_location > 80, base_start_location -32, 1111)))  %>%
  mutate(Biscuit4 = if_else(Biscuit4 == FALSE & base_start_location <= 80,  base_start_location + 42, 
                            if_else(Biscuit4 == FALSE & base_start_location > 80, base_start_location -42, 1111)))  %>%
  mutate(Biscuit5 = if_else(Biscuit5 == FALSE & base_start_location <= 80,  base_start_location + 52, 
                            if_else(Biscuit5 == FALSE & base_start_location > 80, base_start_location -52, 1111)))  %>%
  # trial timing information
  mutate(Trial = if_else(Trial == "Trial_1", Trial, if_else(Time == first(Time), "ITI", Trial))) %>%
  mutate_cond(Trial == "ITI", 
              GhostLocation = NA, UserLocation = NA, 
              Biscuit1 = NA, Biscuit2 = NA, Biscuit3 = NA, Biscuit4 = NA, Biscuit5 = NA, 
              Attack = NA, Chase = NA, Eaten = NA, TrialType = NA) %>%
  mutate(trial_time = if_else(Trial == "ITI", 999, Time - first(Time))) %>%
  mutate(trial_flip = 1:n()) %>%
  mutate(time_lag = c(FALSE, diff(trial_time))) %>%
  mutate(trial_end = as.numeric(c(diff(trial_numeric) > 0, FALSE))) %>%
  mutate(trial_length = max(trial_time)) %>%
  # trial grouping variables
  mutate(reward_groups = if_else(TrialType %in% c(1, 5, 9, 13), 2, 
                                 if_else(TrialType %in% c(2, 6, 10, 14), 3, 
                                         if_else(TrialType %in% c(3, 7, 11, 15), 1, 
                                                 if_else(TrialType %in% c(4, 8, 12, 16), 4, 99))))) %>%
  mutate(dots_eaten = max(Eaten)) %>%
  mutate(ghost_start_dir = if_else(TrialType > 16, "no_ghost", 
                                   if_else(TrialType <= 4 | TrialType >= 13, "away", "towards"))) %>%
  mutate(rewards_direction_groups = paste0(reward_groups, "_", ghost_start_dir)) %>%
  mutate(attack_chase_bob = if_else(Attack == T, "Attack", if_else(Chase == T, "Chase", "Bob"))) %>%
  mutate(ghost_objective_direction_tmp = c(FALSE, diff(GhostLocation))) %>%
  mutate(ghost_objective_direction = if_else(ghost_objective_direction_tmp >= 2, "Right", 
                                             if_else(ghost_objective_direction_tmp <= -2, "Left", "still"))) %>%
  select(-ghost_objective_direction_tmp) %>%
  mutate(ghost_direction = if_else((base_start_location < 100 & ghost_objective_direction == "Left") |
                                    (base_start_location > 100 & ghost_objective_direction == "Right") , "Towards",
                                   if_else(ghost_objective_direction == "still", "still", "Away"))) %>%
  ungroup() %>%
  group_by(subject) %>%
  arrange(subject, trial_numeric) %>%
  mutate(life_change = as.numeric(c(diff(Score) < 0, FALSE))) %>%
  group_by(subject, Trial) %>%
  mutate(died = sum(life_change)) %>%
  select(-life_change) %>%
  ungroup()

# get rid of paused trials #
paused_trials <- pilot_game_data_clean %>%
  filter(time_step > 1 & trial_flip != 1 & Trial != "ITI") %>%
  ungroup() %>%
  mutate(trial_ids = paste0(subject, "_", trial_numeric)) %>%
  pull(trial_ids) %>%
  unique()

pilot_game_data_clean <- pilot_game_data_clean %>%
  ungroup() %>%
   mutate(trial_ids = paste0(subject, "_", trial_numeric)) %>%
  filter(!trial_ids %in% paused_trials)
 
pilot_game_data_distance <- pilot_game_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(!is.na(GhostLocation)) %>%
  filter(died == 0) %>%
  group_by(subject, Trial) %>%
  # user movement and distance measures
  mutate(distance_to_ghost = abs(GhostLocation - UserLocation)) %>%
  mutate(min_distance = min(distance_to_ghost)) %>%
  mutate(towards_ghost = if_else(Direction == 2 & GhostLocation < UserLocation, "Towards", 
                                 if_else(Direction == 11 & GhostLocation > UserLocation, "Towards",
                                         if_else(Direction == 4, "Still", "Away")))) %>%
  mutate(away_choice_tmp = c(0, diff(factor(towards_ghost)))) %>%
  mutate(away_choice = if_else( (away_choice_tmp == -2 & towards_ghost == "Away") | 
                                  (away_choice_tmp == -1 & towards_ghost == "Away"), distance_to_ghost, 0)) %>%
  select(-away_choice_tmp) %>%
  mutate(number_of_runs = sum(away_choice > 0, na.rm = T)) %>%
  mutate(last_away = if_else(number_of_runs == 0, 0, last(away_choice[away_choice > 0]) )) %>%
  ungroup()

```

```{r game-level-variables, echo = F}


pilot_all_vars_df <- pilot_game_data_clean %>%
  group_by(subject) %>%
  filter(!is.na(Score)) %>%
  filter(Trial != "ITI") %>%
  # calculate number of deaths
  mutate(death_check = as.numeric(c(diff(Score) < 0, FALSE))) %>%
  mutate(total_deaths = sum(death_check)) %>%
  mutate(max_trial = max(trial_numeric)) %>%
  mutate(trial_in_block = trial_numeric %% 20) %>%
  mutate(trial_in_block = if_else(trial_in_block == 0, 20, trial_in_block)) %>%
  # new minigame
  mutate(lives_check = as.numeric(c(diff(Lives) > 0, FALSE))) %>%
  mutate(total_games = sum(lives_check) + 1) %>%
  group_by(subject, Trial) %>%
  mutate(dots_eaten = max(Eaten)) %>%
  mutate(max_score = max(Score, na.rm = T)) %>%
  mutate(chase_trial = any(Chase)) %>%
  mutate(attack_trial = any(Attack)) %>%
  mutate(trial_died = sum(death_check)) %>%
  mutate(last_trial_in_minigame = sum(lives_check)) %>% # if lose all lives, mark as last trial
  mutate(last_trial_in_minigame = if_else(trial_in_block == 20, 1, last_trial_in_minigame)) %>% # 20 is always last trial 
  group_by(subject) %>%
  mutate(average_score = mean(max_score)) %>%
  mutate(max_time = max(Time)) %>%
  select(subject, Trial, trial_numeric, trial_in_block, TrialType,
         trial_died, last_trial_in_minigame, Lives, dots_eaten,
         chase_trial, attack_trial, 
         max_trial, total_deaths, average_score, final_score, max_time) %>%
  distinct()

# get trials in minigame
round <- 1
game <- 1
pilot_all_vars_df$trial_in_minigame <- 0
pilot_all_vars_df$minigame <- 0
for(idx in 1:nrow(pilot_all_vars_df)){
  # add to df
  pilot_all_vars_df$trial_in_minigame[idx] <- round
  pilot_all_vars_df$minigame[idx] <- game
  if(pilot_all_vars_df$last_trial_in_minigame[idx] == 1){
    round <- 1
    game <- game + 1
  } else {
    round <- round + 1
  }
  
  if(pilot_all_vars_df$subject[idx + 1] != pilot_all_vars_df$subject[idx] & idx != nrow(pilot_all_vars_df)) {
    round <- 1
    game <- 1
  }
  
}

# max trials in minigame and such
pilot_all_vars_df <- pilot_all_vars_df %>%
  group_by(subject) %>%
  mutate(longest_minigame = max(trial_in_minigame)) %>%
  mutate(longest_minigame_under20 = max(trial_in_minigame[trial_in_minigame < 20])) %>%
  mutate(number_of_minigames = max(minigame)) %>%
  mutate(block = ceiling(trial_numeric/20)) %>%
  group_by(subject, block) %>%
  mutate(block_deaths = sum(trial_died)) %>%
  mutate(average_dots_per_block = mean(dots_eaten))

```


## Game play over time

People seem to be very good at the game-- every player had at least one block where they did not have a new minigame (no more than 3 deaths). People get better over time, especially over the first two blocks.

```{r game-level-time, echo = F, fig.width=9, fig.height=4.5}


pilot_all_vars_df %>%
  ggplot(., aes(x = factor(block), y = block_deaths)) +
  geom_boxplot() +
  theme(panel.background = element_rect(fill = "white"),
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        plot.title  = element_text(color = "black", size = 16),
        plot.subtitle = element_text(color = "black", size = 14)) +
    labs(subtitle = "Players were eaten ~3x per block, and tended to do better over time", x = "Block", y = "Deaths") +
  ggtitle("Number of Deaths per Block")

pilot_all_vars_df %>%
  ggplot(., aes(x = factor(block), y = average_dots_per_block, fill = 'f')) +
  geom_violin(alpha = .7) +
  geom_boxplot(notch = T, width =.2) +
  labs(y = "Dots") +
 theme(panel.background = element_rect(fill = "white"), legend.position = "none",
        axis.text = element_text(color = "black", size = 12),
        axis.title = element_text(color = "black", size = 12),
        plot.title  = element_text(color = "black", size = 16),
        plot.subtitle = element_text(color = "black", size = 14))  +
  labs(subtitle = "People most often collected 4 dots and then turned around", x = "Block") +
  ggtitle("Average Dots Eaten per Block")



```

## Trial Level Variables

### Avoiding the Ghost

```{r distance, warning=F, fig.width=9, fig.height=4.5, echo = F}


# number of turns #
pilot_game_data_distance %>%
  select(subject, trial_numeric, number_of_runs) %>%
  distinct() %>%
  ggplot(., aes(x = subject, fill = factor(number_of_runs))) +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(), 
        legend.position = "top") +
  labs(fill = "Number of turns from ghost", title = "Number of turns per trial by subject", subtitle = "Most subjects had a single turn from the ghost") +
  geom_bar() +
  scale_fill_viridis(discrete = T, direction = -1) +
  guides(fill=guide_legend(nrow=1,byrow=TRUE))


# by subject hist of distance #
pilot_game_data_distance %>%
  filter(Trial != "ITI") %>%
  ggplot(., aes(x = distance_to_ghost)) +
  theme(panel.background = element_rect(fill = "white")) +
  geom_histogram(binwidth = 10, alpha = .7) +
  labs(title = "Histogram of distance to ghost within and across trials")


```

#### Operationalizing the choice to avoid

There are two reasonable choices for characterizing risk or avoidance during the trial. The first is the distance to the ghost when the player turned away from the ghost and the second is the minimum distance from the ghost on any given trial. I tend to think that the former is a slightly better choice since it is more closely tied to player choice, whereas the min distance can also be driven by the ghost turning around when the subject didn't expect it.

```{r last_away_min_dist, warning=F, fig.width=9, fig.height=4.5, echo = F}


# last away #
pilot_game_data_distance %>%
  # filters #
  filter(number_of_runs > 0) %>%
  # distinct #
  select(trial_numeric, subject, last_away) %>%
  distinct() %>%
  filter(subject %in% sample(subject, 20)) %>%
  ggplot(., aes(x = subject, y = last_away)) +
  # geom_point(alpha = .3) +
  # geom_violin() +
  geom_jitter(alpha = .5, color = "grey") +
  geom_boxplot(notch = T) +
  ylab("Distance to Ghost at Turnaround") + xlab("Subjects") +
  theme(panel.background = element_rect(fill = "white"), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  ggtitle("Subject Variability in Turning Distance", subtitle = "Random sample of 20 subjects shows that the within subject variability \nin turn around time is usually less than across subject variability")


# min distance #
pilot_game_data_distance %>%
  # filters #
  filter(number_of_runs > 0) %>%
  # distinct #
  select(trial_numeric, subject, min_distance) %>%
  distinct() %>%
  filter(subject %in% sample(subject, 20)) %>%
  ggplot(., aes(x = subject, y = min_distance)) +
  # geom_point(alpha = .3) +
  # geom_violin() +
  geom_jitter(alpha = .5, color = "grey") +
  geom_boxplot(notch = T) +
  ylab("Minimum Distance from Ghost") + xlab("Subjects") +
  theme(panel.background = element_rect(fill = "white"), axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  ggtitle("Subject Variability in Minimum Distance", subtitle = "Random sample of 20 subjects shows that the within subject variability \nin min distance to ghost each trial is usually less than across subject variability")


```

### How did distance to ghost change based on other trial dynamics

```{r distance_reward, warning=F, fig.width=9, fig.height=4.5, echo = F}

# last away ~ reward groups
pilot_game_data_distance %>%
  select(reward_groups, last_away, min_distance, trial_numeric, subject) %>%
  distinct() %>%
  ggplot(., aes(x = factor(reward_groups), y = last_away, fill = factor(reward_groups))) +
  geom_jitter(alpha = .2, color = "grey") +
  geom_boxplot(notch = T) +
  coord_flip() +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "top") +
  scale_fill_viridis(discrete = T, direction = -1) +
  labs(y = "Reward Groups", x = "Distance to Ghost at Turnaround", fill = "Reward Groups", title = "Turnaround Dsitance by Reward Groups", subtitle = 
         "Reward Groups with the larger reward in the last position had shorter turnaround distances")


# Eaten ~ reward groups
pilot_game_data_distance %>%
  select(reward_groups, Eaten, trial_numeric, subject) %>%
  distinct() %>%
  ggplot(., aes(x = factor(Eaten), fill = factor(reward_groups))) +
  geom_bar(position = "dodge2") +
  # geom_errorbar(aes(ymin=stat_count()-sd, ymax=stat_count()+sd), width=.2,
                 # position="dodge2") +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "top") +
  scale_fill_viridis(discrete = T, direction = -1) +
  labs(x = "Number of Dots Eaten", y = "Eaten", fill = "Reward Groups", title = "Number of Dots Eaten by Reward Group", subtitle = 
         "All 5 dots were eaten more often when the last dot was the higher reward")


# last_away ~ lives
pilot_game_data_distance %>%
  select(Lives, last_away, subject) %>%
  distinct() %>%
  ggplot(., aes(x = factor(Lives), y = last_away, fill = factor(Lives))) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(x = "Lives", y = "Distance to Ghost at Turnaround", fill = "Lives", title = "Turn Around Distance By Number of Remaining Lives", subtitle = "Subjects stayed farther away from the ghost when they only had one life remaining")



# Did the the ghost direction make it more likely to turn around?
pilot_game_data_distance %>%
  filter(last_away == away_choice) %>%
  filter(ghost_direction != "still") %>%
  ggplot(., aes(x = ghost_direction, fill = ghost_direction)) +
  geom_bar() +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(x = "Ghost Direction", title = "Ghost Direction at time of last turnaround", subtitle = "Players were more likely to turnaround if the ghost was moving towards them")


pilot_game_data_distance %>%
  filter(number_of_runs > 0) %>%
  filter(last_away == away_choice) %>%
  filter(ghost_direction != "still") %>%
  ggplot(., aes(x = ghost_direction, y = last_away, fill = ghost_direction)) +
  geom_jitter(color = 'grey', alpha = .2) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(x = "Ghost Direction", title = "Turnaround Distance by Ghost Direction", subtitle = "Players turnaround at a farther distance from the ghost when the ghost was moving ~away~ from them")
```

## Chase and Attack

### Chase

```{r chase-df, warning=F, fig.width=9, fig.height=4.5, echo = F}

pilot_all_vars_df %>%
  filter(chase_trial == T) %>%
  select(subject, trial_numeric) %>%
  distinct() %>%
  group_by(subject) %>%
  add_count() %>%
  ggplot(., aes(x = n)) +
  geom_histogram() +
  theme(panel.background = element_rect(fill = "white")) +
  labs(x = "Number of Trials", title = "Number of Trials with a Chase", subtitle = "10-35% of trials include a chase (out of 200 trials total)")


pilot_all_vars_df %>%
  ungroup() %>%
  filter(chase_trial == T & trial_died) %>%
  select(subject, trial_numeric) %>%
  distinct() %>%
  group_by(subject) %>%
  add_count() %>%
  ggplot(., aes(x = n)) +
  geom_histogram(binwidth = 1) +
  theme(panel.background = element_rect(fill = "white")) +
  labs(x = "Number of Deaths", title = "Number of deaths on chase trials by subject", subtitle = "Dying on a chase trial is fairly rare, with most players dying on about 5 chase trials (out of 20-70 trials)")


```

### Attack

```{r attack-df, warning=F, fig.width=9, fig.height=4.5, echo = F}

pilot_all_vars_df %>%
  filter(attack_trial == T) %>%
  select(subject, trial_numeric) %>%
  distinct() %>%
  group_by(subject) %>%
  add_count() %>%
  ggplot(., aes(x = n)) +
  geom_histogram() +
  theme(panel.background = element_rect(fill = "white")) +
  labs(x = "Number of Trials", title = "Number of Trials with a Attack", subtitle = "5-20% of trials include a attack (out of 200 trials total)")


pilot_all_vars_df %>%
  ungroup() %>%
  filter(attack_trial == T & trial_died == 1) %>%
  select(subject, trial_numeric) %>%
  distinct() %>%
  group_by(subject) %>%
  add_count() %>%
  ggplot(., aes(x = n)) +
  geom_histogram(binwidth = 1) +
  theme(panel.background = element_rect(fill = "white")) +
  labs(x = "Number of Deaths", title = "Number of deaths on attack trials by subject", subtitle = "Dying on an attack trial is common (by design), with most players dying on most of their attack trials")


```


## Were Number of Dots Eaten / Distance to Ghost affected by 'irrelevant' variables?


```{r eaten_irrev, warning=F, fig.width=9, fig.height=4.5, echo = F}

# eaten ~ direction
pilot_game_data_distance %>%
  select(subject, trial_numeric, dots_eaten, base_start_location) %>%
  mutate(left_right = if_else(base_start_location < 100, "Left", "Right")) %>%
  group_by(subject, left_right) %>%
  mutate(average_dots_eaten = mean(dots_eaten)) %>%
  distinct() %>%
  ggplot(., aes(x = left_right, y = average_dots_eaten)) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white")) +
  labs(y = "Average Dots Eaten", x= "", title = "Dots Eaten by Starting Location", subtitle = "No effect of starting location on the number of dots eaten")


# last away ~ direction
pilot_game_data_distance %>%
  select(subject, trial_numeric, last_away, base_start_location) %>%
  mutate(left_right = if_else(base_start_location < 100, "Left", "Right")) %>%
  group_by(subject, left_right) %>%
  mutate(average_last_away = mean(last_away)) %>%
  distinct() %>%
  ggplot(., aes(x = left_right, y = average_last_away)) +
  geom_boxplot(notch = T) +
  theme(panel.background = element_rect(fill = "white")) +
  labs(y = "Average Turnaround Distance", x= "", title = "Last Away Distance by Starting Location", subtitle = "No effect of starting location on turnaround distance")


```




## BJH016

```{r BJH016-data-load, echo = F, eval = F}

bj16_data <- read_csv(path(here(), './data/ieeg_behave/BJH016_raw_behave.csv'), col_types = cols(X1 = col_double(),
                                                                                              Subject = col_character(),
                                                                                              Trial = col_character(),
                                                                                              Lives = col_double(),
                                                                                              Trial_on_off = col_double(),
                                                                                              TrialType = col_double(),
                                                                                              Time = col_double(),
                                                                                              GhostLocation = col_double(),
                                                                                              UserLocation = col_double(),
                                                                                              Direction = col_double(),
                                                                                              Biscuit1 = col_logical(),
                                                                                              Biscuit2 = col_logical(),
                                                                                              Biscuit3 = col_logical(),
                                                                                              Biscuit4 = col_logical(),
                                                                                              Biscuit5 = col_logical(),
                                                                                              Attack = col_logical(),
                                                                                              Chase = col_logical(),
                                                                                              Eaten = col_double(),
                                                                                              Score = col_double()))


```

```{r BJH016-data-prep, echo = F, eval = F}


# clean Biscuits #
bj16_data_clean <- bj16_data %>%
  rename(subject = Subject) %>%
  # ungrouped timing variables
  rename(sample = Time) %>%
  mutate(Time = sample /2000) %>%
  mutate(time_step = c(FALSE, diff(Time))) %>%
  mutate(trial_numeric = as.numeric(gsub("Trial_", "", Trial))) %>%
  ## grouped by trial variables
  group_by(subject, Trial) %>%
  mutate(jittered_start_location = first(UserLocation)) %>%
  mutate(base_start_location = if_else(TrialType %in% c(16, 8), 30,
                                       if_else(TrialType %in% c(19, 15, 14, 7, 6), 50,
                                               if_else(TrialType %in% c(20, 13, 5), 70,
                                                   if_else(TrialType %in% c(17, 12, 4), 110,
                                                       if_else(TrialType %in% c(18, 11, 10, 3, 2), 130,
                                                               if_else(TrialType %in% c(9, 1), 150, 999))))))) %>%
  # get correct trial type info (sometimes trial type switches early/ lags)
  mutate(TrialType = names(sort(table(TrialType),decreasing=TRUE))[1]) %>%
  # same deal with lives
  mutate(Lives = as.numeric(names(sort(table(Lives),decreasing=TRUE))[1])) %>%
  # biscuit location
  mutate(Biscuit1 = if_else(Biscuit1 == FALSE & base_start_location <= 80,  base_start_location + 12, 
                            if_else(Biscuit1 == FALSE & base_start_location > 80, base_start_location -12, 1111)))  %>%
  mutate(Biscuit2 = if_else(Biscuit2 == FALSE & base_start_location <= 80,  base_start_location + 22, 
                            if_else(Biscuit2 == FALSE & base_start_location > 80, base_start_location -22, 1111)))  %>%
  mutate(Biscuit3 = if_else(Biscuit3 == FALSE & base_start_location <= 80,  base_start_location + 32, 
                            if_else(Biscuit3 == FALSE & base_start_location > 80, base_start_location -32, 1111)))  %>%
  mutate(Biscuit4 = if_else(Biscuit4 == FALSE & base_start_location <= 80,  base_start_location + 42, 
                            if_else(Biscuit4 == FALSE & base_start_location > 80, base_start_location -42, 1111)))  %>%
  mutate(Biscuit5 = if_else(Biscuit5 == FALSE & base_start_location <= 80,  base_start_location + 52, 
                            if_else(Biscuit5 == FALSE & base_start_location > 80, base_start_location -52, 1111)))  %>%
  # trial timing information
  mutate(Trial = if_else(Trial_on_off == 0, "ITI", Trial)) %>%
  mutate_cond(Trial == "ITI", 
              GhostLocation = NA, UserLocation = NA, Lives = NA,
              Biscuit1 = NA, Biscuit2 = NA, Biscuit3 = NA, Biscuit4 = NA, Biscuit5 = NA, 
              Attack = NA, Chase = NA, Eaten = NA, TrialType = NA) %>%
  mutate(trial_time = if_else(Trial == "ITI", 999, Time - first(Time))) %>%
  mutate(trial_flip = 1:n()) %>%
  mutate(time_lag = c(FALSE, diff(trial_time))) %>%
  mutate(trial_end = as.numeric(c(diff(trial_numeric) > 0, FALSE))) %>%
  mutate(trial_length = max(trial_time)) %>%
  # trial grouping variables
  mutate(reward_groups = if_else(TrialType %in% c(1, 5, 9, 13), 2, 
                                 if_else(TrialType %in% c(2, 6, 10, 14), 3, 
                                         if_else(TrialType %in% c(3, 7, 11, 15), 1, 
                                                 if_else(TrialType %in% c(4, 8, 12, 16), 4, 99))))) %>%
  mutate(ghost_start_dir = if_else(TrialType > 16, "no_ghost", 
                                   if_else(TrialType <= 4 | TrialType >= 13, "away", "towards"))) %>%
  mutate(rewards_direction_groups = paste0(reward_groups, "_", ghost_start_dir)) %>%
  mutate(attack_chase_bob = if_else(Attack == T, "Attack", if_else(Chase == T, "Chase", "Bob"))) %>%
  ungroup() %>%
  group_by(subject) %>%
  arrange(subject, trial_numeric) %>%
  mutate(life_change = as.numeric(c(diff(Score) < 0, FALSE))) %>%
  group_by(subject, Trial) %>%
  mutate(died = sum(life_change)) %>%
  select(-life_change) %>%
  ungroup()

# get rid of paused trials  don't think they exist for this subject#
# bj16_paused_trials <- bj16_data_clean %>%
#   filter(ghost_start_dir != "no_ghost" & Trial != "ITI") %>%
#   group_by(Trial) %>%
#   mutate(ghost_step = c(FALSE, diff(GhostLocation))) %>%
#   mutate(user_step = c(FALSE, diff(UserLocation))) %>%
#   filter(ghost_step == 0 & user_step == 0) %>%
#   filter(c(0, diff(trial_flip)) == 1)
# 
# 
# pilot_game_data_clean <- pilot_game_data_clean %>%
#   ungroup() %>%
#    mutate(trial_ids = paste0(subject, "_", trial_numeric)) %>%
#   filter(!trial_ids %in% paused_trials)
 
bj16_data_distance <- bj16_data_clean %>%
  filter(Trial != "ITI") %>%
  filter(!is.na(GhostLocation)) %>%
  filter(died == 0) %>%
  group_by(subject, Trial) %>%
  # user movement and distance measures
  mutate(distance_to_ghost = abs(GhostLocation - UserLocation)) %>%
  mutate(min_distance = min(distance_to_ghost)) %>%
  mutate(towards_ghost = if_else(Direction == 2 & GhostLocation < UserLocation, "Towards", 
                                 if_else(Direction == 11 & GhostLocation > UserLocation, "Towards",
                                         if_else(Direction == 4, "Still", "Away")))) %>%
  mutate(away_choice_tmp = c(0, diff(factor(towards_ghost)))) %>%
  mutate(away_choice = if_else( (away_choice_tmp == -2 & towards_ghost == "Away") | 
                                  (away_choice_tmp == -1 & towards_ghost == "Away"), distance_to_ghost, 0)) %>%
  select(-away_choice_tmp) %>%
  mutate(number_of_runs = sum(away_choice > 0, na.rm = T)) %>%
  mutate(last_away = if_else(number_of_runs == 0, 0, last(away_choice[away_choice > 0]) )) %>%
  ungroup()


bj16_all_vars_df <- bj16_data_clean %>%
  group_by(subject) %>%
  filter(!is.na(Score)) %>%
  filter(Trial != "ITI") %>%
  filter(Trial != 0) %>%
  # calculate number of deaths
  mutate(death_check = as.numeric(c(diff(Score) < 0, FALSE))) %>%
  mutate(total_deaths = sum(death_check)) %>%
  mutate(max_trial = max(trial_numeric)) %>%
  mutate(trial_in_block = trial_numeric %% 20) %>%
  mutate(trial_in_block = if_else(trial_in_block == 0, 20, trial_in_block)) %>%
  # new minigame
  mutate(lives_check = as.numeric(c(diff(Lives) > 0, FALSE))) %>%
  mutate(total_games = sum(lives_check) + 1) %>%
  group_by(subject, Trial) %>%
  mutate(dots_eaten = max(Eaten)) %>%
  mutate(max_score = max(Score, na.rm = T)) %>%
  mutate(trial_died = sum(death_check)) %>%
  mutate(last_trial_in_minigame = sum(lives_check)) %>% # if lose all lives, mark as last trial
  mutate(last_trial_in_minigame = if_else(trial_in_block == 20, 1, last_trial_in_minigame)) %>% # 20 is always last trial 
  group_by(subject) %>%
  mutate(average_score = mean(max_score)) %>%
  mutate(max_time = max(Time)) %>%
  select(subject, Trial, trial_numeric, trial_in_block, TrialType, trial_length,
         trial_died, last_trial_in_minigame, Lives, dots_eaten,
         max_trial, total_deaths, average_score, max_time) %>%
  distinct()

# get trials in minigame
round <- 1
game <- 1
bj16_all_vars_df$trial_in_minigame <- 0
bj16_all_vars_df$minigame <- 0
for(idx in 1:nrow(bj16_all_vars_df)){
  # add to df
  bj16_all_vars_df$trial_in_minigame[idx] <- round
  bj16_all_vars_df$minigame[idx] <- game
  if(bj16_all_vars_df$last_trial_in_minigame[idx] == 1){
    round <- 1
    game <- game + 1
  } else {
    round <- round + 1
  }
  
  if(bj16_all_vars_df$subject[idx + 1] != bj16_all_vars_df$subject[idx] & idx != nrow(bj16_all_vars_df)) {
    round <- 1
    game <- 1
  }
  
}

# max trials in minigame and such
pilot_all_vars_df <- pilot_all_vars_df %>%
  group_by(subject) %>%
  mutate(longest_minigame = max(trial_in_minigame)) %>%
  mutate(longest_minigame_under20 = max(trial_in_minigame[trial_in_minigame < 20])) %>%
  mutate(number_of_minigames = max(minigame)) %>%
  mutate(block = ceiling(trial_numeric/20)) %>%
  group_by(subject, block) %>%
  mutate(block_deaths = sum(trial_died)) %>%
  mutate(average_dots_per_block = mean(dots_eaten))


bj16_all_vars_df <- bj16_all_vars_df %>%
  group_by(subject) %>%
  mutate(longest_minigame = max(trial_in_minigame)) %>%
  mutate(longest_minigame_under20 = max(trial_in_minigame[trial_in_minigame < 20])) %>%
  mutate(number_of_minigames = max(minigame)) %>%
  mutate(block = ceiling(trial_numeric/20)) %>%
  group_by(subject, block) %>%
  mutate(block_deaths = sum(trial_died)) %>%
  mutate(average_dots_per_block = mean(dots_eaten)) %>%
  ungroup()
  
bj16_all_vars_df <- bj16_all_vars_df %>%
  mutate(block = factor(block, levels = 0:23, labels = 0:23))

pilot_all_vars_df <- pilot_all_vars_df %>%
  mutate(block = factor(block, levels = 0:23, labels = 0:23))

```

```{r comparative, echo = F, eval = F}


pilot_all_vars_df %>%
  ggplot(., aes(x = block, y = average_dots_per_block, fill = 'f')) +
  geom_point(data = bj16_all_vars_df, aes(x = block, y = average_dots_per_block), size = 2, color = "red") +
  geom_violin(alpha = .7) +
  geom_boxplot(notch = T, width =.2) +
  geom_point(data = bj16_all_vars_df, aes(x = block, y = average_dots_per_block), size = 2, color = "red") +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(subtitle = "This was consistent across blocks", x = "Block") +
  ggtitle("People most often collected 4 dots and then turned around")



pilot_all_vars_df %>%
  ggplot(., aes(x = block, y = block_deaths, fill = 'f')) +
  geom_point(data = bj16_all_vars_df, aes(x = block, y = block_deaths), size = 2, color = "red") +
  # geom_violin(alpha = .7) +
  geom_boxplot(notch = F, width =.2) +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "none") +
  labs(subtitle = "He did improve with time", x = "Block") +
  ggtitle("BJH016 died much more often than controls")

```
