---
title: "Theta Hippocampus"
output: html_document
date: "2023-09-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 5,  # set default width of figures
  fig.height = 8,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(ggeffects)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lmerTest)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(scales)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)



```


# Linear Mixed Effects Models

### Problems with singular fit

Due to unbalanced groups, there are some singular fits. I have looked into this and it is resolved when I use a simpler model with only a random effect of subject. However, it does make sense to have a different intercept for each electrode, since I know they can vary. I looked at it both ways, and it did not change the significance or direction of the fixed effects. Plan going forward is to use the more complex model but to double check it holds in the simpler model. Another thing to checkis if the variance of elec_id:subject is regularly close to 0. That might indicate that while it makes sense each electrode would get its own intercept, it just isn't necessary.


## Data Prep and EDA


```{r load-data}

# ieeg data #
hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))

# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))

# combine ghost and no ghost #
all_subs_dist <- all_subs_g_dist %>% 
  select(-GhostLocation, -distance_to_ghost, -min_distance, -cdf_distance)
all_subs_dist <- rbind(all_subs_dist, all_subs_ng_dist)

# add ITI to behavioral df
behavior_iti_df <- all_subs_dist %>% 
  select(subject, trial_numeric, trial_time) %>%
  filter(trial_time < 1) %>%
  mutate(trial_time = round(trial_time - 1, 2))

all_subs_dist <- full_join(all_subs_dist, behavior_iti_df)

```

```{r elec-response, fig.width=20, fig.height=40}

## plot electrode level ERPS ##

avg_hc_theta_data <- hc_theta_data %>%
  rename(theta = theta) %>%
  group_by(trial_time, electrode, subject) %>%
  mutate(mean_elec_theta = mean(theta)) %>%
  ungroup() %>%
  select(-trial_numeric, -theta) %>%
  distinct() 

avg_hc_theta_data %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  ggplot(., aes(x = trial_time, y = mean_elec_theta, color = subject)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~elec_id, ncol = 6) +
  ylim(-1.5, 1.5) +
  scale_color_manual(values = getPalette(15)) 

```


```{r subject-overall-response, fig.width= 12, fig.height=12}

## plot subject and combined ERPS ##

avg_hc_theta_data %>%
  group_by(trial_time, subject) %>%
  mutate(mean_theta = mean(mean_elec_theta)) %>%
  ungroup() %>%
  ggplot(., aes(x = trial_time, y = mean_theta, color = subject)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject) +
  scale_color_manual(values = getPalette(15)) 

avg_hc_theta_data %>%
  group_by(trial_time, subject) %>%
  mutate(mean_sub_theta = mean(mean_elec_theta)) %>%
  ungroup() %>%
  select(-mean_elec_theta, -electrode) %>%
  distinct() %>%
  group_by(trial_time) %>%
  mutate(mean_theta = mean(mean_sub_theta)) %>%
  ggplot(., aes(x = trial_time, y = mean_theta)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  theme(panel.background = element_rect(fill = "white")) 


```



```{r merge-with-behavior, fig.width= 12, fig.height=12}

# merge behavior data with ieeg data
hc_theta_behave_df <- left_join(all_subs_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               hc_theta_data %>% mutate(trial_time = round(trial_time, 2)))

# validate we get the same ieeg data by comparing with above plots
avg_hc_theta_behave_df <- hc_theta_behave_df %>%
  filter(trial_time <= 5.10) %>%
  select(subject, trial_time, electrode, theta, trial_numeric) %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(subject != "BJH026") %>%
  group_by(trial_time, electrode, subject) %>%
  mutate(mean_elec_theta = mean(theta, na.rm = T)) %>%
  ungroup() %>%
  select(-trial_numeric, -theta) %>%
  distinct() %>%
  group_by(trial_time, subject) %>%
  mutate(mean_sub_theta = mean(mean_elec_theta, na.rm = T)) %>%
  ungroup() %>%
  select(-mean_elec_theta, -electrode) %>%
  distinct() %>%
  group_by(trial_time) %>%
  mutate(mean_theta = mean(mean_sub_theta, na.rm = T))

avg_hc_theta_behave_df %>%
  ggplot(., aes(x = trial_time, y = mean_sub_theta, color = subject)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject) +
  scale_color_manual(values = getPalette(15)) +
  xlim(-1, 5) 



avg_hc_theta_behave_df %>%
  ggplot(., aes(x = trial_time, y = mean_theta)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  xlim(-1, 5) 


```

## Linear Effects Model Results and Plots

```{r}
brain_df <- hc_theta_data
distance_df <-   all_subs_g_dist
# merge behavior data with ieeg data
brain_behave_df <- left_join(distance_df %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)) %>% filter(!(subject == "SLCH002" & trial_numeric == 220)), 
                             brain_df %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
brain_behave_lme_df <- brain_behave_df %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # exclude time before they started moving, may be good to look at not doing this as well
  filter(Direction != "Still") %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  # shift the time so that time 0 is the start of movement onset
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  # filter time so that trials end when the person turnaround for the final time
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  mutate(turnaround_time = if_else(event == 1, move_time, 0)) %>%
  filter(move_time < max(turnaround_time)) %>%
  ungroup() %>%
  # filter to max time 3 since after 3s we start losing a lot of trials
  filter(move_time < 3) %>%
  # select and rescale the necessary variables for the model
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, distance_to_ghost)  %>%
  mutate(points_remaining = rescale(points_remaining)) %>%
  mutate(distance_to_ghost = rescale(distance_to_ghost))


time_step_df <- brain_behave_lme_df %>%
        filter(move_time == 0)
      
# fit the model with random effects of subject and electrode
model_all <- summary(robustlmm::rlmer(theta ~ distance_to_ghost + points_remaining + (1|subject/elec_id), data = time_step_df))
      

```


## Onset Before Turn

```{r onset-before-turn}


# hc and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_before_turn_model_and_plot("hc", "theta", 
                                all_subs_g_dist, hc_theta_data, 
                                y_low = -8, y_high = 8,
                                plot_title = "Theta encodes reward and threat values in the hc at trial onset",
                                rerun_model = TRUE)

# hc and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_before_turn_model_and_plot("hc", "theta", 
                                all_subs_g_dist, hc_theta_data, 
                                plot_title = "Theta encodes (some?) reward values in the hc at trial onset",
                                y_low = -10, y_high = 10,
                                rerun_model = FALSE)


```


## Approach Only


```{r onset-before-turn}


# hc and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_turnaround_model_and_plot("hc", "theta", 
                                all_subs_g_dist, hc_theta_data, 
                                y_low = -8, y_high = 8,
                                plot_title = "Theta encodes reward and threat values in the hc at turnaround",
                                rerun_model = TRUE)

# hc and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_turnaround_model_and_plot("hc", "theta", 
                                all_subs_g_dist, hc_theta_data, 
                                plot_title = "Theta  encodes  values in the HC at turnaround",
                                y_low = -5, y_high = 5,
                                rerun_model = FALSE)


```


## Other Variables of Interest Combined Value, Pacman Location, Userlocation

```{r other-single-regressors}

individual_and_overall_lme_onset_combval_before_turn_model_and_plot("hc", "theta", 
                                all_subs_g_dist, hc_theta_data %>% filter(theta < 20), 
                                plot_title = "Theta  encodes  values in the HC at turnaround",
                                y_low = -5, y_high = 5,
                                rerun_model = TRUE)

individual_and_overall_lme_onset_combval_before_turn_model_and_plot("hc", "theta", 
                                all_subs_g_dist, hc_theta_data, 
                                plot_title = "Theta  encodes integrated reward/threat values in the HC at turnaround",
                                y_low = -20, y_high = 20,
                                rerun_model = FALSE)


```


```{r}
distance_df <- all_subs_g_dist
brain_df <- hc_theta_data

# merge behavior data with ieeg data
brain_behave_df <- left_join(distance_df %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                             brain_df %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
brain_behave_lme_df <- brain_behave_df %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # exclude time before they started moving, may be good to look at not doing this as well
  filter(Direction != "Still") %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  # shift the time so that time 0 is the start of movement onset
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  # filter time so that trials end when the person turnaround for the final time
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  mutate(turnaround_time = if_else(event == 1, move_time, 0)) %>%
  filter(move_time < max(turnaround_time)) %>%
  ungroup() %>%
  # filter to max time 3 since after 3s we start losing a lot of trials
  filter(move_time < 3) %>%
  # select and rescale the necessary variables for the model
  rowwise() %>%
  mutate(combined_value = points_remaining * distance_to_ghost) %>%
  ungroup() %>%
  mutate(combined_value = rescale(combined_value)) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, combined_value)  %>%
  mutate(combined_value = rescale(combined_value))

brain_behave_lme_df %>%
  filter(subject == "LL10") %>%
  filter(move_time == 1.4) %>%
  filter(theta < 20) %>%
  ggplot(., aes(x = combined_value, y = theta)) +
  geom_point(color = "#D1B5F4") +
  geom_smooth(method = "lm", model = "y~x", fill = "#D1B5F4", alpha = .5, color ="black") +
  facet_wrap(~elec_id, nrow = 1)

brain_behave_lme_df %>%
  ggplot(., aes(x = theta)) +
  geom_histogram(binwidth = .5) +
  theme(panel.background = element_rect(fill = "white")) 
  
```





## Pacman Location

```{r value-model}

# merge behavior data with ieeg data
hc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               hc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
hc_theta_lme_df <- hc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, UserLocation)  %>%
  mutate(UserLocation = rescale(UserLocation))


userloc_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(hc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- hc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ UserLocation + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  userloc_results_only <- rbind(userloc_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_userloc <- userloc_results_only %>% mutate(move_time = sort(unique(hc_theta_lme_df$move_time)))
                       

plot <- model_results_userloc %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#65ADC1") +
  geom_line(color = "#65ADC1") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 1) +
  ggtitle("HC Theta, Pacman Location")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "hc_theta_trial_pacman_location.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```

## Ghost Location

```{r value-model}

# merge behavior data with ieeg data
hc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               hc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
hc_theta_lme_df <- hc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, GhostLocation)  %>%
  mutate(GhostLocation = rescale(GhostLocation))


ghostloc_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(hc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- hc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ GhostLocation + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  ghostloc_results_only <- rbind(ghostloc_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_ghostloc <- ghostloc_results_only %>% mutate(move_time = sort(unique(hc_theta_lme_df$move_time)))
                       

plot <- model_results_ghostloc %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#EF7474") +
  geom_line(color = "#EF7474") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 1) +
  ggtitle("HC Theta, Ghost Location")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "hc_theta_trial_ghost_location.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```



## Combined value

```{r value-model}

# merge behavior data with ieeg data
hc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               hc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
hc_theta_lme_df <- hc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, distance_to_ghost)  %>%
  rowwise() %>%
  mutate(combined_value = points_remaining * distance_to_ghost) %>%
  ungroup() %>%
  mutate(combined_value = rescale(combined_value))


value_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(hc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- hc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ combined_value + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  value_results_only <- rbind(value_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_value <- value_results_only %>% mutate(move_time = sort(unique(hc_theta_lme_df$move_time)))
                       

plot <- model_results_value %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#D1B5F4") +
  geom_line(color = "#D1B5F4") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 3) +
  ggtitle("HC Theta, Combined Value")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "hc_theta_trial_combined_value.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```



```{r save}

write_csv(model_results_whole_trial, path(here(), "results", "hc_theta_model_results_whole_trial.csv"))
write_csv(model_results, path(here(), "results", "hc_theta_model_results_turnarouns.csv"))
write_csv(model_results_value, path(here(), "results", "hc_theta_model_results_integrated_value.csv"))


```
