---
title: "OFC Theta"
output: html_document
date: "2023-09-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,  # don't print the code chunk
  warning = FALSE,  # don't print warnings
  message = FALSE,  # don't print messages
  fig.width = 5,  # set default width of figures
  fig.height = 8,  # set default height of figures
  fig.align = "center",  # always align figure in center
  fig.pos = "H",  # always plot figure at the exact location of the code chunk
  cache = FALSE)  # cache results

## libraries ##
library(tidyverse)
library(ggplot2)
library(ggeffects)
library(magrittr)
library(ggthemr)
library(grid)
library(gtable)
library(gridExtra)
library(wesanderson)
library(ggsci)
library(zoo)
library(kableExtra)
library(lmerTest)
library(RColorBrewer)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(ggcorrplot)
library(viridis)
library(lmtest)
library(gt)
library(survminer)
library(survival)
library(scales)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))

## plotting helpers ##
ggthemr("light")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# ## parallelization ##
# nCores <- 2
# registerDoParallel(nCores)



```


# Linear Mixed Effects Models

### Problems with singular fit

Due to unbalanced groups, there are some singular fits. I have looked into this and it is resolved when I use a simpler model with only a random effect of subject. However, it does make sense to have a different intercept for each electrode, since I know they can vary. I looked at it both ways, and it did not change the significance or direction of the fixed effects. Plan going forward is to use the more complex model but to double check it holds in the simpler model. Another thing to checkis if the variance of elec_id:subject is regularly close to 0. That might indicate that while it makes sense each electrode would get its own intercept, it just isn't necessary.


## Data Prep and EDA

```{r load-data}

# ieeg data #
ofc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_ofc_all_subs_logged_iti_onset.csv"))

# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_distance_df.csv"))

# combine ghost and no ghost #
all_subs_dist <- all_subs_g_dist %>% 
  select(-GhostLocation, -distance_to_ghost, -min_distance, -cdf_distance)
all_subs_dist <- rbind(all_subs_dist, all_subs_ng_dist)

# add ITI to behavioral df
behavior_iti_df <- all_subs_dist %>% 
  select(subject, trial_numeric, trial_time) %>%
  filter(trial_time < 1) %>%
  mutate(trial_time = round(trial_time - 1, 2))

all_subs_dist <- full_join(all_subs_dist, behavior_iti_df)

```

```{r elec-response, fig.width=20, fig.height=40}

## plot electrode level ERPS ##

avg_ofc_theta_data <- ofc_theta_data %>%
  rename(theta = theta) %>%
  group_by(trial_time, electrode, subject) %>%
  mutate(mean_elec_theta = mean(theta)) %>%
  ungroup() %>%
  select(-trial_numeric, -theta) %>%
  distinct() 

avg_ofc_theta_data %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  ggplot(., aes(x = trial_time, y = mean_elec_theta, color = subject)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~elec_id, ncol = 6) +
  ylim(-1.5, 1.5) +
  scale_color_manual(values = getPalette(15)) 

```


```{r subject-overall-response, fig.width= 12, fig.height=12}

## plot subject and combined ERPS ##

avg_ofc_theta_data %>%
  group_by(trial_time, subject) %>%
  mutate(mean_theta = mean(mean_elec_theta)) %>%
  ungroup() %>%
  ggplot(., aes(x = trial_time, y = mean_theta, color = subject)) +
  geom_point() +
  geom_line() +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject) +
  scale_color_manual(values = getPalette(15)) 

avg_ofc_theta_data %>%
  group_by(trial_time, subject) %>%
  mutate(mean_sub_theta = mean(mean_elec_theta)) %>%
  ungroup() %>%
  select(-mean_elec_theta, -electrode) %>%
  distinct() %>%
  group_by(trial_time) %>%
  mutate(mean_theta = mean(mean_sub_theta)) %>%
  ggplot(., aes(x = trial_time, y = mean_theta)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  theme(panel.background = element_rect(fill = "white")) 


```



```{r merge-with-behavior, fig.width= 12, fig.height=12}

# merge behavior data with ieeg data
ofc_theta_behave_df <- left_join(all_subs_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ofc_theta_data %>% mutate(trial_time = round(trial_time, 2)))

# validate we get the same ieeg data by comparing with above plots
avg_ofc_theta_behave_df <- ofc_theta_behave_df %>%
  group_by(trial_time, electrode, subject) %>%
  mutate(mean_elec_theta = mean(theta, na.rm = T)) %>%
  ungroup() %>%
  select(-trial_numeric, -theta) %>%
  distinct() %>%
  group_by(trial_time, subject) %>%
  mutate(mean_sub_theta = mean(mean_elec_theta, na.rm = T)) %>%
  ungroup() %>%
  select(-mean_elec_theta, -electrode) %>%
  distinct() %>%
  group_by(trial_time) %>%
  mutate(mean_theta = mean(mean_sub_theta, na.rm = T))


avg_ofc_theta_behave_df %>%
  ggplot(., aes(x = trial_time, y = mean_theta)) +
  geom_point(color = "black") +
  geom_line(color = "black") +
  theme(panel.background = element_rect(fill = "white")) +
  xlim(-1, 5) + ylim(-.15, .45)


```

## Linear Effects Model Results and Plots

## Onset Before Turn

```{r onset-before-turn}
# Register the parallel backend
cl <- makeCluster(detectCores() - 1)  # Leave one core free
registerDoParallel(cl)


# OFC and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_before_turn_model_and_plot("OFC", "theta", 
                                all_subs_g_dist, ofc_theta_data, 
                                y_low = -8, y_high = 8,
                                plot_title = "Theta encodes reward and threat values in the OFC at trial onset",
                                rerun_model = TRUE)

# OFC and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_before_turn_model_and_plot("OFC", "theta", 
                                all_subs_g_dist, ofc_theta_data, 
                                plot_title = "Theta encodes reward and threat values in the OFC at trial onset",
                                y_low = -8, y_high = 8,
                                rerun_model = FALSE)
```

```{r fig.height=6, fig.width=8}


brain_behave_lme_df %>%
  select(subject, max_move_time, trial_numeric) %>%
  unique() %>%
  ggplot(., aes(x = max_move_time)) +
  geom_histogram(binwidth = .2) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject)

brain_behave_lme_df %>%
  select(subject, max_move_time, trial_numeric) %>%
  unique() %>%
  ggplot(., aes(x = max_move_time)) +
  geom_histogram(binwidth = .05) +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~subject, scales = "free_y") +
  xlim(1.5, 4)


```


```{r, fig.width = 10, fig.height = 8}
## Run LME Multiple Regression Models with two predictors: Distance to Ghost, Points Remaining

distance_df <- all_subs_g_dist
brain_df <- ofc_theta_data
  
  
# merge behavior data with ieeg data
brain_behave_df <- left_join(distance_df %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                                 brain_df %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
brain_behave_lme_df <- brain_behave_df %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # exclude time before they started moving, may be good to look at not doing this as well
  filter(Direction != "Still") %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  # shift the time so that time 0 is the start of movement onset
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  # filter time so that trials end when the person turnaround for the final time
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  mutate(turnaround_time = if_else(event == 1, move_time, 0)) %>%
  filter(max(turnaround_time) >= 1.2) %>%
  filter(move_time < max(turnaround_time)) %>%
  ungroup() %>%
  # filter to max time 3 since after 3s we start losing a lot of trials
  filter(move_time < 1.2) %>%
  # select and rescale the necessary variables for the model
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, distance_to_ghost)  %>%
  mutate(points_remaining = rescale(points_remaining)) %>%
  mutate(distance_to_ghost = rescale(distance_to_ghost)) 

tmp <- brain_behave_lme_df %>% group_by(subject) %>% mutate(n = length(unique(trial_numeric)))


# Parallelized loop over steps
results <- foreach(step=sort(unique(brain_behave_lme_df$move_time)[1:3]), .combine=rbind, .packages=c("dplyr", "robustlmm", "lmerTest", "MASS", "tibble")) %dopar% {
  
  # prep model result dfs - distance to ghost
  dist_to_g_results <- tibble(
    case = character(0),
    time = numeric(0),
    Estimate = numeric(0),
    `Std. Error` = numeric(0),
    `t value` = numeric(0),
    `Pr(>|t|)` = numeric(0)
  )
  
  # prep model result dfs - points remaining
  points_r_results <- tibble(
    case = character(0),
    time = numeric(0),
    Estimate = numeric(0),
    `Std. Error` = numeric(0),
    `t value` = numeric(0),
    `Pr(>|t|)` = numeric(0)
  )

  
  print(step)
  
  # filter to only the necessary timepoint
  time_step_df <- brain_behave_lme_df %>%
    filter(move_time == step)
  
  # fit the model with random effects of subject and electrode
  model_all <- summary(robustlmm::rlmer(theta ~ distance_to_ghost + points_remaining + (1|subject/elec_id), data = time_step_df))
  
  # calculate p value by getting dfs from satteraite approximated dfs
  model_dfs <- summary(lmerTest::lmer(theta ~ distance_to_ghost + points_remaining + (1|subject/elec_id), data = time_step_df))
  coefs <- data.frame(coef(model_dfs))
  coefs.robust <- coef(model_all)
  p.values <- 2*pt(abs(coefs.robust[, "t value"]), coefs$df, lower=FALSE)
  
  # add to results - distance
  dist_to_g_results <- rbind(dist_to_g_results, 
                             tibble(
                               case = "all_subs",
                               time = step, 
                               Estimate = model_all$coefficients[2, "Estimate"],
                               `Std. Error` = model_all$coefficients[2, "Std. Error"],
                               `t value` = model_all$coefficients[2, "t value"],
                               `Pr(>|t|)` = p.values[2]
                             ))
  
  # add to results - points remaining
  points_r_results <- rbind(points_r_results, 
                            tibble(
                              case = "all_subs",
                              time = step, 
                              Estimate = model_all$coefficients[3, "Estimate"],
                              `Std. Error` = model_all$coefficients[3, "Std. Error"],
                              `t value` = model_all$coefficients[3, "t value"],
                              `Pr(>|t|)` = p.values[3]
                            ))
  
  # now loop by subject to get the subject specific estimates by subject
  for(elec in unique(time_step_df$elec_id)){
    
    # put into a try statement for subjects that run out of time points
    try({
      
      model_sub <- summary(MASS::rlm(theta ~ distance_to_ghost + points_remaining, data = time_step_df %>% filter(elec_id == elec)))
      
      # calculate p value by getting dfs from satteraite approximated dfs
      coefs.robust <- coef(model_sub)
      p.values <- 2*pt(abs(coefs.robust[, "t value"]), model_sub$df[2], lower=FALSE)
      
      dist_to_g_results <- rbind(dist_to_g_results, 
                                 tibble(
                                   case = elec,
                                   time = step, 
                                   Estimate = model_sub$coefficients[2, "Value"],
                                   `Std. Error` = model_sub$coefficients[2, "Std. Error"],
                                   `t value` = model_sub$coefficients[2, "t value"],
                                   `Pr(>|t|)` = p.values[2]
                                 ))
      
      # add to results
      points_r_results <- rbind(points_r_results, 
                                tibble(
                                  case = elec,
                                  time = step, 
                                  Estimate = model_sub$coefficients[3, "Value"],
                                  `Std. Error` = model_sub$coefficients[3, "Std. Error"],
                                  `t value` = model_sub$coefficients[3, "t value"],
                                  `Pr(>|t|)` = p.values[3]
                                )) 
    }, TRUE)
  }
  
  return(list(dist_to_g_results_step = dist_to_g_results, points_r_results_step = points_r_results))
}
  
save(results, file = path(here(), "results", "cor_analysis", "ofc_theta_lme_results.Rdata"))

points_r_results <- bind_rows(results[, "points_r_results_step"])
dist_to_g_results <- bind_rows(results[, "dist_to_g_results_step"])


```

```{r}

time_step_df <- brain_behave_lme_df %>%
  filter(move_time == .5)

# fit the model with random effects of subject and electrode
model_all <- robustlmm::rlmer(theta ~ distance_to_ghost + points_remaining + distance_to_ghost*points_remaining + (1|subject), data = time_step_df)

model_all_log <- robustlmm::rlmer(log(theta) ~ distance_to_ghost + points_remaining + distance_to_ghost*points_remaining + (1|subject/elec_id), data = time_step_df)
model_all_log_scale <- robustlmm::rlmer(scale(log(theta)) ~ distance_to_ghost + points_remaining + distance_to_ghost*points_remaining + (1|subject/elec_id), data = time_step_df)

model_all_scale <- robustlmm::rlmer(scale(theta) ~ distance_to_ghost + points_remaining + distance_to_ghost*points_remaining + (1|subject/elec_id), data = time_step_df)
  
model_not_robst <- lmer(log(theta) ~ distance_to_ghost + points_remaining + distance_to_ghost*points_remaining + (1|subject), data = time_step_df)

plot(model_all)

summary(MASS::rlm(theta ~ distance_to_ghost + points_remaining, 
                  data = time_step_df %>% filter(elec_id == "LL12_ROF1-ROF2")))

shapiro.test(resid(model_all))

```


```{r}

time_step_df %>%
  ggplot(., aes(y = theta, x = distance_to_ghost, color = subject)) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  theme(panel.background = element_rect(fill = "white")) +
  facet_wrap(~elec_id, scales = "free")


```



```{r, fig.height = 10, fig.width=10}

distance_df <- all_subs_g_dist
brain_df <-ofc_theta_data
  
# merge behavior data with ieeg data
brain_behave_df <- left_join(distance_df %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                                 brain_df %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
brain_behave_lme_df <- brain_behave_df %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # exclude time before they started moving, may be good to look at not doing this as well
  filter(Direction != "Still") %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  # shift the time so that time 0 is the start of movement onset
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  # filter time so that trials end when the person turnaround for the final time
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  mutate(turnaround_time = if_else(event == 1, move_time, 0)) %>%
  filter(move_time < max(turnaround_time)) %>%
  ungroup() %>%
  # filter to max time 3 since after 3s we start losing a lot of trials
  filter(move_time < 3) %>%
  # select and rescale the necessary variables for the model
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, distance_to_ghost)  %>%
  mutate(points_remaining = rescale(points_remaining)) %>%
  mutate(distance_to_ghost = rescale(distance_to_ghost)) #%>%
  # logtransform theta
  # mutate(theta = log(theta))
 
brain_behave_lme_df %>%
  filter(move_time == .5) %>%
  ggplot(., aes(x = theta)) +
  geom_histogram(binwidth = .5) +
  facet_wrap(~elec_id)

brain_behave_lme_df %>%
  filter(move_time == .5) %>%
  ggplot(., aes(x = log(theta))) +
  geom_histogram(binwidth = .5) +
  facet_wrap(~elec_id)


brain_behave_lme_df %>%
  filter(move_time == .5) %>%
  ggplot(., aes(x = distance_to_ghost, y = theta)) +
  geom_point() +
  geom_smooth(method = "lm") 

brain_behave_lme_df %>%
  filter(move_time == .5) %>%
  ggplot(., aes(x = distance_to_ghost, y = theta)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~subject)

time_step_df <- brain_behave_lme_df %>%
  filter(move_time == .5) 


unrobest.model <- lmerTest::lmer(theta ~ distance_to_ghost + points_remaining + (1|subject/elec_id), data = time_step_df)

# fit the robust equivalent
model <- robustlmm::rlmer(theta ~ distance_to_ghost + points_remaining + (1|subject/elec_id), data = time_step_df)

# get coefficients from non-robust model to extract Satterthwaite approximated DFs
coefs <- data.frame(coef(summary(unrobest.model)))

# get coefficients from robust model to extract t-values
coefs.robust <- coef(summary(model))

# calculate p-values based on robust t-values and non-robust approx. DFs
p.values <- 2*pt(abs(coefs.robust[,3]), coefs$df, lower=FALSE)
p.values      
plot(model)  
summary(model)

hist(resid(model), main="Histogram of Residuals", col="lightblue", border="black")

ks.test(resid(model), "pnorm", mean(resid(model)), sd(resid(model)))

nortest::ad.test(resid(model))

# Additional Q-Q plot
qqnorm(resid(model))
qqline(resid(model))


N <- nrow(getME(model, "X"))
# p: Number of fixed effect parameters
p <- length(fixef(model))
# Degrees of freedom for fixed effects
df_fixed <- N - p
# t-values for fixed effects
t_value <- coef(summary(model))[, "t value"]
# Calculate p-values for fixed effects
p_value_fixed <- 2 * (1 - pt(abs(t_value), df = df_fixed))

```

## Turnaround


```{r onset-before-turn}


# OFC and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_turnaround_model_and_plot("OFC", "theta", 
                                all_subs_g_dist, ofc_theta_data, 
                                y_low = -8, y_high = 8,
                                plot_title = "Theta encodes reward and threat values in the OFC at turnaround",
                                rerun_model = TRUE)

# OFC and Theta Onset Before Turnaround plot
individual_and_overall_lme_onset_turnaround_model_and_plot("OFC", "theta", 
                                all_subs_g_dist, ofc_theta_data, 
                                plot_title = "Theta does not encode reward and threat values in the OFC at turnaround",
                                y_low = -8, y_high = 8,
                                rerun_model = FALSE)


```



## Combined value

```{r value-model}

# merge behavior data with ieeg data
ofc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ofc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
ofc_theta_lme_df <- ofc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, distance_to_ghost)  %>%
  rowwise() %>%
  mutate(combined_value = points_remaining * distance_to_ghost) %>%
  ungroup() %>%
  mutate(combined_value = rescale(combined_value))


value_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(ofc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- ofc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ combined_value + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  value_results_only <- rbind(value_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_value <- value_results_only %>% mutate(move_time = sort(unique(ofc_theta_lme_df$move_time)))
                       

plot <- model_results_value %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#D1B5F4") +
  geom_line(color = "#D1B5F4") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 1.1) +
  ggtitle("OFC Theta, Combined Value")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "ofc_theta_trial_combined_value.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```

## Combined value - before turn

```{r value-model}

# merge behavior data with ieeg data
ofc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ofc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
ofc_theta_lme_df <- ofc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  mutate(turnaround_time = if_else(event == 1, move_time, 0)) %>%
  filter(move_time < max(turnaround_time)) %>%
  ungroup() %>%
  filter(move_time < 3) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, distance_to_ghost)  %>%
  rowwise() %>%
  mutate(combined_value = points_remaining * distance_to_ghost) %>%
  ungroup() %>%
  mutate(combined_value = rescale(combined_value))


value_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(ofc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- ofc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ combined_value + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  value_results_only <- rbind(value_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_value <- value_results_only %>% mutate(move_time = sort(unique(ofc_theta_lme_df$move_time)))
                       

plot <- model_results_value %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#D1B5F4") +
  geom_line(color = "#D1B5F4") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3)  +
  ggtitle("OFC Theta, Combined Value")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "ofc_theta_trial_combined_value_preturn.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```

## Discounted Reward

```{r value-model}

# merge behavior data with ieeg data
ofc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ofc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
ofc_theta_lme_df <- ofc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  mutate(turnaround_time = if_else(event == 1, move_time, 0)) %>%
  filter(move_time < max(turnaround_time)) %>%
  ungroup() %>%
  filter(move_time < 3) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, cdf_distance, points_remaining, distance_to_ghost)  %>%
  rowwise() %>%
  mutate(combined_value = points_remaining * cdf_distance) %>%
  ungroup() %>%
  mutate(combined_value = rescale(combined_value))


value_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(ofc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- ofc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ cdf_distance + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  value_results_only <- rbind(value_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_value <- value_results_only %>% mutate(move_time = sort(unique(ofc_theta_lme_df$move_time)))
                       

plot <- model_results_value %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#FB9A99") +
  geom_line(color = "#FB9A99") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3)  + ylim(-1.5, 1.5) +
  ggtitle("OFC Theta, CDF Threat")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "ofc_theta_trial_combined_value_preturn.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```

## UserLocation

```{r value-model}

# merge behavior data with ieeg data
ofc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ofc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
ofc_theta_lme_df <- ofc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, points_remaining, UserLocation)  %>%
  mutate(UserLocation = rescale(UserLocation))


userloc_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(ofc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- ofc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ UserLocation + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  userloc_results_only <- rbind(userloc_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models}

model_results_userloc <- userloc_results_only %>% mutate(move_time = sort(unique(ofc_theta_lme_df$move_time)))
                       

plot <- model_results_userloc %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#65ADC1") +
  geom_line(color = "#65ADC1") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 1) +
  ggtitle("OFC Theta, Pacman Location")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "ofc_theta_trial_pacman_location.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```

## Ghost Location

```{r value-model}

# merge behavior data with ieeg data
ofc_theta_behave_df <- left_join(all_subs_g_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ofc_theta_data %>% mutate(trial_time = round(trial_time, 2)))


# prep for linear mixed effects models #
ofc_theta_lme_df <- ofc_theta_behave_df %>%
  mutate(trial_time = round(trial_time, 2)) %>%
  filter(Direction != "Still") %>%
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  group_by(elec_id, trial_numeric, subject) %>%
  mutate(move_time = round(trial_time - first(trial_time), 2)) %>%
  ungroup() %>%
  filter(move_time < 5) %>%
  select(subject, elec_id, theta, trial_numeric, move_time, distance_to_ghost, GhostLocation)  %>%
  mutate(GhostLocation = rescale(GhostLocation)) %>%
  mutate(distance_to_ghost = rescale(distance_to_ghost))


ghostloc_results_only <- tibble(
  Estimate = numeric(0),
  `Std. Error` = numeric(0),
  df = numeric(0),
  `t value` = numeric(0),
  `Pr(>|t|)` = numeric(0)
)


for(step in sort(unique(ofc_theta_lme_df$move_time))){
  
  print(step)

  time_step_df <- ofc_theta_lme_df %>%
    filter(move_time == step)
  
  model_1 <- summary(lmer(theta ~ GhostLocation  + (1|subject/elec_id), data = time_step_df))
  
    # add to results
  ghostloc_results_only <- rbind(ghostloc_results_only, 
                           tibble(
                             Estimate = model_1$coefficients[2, "Estimate"],
                             `Std. Error` = model_1$coefficients[2, "Std. Error"],
                             df = model_1$coefficients[2, "df"],
                             `t value` = model_1$coefficients[2, "t value"],
                             `Pr(>|t|)` = model_1$coefficients[2, "Pr(>|t|)"]
                           ))

}




```

```{r viz-models, fig.height=8, fig.width=12}

model_results_ghostloc <- ghostloc_results_only %>% mutate(move_time = sort(unique(ofc_theta_lme_df$move_time)))
                       

plot <- model_results_ghostloc %>%
  mutate(sig = if_else(`Pr(>|t|)` < .05, "Sig", "Not Sig.")) %>%
  ggplot(., aes(x = move_time, y = Estimate)) +
  geom_point(aes(color = sig), size = 6, shape = 21, fill = "#EF7474") +
  geom_line(color = "#EF7474") +
  theme(panel.background = element_rect(fill = "white"), legend.position = "top") +
  scale_color_manual(values = c("white", "black")) +
  xlim(0, 3.5) +ylim(-1, 1) +
  ggtitle("OFC Theta, Ghost Location")


ggsave(path(here(), "figures", "linear_mixed_effect_models", "ofc_theta_trial_ghost_location.png"),
       plot = plot,
       width = 12,
       height = 8,
       units = "in",
       dpi = 300)


```


```{r save}

write_csv(model_results_whole_trial, path(here(), "results", "ofc_model_results_whole_trial.csv"))
write_csv(model_results, path(here(), "results", "ofc_model_results_turnarouns.csv"))
write_csv(model_results_value, path(here(), "results", "ofc_model_results_integrated_value.csv"))


```
