---
title: "All ROI HFA Ghost Attack"
output: html_document
date: "2024-10-29"
---

```{r setup, include=FALSE}
## libraries ##
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(lmtest)
library(blme)
library(scales)
library(ggthemr)
library(RColorBrewer)
library(broom.mixed)
library(brms)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))
source(path(here(), "R", 'separate_mfg_sfg.R'))

## plotting helpers ##
ggthemr("light")
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

```


## Testing for elevated theta power during approach compared to avoidance

This script tests for elevated theta power during approach in the hippocampus, amygdala, OFC, ACC, Insula, MFG, & SFG in both conflict and no-conflict trials. The window of interest is from 1.5 seconds before turning until 1.5 seconds after turning. I average this window within trials, electrodes, and subjects and then compare the approach vs avoiding sections using the following equation:

lmer(trial_theta ~ aac + (1 + aac|subject), data = aac_df)

I tried to first use:

lmer(trial_theta ~ aac + (1 + aac|subject/elec_id), data = aac_df)

But this resulted in singular fits for the no conflict trials. Removing the random slope drastically changed the degrees of freedom and a model with slopes was significantly better than a model without slopes as assessed by an anova.

Meanwhile, removing the nested random effect of electrode did not change the fixed effects estimate hardly at all, and there was no sig difference when I compared the models via anova. The effects in the conflict trials also hold if I include the nested effect of electrode.

Therefore, I believe the best model to assess the affecr of approaching vs avoiding (`aac`) is the one without the nested random effect of electrode, but with a random intercept and slope for subject. I will use this model for all the analyses.



```{r load-data}

## Gamma ##
# ieeg limbic data #
# cing_gamma_data <- read_csv( path(here(), "munge", "gamma_ieeg_cing_all_subs_logged_iti_onset.csv"))
# ofc_gamma_data <- read_csv( path(here(), "munge", "gamma_ieeg_ofc_all_subs_logged_iti_onset.csv"))
# amyg_gamma_data <- read_csv( path(here(), "munge", "gamma_ieeg_amyg_all_subs_logged_iti_onset.csv"))
# hc_gamma_data <- read_csv( path(here(), "munge", "gamma_ieeg_hc_all_subs_logged_iti_onset.csv"))
# insula_gamma_data <- read_csv( path(here(), "munge", "gamma_ieeg_insula_all_subs_logged_iti_onset.csv"))
# dlpfc_gamma_data <- read_csv( path(here(), "munge", "gamma_ieeg_dlpfc_all_subs_logged_iti_onset.csv"))
# 
# # separate dlpfc into sfg and mfg
# dlpfc_gamma_data <- dlpfc_gamma_data %>%
#   mutate(electrode = gsub("_.*", "", electrode))
# dlpfc_gamma_data <- separate_mfg_sfg(dlpfc_gamma_data)
# sfg_gamma_data <- dlpfc_gamma_data %>% filter(sfg == 1) %>% select(-sfg, -mfg)
# mfg_gamma_data <- dlpfc_gamma_data %>% filter(mfg == 1) %>% select(-sfg, -mfg)


## HFA ##
# ieeg limbic data #
cing_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_cing_all_subs_logged_iti_onset.csv"))
ofc_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_ofc_all_subs_logged_iti_onset.csv"))
amyg_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_amyg_all_subs_logged_iti_onset.csv"))
hc_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_hc_all_subs_logged_iti_onset.csv"))
insula_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_insula_all_subs_logged_iti_onset.csv"))
dlpfc_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_dlpfc_all_subs_logged_iti_onset.csv"))

# separate dlpfc into sfg and mfg
dlpfc_hfa_data <- dlpfc_hfa_data %>%
  mutate(electrode = gsub("_.*", "", electrode))
dlpfc_hfa_data <- separate_mfg_sfg(dlpfc_hfa_data)
sfg_hfa_data <- dlpfc_hfa_data %>% filter(sfg == 1) %>% select(-sfg, -mfg)
mfg_hfa_data <- dlpfc_hfa_data %>% filter(mfg == 1) %>% select(-sfg, -mfg)


# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))


# add ITI to behavioral df
behavior_iti_df <- all_subs_g_dist %>% 
  select(subject, trial_numeric, trial_time) %>%
  filter(trial_time < 1) %>%
  mutate(trial_time = round(trial_time - 1, 2))

all_subs_dist <- full_join(all_subs_g_dist, behavior_iti_df)


```

```{r merge-ieeg-hfa-data-behave-data}

# prep hfa data #
cing_data <- cing_hfa_data %>% 
  mutate(freq = "hfa") %>%
  mutate(region = "Ant. Cingulate") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

ofc_data <- ofc_hfa_data %>% 
  mutate(freq = "hfa") %>%
  mutate(region = "OFC") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

hc_data <- hc_hfa_data %>% 
  mutate(freq = "hfa") %>%
  mutate(region = "Hippocampus") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

amyg_data <- amyg_hfa_data %>% 
  mutate(freq = "hfa") %>%
  mutate(region = "Amygdala") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

insula_data <- insula_hfa_data %>% 
  mutate(freq = "hfa") %>%
  mutate(region = "Insula") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))


mfg_data <- mfg_hfa_data %>%
  mutate(freq = "hfa") %>%
  mutate(region = "MFG") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

# bind ieeg data #
ieeg_hfa_data <- bind_rows(cing_data, ofc_data, hc_data, amyg_data, insula_data, mfg_data)

# crop time 
ieeg_hfa_data <- ieeg_hfa_data %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)


# bind with behavioral data #
ieeg_hfa_behave_df <- inner_join(all_subs_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ieeg_hfa_data %>% mutate(trial_time = round(trial_time, 2)))

```


```{r read-in-attack-tables}

## load and compile attack tables ##
for(sub in unique(all_subs_dist$subject)){
  
  tmp <- read_csv(path(here(), "data", "ieeg_behave", paste0(sub, "_attack_events.csv")))
  tmp <- tmp %>%
    mutate(subject = sub)
  
  if(exists("attack_events")){
    attack_events <- bind_rows(attack_events, tmp)
  } else {
    attack_events <- tmp
  }
  
}

## modify to get trials of interest ##
attack_events <- attack_events %>%
  mutate(trial_numeric = neural_trial_numeric + 1) %>%
  mutate(attacks_ids = paste0(subject, "_", trial_numeric))


```


```{r shift-to-attack}

# merge attack df
ieeg_attack_hfa_df <- left_join(ieeg_hfa_behave_df, attack_events %>% rename(attack_begin = event) %>% select(subject, trial_numeric, sample, attack_begin))
ieeg_attack_hfa_df <- ieeg_attack_hfa_df %>%
  mutate(attack_begin = if_else(is.na(attack_begin), 0, 1)) %>%
  group_by(subject, trial_numeric) %>%
  mutate(attacked = if_else(sum(attack_begin) != 0, 1, 0)) %>%
  ungroup()

# shift to center around turnaround  #
attack_hfa_centered_df <- ieeg_attack_hfa_df %>%
  filter(attacked == 1) %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  # shift the time so that time 0 is the start of movement onset
  group_by(elec_id, trial_numeric, subject, freq, region) %>%
  # filter time so that trials end when the person turnaround for the final time
  mutate(attack_time = if_else(attack_begin == 1, trial_time, 0)) %>%
  mutate(attack_time = max(attack_time)) %>%
  mutate(time = trial_time - attack_time) %>%
  ungroup() 



```

```{r sig-test-df-prep-function}


create_sig_test_df <- function(behave_df){


  # filter between 1.5 before and after turn, and create approach, avoid condition, average across trial
  attack_df <- behave_df %>%
    mutate(time = round(time, 2)) %>%
    filter(time <= 1 & time >= -1) %>%
    mutate(attack = if_else(time <=0, "Pre-Attack", "Post-Attack")) %>%
    group_by(elec_id, attack, trial_numeric) %>%
    mutate(trial_hfa = mean(power)) %>%
    select(trial_hfa, elec_id, trial_numeric, subject, attack) %>%
    distinct()  
  
  # run model with rnadom effects of subject and electrode  
  model_tmp <- summary(lmer(trial_hfa ~ attack + (1 + attack|subject), data = attack_df))
  pval <- model_tmp$coefficients[2, 5]
  
  
  # Create visualization df, by averaging, across electrode, and subject
  acc_df <- attack_df %>%
    mutate(pvalue = pval) 
    
  return(acc_df)
  
}


```

```{r plot-mfg, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
mfg_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "MFG"))


# # create plot
# mfg_plot <- plot_pre_post_attack(mfg_attack_plot_df, "MFG")
# 
# # print plot
# mfg_plot
# 
# # save plot
# ggsave(path(here(), "figures", "figure6_mfg_attack_hfa_plot.png"), plot = mfg_plot, width = 5.5, height = 3)

```

### Left/Right Differences


```{r}

# load MNI data
mni_data <- read_csv(path(here(), "munge", "mni_coordinates_all_subs.csv"))

# separate out the bipolar pairs
mfg_attack_plot_df <- mfg_attack_plot_df %>%
  mutate(electrode = gsub(paste0(subject, "_"), "", elec_id)) %>%
  mutate(first_elec = gsub("-.*", "", electrode)) %>%
  mutate(second_elec = gsub(".*-", "", electrode)) 

attack_hfa_centered_df <- attack_hfa_centered_df %>%
  mutate(first_elec = gsub("-.*", "", electrode)) %>%
  mutate(second_elec = gsub(".*-", "", electrode))   

# merge with anatomy
leftright_data <- mni_data %>%
  mutate(left_right = if_else(X <= 0, "Left", "Right")) %>%
  select(subject, left_right, Electrode)

mfg_attack_plot_df <- left_join(mfg_attack_plot_df, leftright_data, by = c("subject" = "subject", "first_elec" = "Electrode"))
attack_hfa_centered_df <- left_join(attack_hfa_centered_df, leftright_data, by = c("subject" = "subject", "first_elec" = "Electrode"))


```


```{r plot-mfg, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
mfgr_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "MFG" & left_right == "Right"))


# # create plot
# mfgr_plot <- plot_pre_post_attack(mfgr_attack_plot_df, "Right MFG")
# 
# # print plot
# mfgr_plot
# 
# # save plot
# ggsave(path(here(), "figures", "figure6_rmfg_attack_hfa_plot.png"), plot = mfgr_plot, width = 5.5, height = 3)

```

```{r brms-hc}

library(brms)

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


# Fit the model
mfg_lr_model <- brm(
  formula = trial_hfa ~ attack*left_right + (1 + attack | subject/elec_id),
  data = mfg_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(mfg_lr_model)

# save full model #
save(mfg_lr_model, file = path(here(), "results", "attack_mfg_lr_hfa_model_brms.RData"))
load(path(here(), "results", "attack_mfg_lr_hfa_model_brms.RData"))
summary(mfg_lr_model)
```





```{r plotting-functions}

plot_pre_post_attack <- function(attack_test_df, roi) {
  
  
 attack_elec_test_df <- attack_test_df %>%
    group_by(elec_id, attack) %>%
    mutate(elec_hfa = mean(trial_hfa)) %>%
    select(-trial_hfa, -trial_numeric) %>%
    distinct()
 
 
attack_sub_test_df <-  attack_elec_test_df %>%
    group_by(subject, attack) %>%
    mutate(sub_hfa = mean(elec_hfa)) %>%
    select(-elec_hfa, -elec_id) %>%
    distinct() %>%
    mutate(attack = factor(attack, levels = c("Pre-Attack", "Post-Attack")))

pval_df <- attack_sub_test_df %>%
    ungroup() %>%
    select(pvalue) %>%
    distinct() %>%
    mutate(pvalue = if_else(pvalue < .05, sprintf("p = %.2g***", pvalue), sprintf("p = %.2g", pvalue)))
  
  attack_plot <- attack_sub_test_df %>%
    ggplot(.) +
    geom_boxplot(aes(x = attack, y = sub_hfa, fill = attack), color = "#2D2327") +
    geom_jitter(aes(x = attack, fill = attack, y = sub_hfa), color = "#2D2327", width = .1, size = 2, shape = 17) +
    geom_line(aes(x = attack, y = sub_hfa, group = subject), size = .5, alpha = .5, color = "#2D2327") +
    geom_jitter(data = attack_elec_test_df, aes(x = attack, fill = attack, y = elec_hfa), width = .1, size = 2, alpha = .5, shape = 21, color = "#2D2327") +
    theme(panel.background = element_rect(fill = "white")) +
    scale_fill_manual(values = c("#2c75b3", "#c2383a")) +
    scale_color_manual(values = c("#2c75b3", "#c2383a")) +
    ggsignif::geom_signif(data = pval_df, manual = T, aes(y_position=c(2), xmin= c(1), xmax = c(2), annotations = pvalue),
                family = "Gill Sans", color = "#2D2327", textsize = 5, vjust =-.5) +
    theme(panel.background = element_rect(fill = "white"), 
          legend.position = "none",
          axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 16),
          axis.title = element_text(family = "Gill Sans", color = "#2D2327", size = 17),
          legend.title = element_text(family = "Gill Sans", color = "#2D2327", size = 18),
          legend.text  = element_text(family = "Gill Sans", color = "#2D2327", size = 17),
          strip.text = element_text(family = "Gill Sans", color = "#2D2327", size = 17),
          plot.subtitle = element_text(family = "Gill Sans", color = "#2D2327", size = 17),
          plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 19, hjust = .5)) +
    labs(y = "Average hfa power (a.u.)", x = "", fill = "", color = "") +
    ggtitle(roi) 
  
  return(attack_plot)

}


```
```{r brms-version}

library(brms)

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


# Fit the model
hc_model <- brm(
  formula = trial_theta ~ aac + (1 + aac | subject/elec_id),
  data = hc_conflict_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(hc_model)

# save full model #
save(hc_model, file = path(here(), "results", "app_avd_hc_theta_model_brms.RData"))
```

## Conflict Trials

## Hippocampus


```{r plot-both-hc, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
hc_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "Hippocampus"))


# create plot
hc_plot <- plot_pre_post_attack(hc_attack_plot_df, "Hippocampus")

# print plot
hc_plot

# save plot
ggsave(path(here(), "figures", "figure6_hc_attack_hfa_plot.png"), plot = hc_plot, width = 5.5, height = 3)

```

```{r brms-hc}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


# Fit the model
hc_model <- brm(
  formula = trial_hfa ~ attack + (1 + attack | subject/elec_id),
  data = hc_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(hc_model)

# save full model #
save(hc_model, file = path(here(), "results", "attack_hc_hfa_model_brms.RData"))

```

## Amygdala

```{r plot-amyg, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
amyg_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "Amygdala"))


# create plot
amyg_plot <- plot_pre_post_attack(amyg_attack_plot_df, "Amygdala")

# print plot
amyg_plot

# save plot
ggsave(path(here(), "figures", "figure6_amyg_attack_hfa_plot.png"), plot = amyg_plot, width = 5.5, height = 3)

```

## OFC

```{r plot-ofc, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
ofc_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "OFC"))


# create plot
ofc_plot <- plot_pre_post_attack(ofc_attack_plot_df, "OFC")

# print plot
ofc_plot

# save plot
ggsave(path(here(), "figures", "figure6_ofc_attack_hfa_plot.png"), plot = ofc_plot, width = 5.5, height = 3)

```


## Anterior Cingulate

```{r plot-cing, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
cing_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "Ant. Cingulate"))


# create plot
cing_plot <- plot_pre_post_attack(cing_attack_plot_df, "Ant. Cingulate")

# print plot
cing_plot

# save plot
ggsave(path(here(), "figures", "figure6_cing_attack_hfa_plot.png"), plot = cing_plot, width = 5.5, height = 3)

```


## Insula

```{r plot-insula, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
insula_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "Insula"))


# create plot
insula_plot <- plot_pre_post_attack(insula_attack_plot_df, "Insula")

# print plot
insula_plot

# save plot
ggsave(path(here(), "figures", "figure6_insula_attack_hfa_plot.png"), plot = insula_plot, width = 5.5, height = 3)

```

## MFG

```{r plot-mfg, fig.width = 8, fig.height = 7, warning = F}


# create df for conflict, no conflict trials
mfg_attack_plot_df <- create_sig_test_df(attack_hfa_centered_df %>% filter(region == "MFG"))


# create plot
mfg_plot <- plot_pre_post_attack(mfg_attack_plot_df, "MFG")

# print plot
mfg_plot

# save plot
ggsave(path(here(), "figures", "figure6_mfg_attack_hfa_plot.png"), plot = mfg_plot, width = 5.5, height = 3)

```

```{r brms-hc}

# Fit the model
mfg_model <- brm(
  formula = trial_hfa ~ attack + (1 + attack | subject/elec_id),
  data = mfg_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(mfg_model)

# save full model #
save(mfg_model, file = path(here(), "results", "attack_mfg_hfa_model_brms.RData"))


load(path(here(), "results", "attack_mfg_hfa_model_brms.RData"))

```


```{r random-effects}
library(posterior)

# pull random efftcs
subject_random_effects <- ranef(mfg_model, groups = "subject")

# Extract posterior samples of random effects
posterior_ranef_subject <- as_draws_df(mfg_model) %>%
  select(starts_with("r_subject["))

posterior_ranef_electrode <- as_draws_df(mfg_model) %>%
  select(starts_with("r_subject:elec_id["))

# Extract posterior samples of the fixed effect
posterior_fixed <- as_draws_df(mfg_model, variable = "b_attackPreMAttack")

# Get the list of subjects
subjects <- unique(mfg_model$data$subject)

# Initialize a list to store subject-specific effect samples
subject_effects <- list()

# Loop over each subject
for (subject in subjects) {
  # Create the variable name for the random effect
  ranef_var <- paste0("r_subject[", subject, ",attackPreMAttack]")
  
  # Check if the variable exists in the posterior samples
  if (ranef_var %in% names(posterior_ranef_subject)) {
    ranef_samples <- posterior_ranef_subject[[ranef_var]]
  } else {
    stop(paste("Random effect variable", ranef_var, "not found in posterior samples."))
  }
  
  # Combine fixed and random effects
  subject_specific_samples <- posterior_fixed$b_attackPreMAttack + ranef_samples
  
  # Store the samples
  subject_effects[[as.character(subject)]] <- subject_specific_samples
}

```


```{r, subject-ci}

# Initialize a data frame to store the results
subject_ci <- data.frame(
  subject = character(),
  mean = numeric(),
  lower = numeric(),
  upper = numeric(),
  significant = logical(),
  stringsAsFactors = FALSE
)

for (subject in names(subject_effects)) {
  # Get the samples
  samples <- subject_effects[[subject]]
  
  # Calculate mean and credible intervals
  mean_effect <- mean(samples)
  ci_lower <- quantile(samples, probs = 0.025)
  ci_upper <- quantile(samples, probs = 0.975)
  
  # Determine if CI includes zero
  significant <- ci_lower > 0 | ci_upper < 0
  
  # Add to the data frame
  subject_ci <- rbind(subject_ci, data.frame(
    subject = subject,
    mean = mean_effect,
    lower = ci_lower,
    upper = ci_upper,
    significant = significant,
    stringsAsFactors = FALSE
  ))
}


```


```{r elec-ranef}

# Extract unique combinations of subject and elec_id from the model data
electrode_info <- unique(mfg_model$data[, c("subject", "elec_id")])

# Create a unique identifier for electrodes (subject_elec_id)
electrode_info$subject_elec_id <- paste0(electrode_info$subject, "_", electrode_info$elec_id)

# Initialize a list to store electrode-specific effect samples
electrode_effects <- list()

# Loop over each electrode
for (i in 1:nrow(electrode_info)) {
  subject <- electrode_info$subject[i]
  elec_id <- electrode_info$elec_id[i]
  subject_elec_id <- electrode_info$subject_elec_id[i]
  
  # Create variable names for random effects
  ranef_subject_var <- paste0("r_subject[", subject, ",attackPreMAttack]")
  ranef_electrode_var <- paste0("r_subject:elec_id[", subject_elec_id, ",attackPreMAttack]")
  
  # Check if variables exist in the posterior samples
  if (ranef_subject_var %in% names(posterior_ranef_subject)) {
    ranef_subject_samples <- posterior_ranef_subject[[ranef_subject_var]]
  } else {
    stop(paste("Random effect variable", ranef_subject_var, "not found in posterior samples."))
  }
  
  if (ranef_electrode_var %in% names(posterior_ranef_electrode)) {
    ranef_electrode_samples <- posterior_ranef_electrode[[ranef_electrode_var]]
  } else {
    stop(paste("Random effect variable", ranef_electrode_var, "not found in posterior samples."))
  }
  
  # Combine fixed effect, subject random effect, and electrode random effect
  electrode_specific_samples <- posterior_fixed$b_attackPreMAttack + ranef_subject_samples + ranef_electrode_samples
  
  # Store the samples
  electrode_effects[[subject_elec_id]] <- electrode_specific_samples
}


```

```{r elec-ci}

# Initialize a data frame to store the results
electrode_ci <-  data.frame(
  subject_elec_id = character(),
  subject = character(),
  elec_id = character(),
  mean = numeric(),
  lower = numeric(),
  upper = numeric(),
  significant = logical(),
  stringsAsFactors = FALSE
)

for (subject_elec_id in names(electrode_effects)) {
  # Get the samples
  samples <- electrode_effects[[subject_elec_id]]
  
  # Calculate mean and credible intervals
  mean_effect <- mean(samples)
  ci_lower <- quantile(samples, probs = 0.025)
  ci_upper <- quantile(samples, probs = 0.975)
  
  # Determine if CI includes zero
  significant <- ci_lower > 0 | ci_upper < 0
  
  # Extract subject and elec_id from subject_elec_id
  parts <- strsplit(subject_elec_id, "_")[[1]]
  subject <- parts[1]
  elec_id <- parts[2]
  
  # Add to data frame
  electrode_ci <- rbind(electrode_ci, data.frame(
    subject_elec_id = subject_elec_id,
    subject = subject,
    elec_id = elec_id,
    mean = mean_effect,
    lower = ci_lower,
    upper = ci_upper,
    significant = significant,
    stringsAsFactors = FALSE
  ))
}

electrode_ci <- electrode_ci %>%
  rowwise() %>%
  mutate(subject_names = paste0(subject, "_", subject, "_")) %>%
  mutate(electrode = gsub(subject_names, "", subject_elec_id)) %>%
  select(-subject_names, -elec_id) %>%
  mutate(first_elec = gsub("-.*", "", electrode)) %>%
  mutate(second_elec = gsub(".*-", "", electrode)) %>%
  mutate(big_attack_effect = if_else(significant, "yes", "no"))

write_csv(electrode_ci, path(here(), "munge", "sig_electrodes_ci_mfg_attack_diff.csv"))

electrode_ci <- read_csv(path(here(), "munge", "sig_electrodes_ci_mfg_attack_diff.csv"))
```
```{r}

# load MNI data
mni_data <- read_csv(path(here(), "munge", "mni_coordinates_all_subs.csv"))

# merge with anatomy
leftright_data <- mni_data %>%
  mutate(left_right = if_else(X <= 0, "Left", "Right")) %>%
  select(subject, left_right, Electrode)

electrode_ci <- left_join(electrode_ci, leftright_data, by = c("subject" = "subject", "first_elec" = "Electrode"))

table(electrode_ci$left_right, electrode_ci$big_attack_effect)

```


