---
title: "Attack Chase Death"
output: html_document
date: "2024-10-29"
---

```{r setup, include=FALSE}
## libraries ##
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(lmtest)
library(blme)
library(scales)
library(ggthemr)
library(RColorBrewer)
library(broom.mixed)
library(brms)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))
source(path(here(), "R", 'separate_mfg_sfg.R'))

## plotting helpers ##
ggthemr("light")
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

```


## Testing for elevated theta power during approach compared to avoidance

This script tests for elevated theta power during approach in the hippocampus, amygdala, OFC, ACC, Insula, MFG, & SFG in both conflict and no-conflict trials. The window of interest is from 1.5 seconds before turning until 1.5 seconds after turning. I average this window within trials, electrodes, and subjects and then compare the approach vs avoiding sections using the following equation:

lmer(trial_theta ~ aac + (1 + aac|subject), data = aac_df)

I tried to first use:

lmer(trial_theta ~ aac + (1 + aac|subject/elec_id), data = aac_df)

But this resulted in singular fits for the no conflict trials. Removing the random slope drastically changed the degrees of freedom and a model with slopes was significantly better than a model without slopes as assessed by an anova.

Meanwhile, removing the nested random effect of electrode did not change the fixed effects estimate hardly at all, and there was no sig difference when I compared the models via anova. The effects in the conflict trials also hold if I include the nested effect of electrode.

Therefore, I believe the best model to assess the affecr of approaching vs avoiding (`aac`) is the one without the nested random effect of electrode, but with a random intercept and slope for subject. I will use this model for all the analyses.



```{r load-data}

## HFA ##
dlpfc_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_dlpfc_all_subs_logged_iti_onset.csv"))

# separate dlpfc into sfg and mfg
dlpfc_hfa_data <- dlpfc_hfa_data %>%
  mutate(electrode = gsub("_.*", "", electrode))
dlpfc_hfa_data <- separate_mfg_sfg(dlpfc_hfa_data)
sfg_hfa_data <- dlpfc_hfa_data %>% filter(sfg == 1) %>% select(-sfg, -mfg)
mfg_hfa_data <- dlpfc_hfa_data %>% filter(mfg == 1) %>% select(-sfg, -mfg)


# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))


# add ITI to behavioral df
behavior_iti_df <- all_subs_g_dist %>% 
  select(subject, trial_numeric, trial_time) %>%
  filter(trial_time < 1) %>%
  mutate(trial_time = round(trial_time - 1, 2))

all_subs_dist <- full_join(all_subs_g_dist, behavior_iti_df)


```


```{r}

# load MNI data
mni_data <- read_csv(path(here(), "munge", "mni_coordinates_all_subs.csv"))

# create left/right pairs
leftright_data <- mni_data %>%
  mutate(left_right = if_else(X <= 0, "Left", "Right")) %>%
  select(subject, left_right, Electrode)


```


```{r merge-ieeg-hfa-data-behave-data}

mfg_hfa_clean_data <- mfg_hfa_data %>%
  mutate(freq = "hfa") %>%
  mutate(region = "MFG") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  mutate(first_elec = gsub("-.*", "", electrode)) %>%
  mutate(second_elec = gsub(".*-", "", electrode))  %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)


# merge with anatomy
mfg_hfa_clean_data <- left_join(mfg_hfa_clean_data, leftright_data, by = c("subject" = "subject", "first_elec" = "Electrode"))

# bind with behavioral data #
mfg_hfa_behave_df <- inner_join(all_subs_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               mfg_hfa_clean_data %>% mutate(trial_time = round(trial_time, 2)))

# right only
mfgr_hfa_behave_df <- mfg_hfa_behave_df %>%
  filter(left_right == "Right")

```


```{r read-in-attack-tables}

## load and compile attack tables ##
for(sub in unique(all_subs_dist$subject)){
  
  tmp <- read_csv(path(here(), "data", "ieeg_behave", paste0(sub, "_attack_events.csv")))
  tmp <- tmp %>%
    mutate(subject = sub)
  
  if(exists("attack_events")){
    attack_events <- bind_rows(attack_events, tmp)
  } else {
    attack_events <- tmp
  }
  
}

## modify to get trials of interest ##
attack_events <- attack_events %>%
  mutate(trial_numeric = neural_trial_numeric + 1) %>%
  mutate(attacks_ids = paste0(subject, "_", trial_numeric))

attatck_events_coutn <- attack_events %>%
  filter(subject != "LL14" & subject != "BJH016")

mean(table(attatck_events_coutn$subject))
sd(table(attatck_events_coutn$subject))


```


```{r shift-to-attack}

# merge attack df
mfgr_attack_hfa_df <- left_join(mfgr_hfa_behave_df, attack_events %>% rename(attack_begin = event) %>% select(subject, trial_numeric, sample, attack_begin))
mfgr_attack_hfa_df <- mfgr_attack_hfa_df %>%
  mutate(attack_begin = if_else(is.na(attack_begin), 0, 1)) %>%
  group_by(subject, trial_numeric) %>%
  mutate(attacked = if_else(sum(attack_begin) != 0, 1, 0)) %>%
  ungroup()

# shift to center around turnaround  #
hfa_end_centered_df <- mfgr_attack_hfa_df %>%
  filter(attacked == 1) %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  # shift the time so that time 0 is the start of trial end
  group_by(elec_id, trial_numeric, subject, freq, region) %>%
  mutate(attack_time = if_else(attack_begin == 1, trial_time, -999)) %>%
  mutate(attack_time = max(attack_time)) %>%
  filter(attack_time > 0) %>%
  mutate(end_time = trial_time - trial_length) %>%
  mutate(end_time = round(end_time, 2)) %>%
  filter(trial_time >= attack_time -.5) %>%
  ungroup() 

behavior_check <- hfa_end_centered_df %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died) %>%
  distinct()

```



```{r plot-chase, fig.height = 6, fig.width = 8}


chase_df <- hfa_end_centered_df %>%
  group_by(subject, trial_numeric) %>%
  mutate(chase_trial = any(Chase)) %>%
  filter(chase_trial == T & died == 0) %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died, chase_trial, elec_id, power) %>%
  rowwise() %>%
  mutate(attack_length = trial_length - attack_time) %>%
  mutate(attack_end_time = -1* attack_length) %>%
  arrange(desc(attack_length)) %>%
  mutate(elec_trial_id = factor(paste0(elec_id, "_", trial_numeric)))


chase_df %>%
  ggplot(.,aes (x = end_time, y = elec_trial_id, color = power)) +
  geom_tile(aes(fill = power)) +
  geom_text(aes(x = attack_end_time), label = "*", size = 4, color = "white") +
  theme_minimal() +
  scale_fill_viridis_b(limits = c(-3, 3), oob = scales::squish, option = "C") +
  scale_color_viridis_b(limits = c(-3, 3), oob = scales::squish, option = "C")  +
  theme(panel.background = element_rect(fill = "white"), axis.text.y = element_blank()) 
  


```


```{r plot-chase, fig.height = 5, fig.width =6}


died_df <- hfa_end_centered_df %>%
  group_by(subject, trial_numeric) %>%
  mutate(chase_trial = any(Chase)) %>%
  filter(died == 1 & chase_trial == F) %>%
  mutate(min_time = max(end_time)) %>%
  filter(min_time == 0) %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died, elec_id, power, min_time) %>%
  rowwise() %>%
  mutate(attack_length = trial_length - attack_time) %>%
  mutate(attack_end_time = -1* attack_length) %>%
  arrange(desc(attack_length)) %>%
  mutate(elec_trial_id = factor(paste0(elec_id, "_", trial_numeric)))


died_df %>%
  ggplot(.,aes (x = end_time, y = elec_trial_id, color = power)) +
  geom_tile(aes(fill = power)) +
  geom_text(aes(x = attack_end_time), label = "*", size = 4, color = "white") +
  theme_minimal() +
  scale_fill_viridis_b(limits = c(-5, 5), oob = scales::squish, option = "C") +
  scale_color_viridis_b(limits = c(-5, 5), oob = scales::squish, option = "C")  +
  theme(panel.background = element_rect(fill = "white"), axis.text.y = element_blank()) 
  


```

```{r, fig.height = 5, fig.width =10}

chase_died_df <- bind_rows(chase_df %>% mutate(case = "Chase trial"),
                           died_df %>% mutate(case = "Strike trial"))

chase_died_plot <- chase_died_df %>%
  ggplot(.,aes (x = end_time, y = elec_trial_id, color = power)) +
  geom_tile(aes(fill = power)) +
  geom_text(aes(x = attack_end_time), label = "*", size = 4, color = "white") +
  theme_minimal() +
  scale_fill_viridis_b(limits = c(-3, 3), oob = scales::squish, option = "C") +
  scale_color_viridis_b(limits = c(-3, 3), oob = scales::squish, option = "C")  +
  labs(x = "Time (s), locked to trial end", y = "rMFG Electrode and Trial stacks", fill = "Power (z)", color = "Power (z)") +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "right",
        panel.grid =  element_blank(),
        axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
        axis.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
        axis.text.y = element_blank(),
        legend.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
        legend.text  = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
        strip.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8, face = 'bold'),
        plot.subtitle = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
        plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8, face = 'bold')) + 
  facet_wrap(~case, nrow = 1, scales = "free") +
  ggtitle("")

ggsave(path(here(), "figures", "attack", "figure6_chase_death_rmfg_plot.png"), 
       plot = chase_died_plot, 
       width = 4.1, height = 3, units = "in", dpi = 600)

```


```{r}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


attack_duration_df <- hfa_end_centered_df %>%
  group_by(subject, trial_numeric) %>%
  filter(trial_time >= attack_time) %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died, elec_id, distance_to_ghost, power) %>%
  rowwise() %>%
  mutate(attack_length = trial_length - attack_time) %>%
  mutate(attack_end_time = -1* attack_length) %>%
  ungroup() %>%
  arrange(desc(attack_length)) %>%
  mutate(elec_trial_id = factor(paste0(elec_id, "_", trial_numeric))) %>%
  mutate(distance_to_ghost_scaled = scale(distance_to_ghost)[,1])


# Fit the model
attack_hfa_model <- brm(
  formula = power ~ distance_to_ghost_scaled + (1 + distance_to_ghost_scaled | subject/elec_id),
  data = attack_duration_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(attack_hfa_model)

# save full model #
save(attack_hfa_model, file = path(here(), "results", "attack_hc_hfa_trial_level_model_brms.RData"))


```



```{r}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores())

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


attack_duration_df <- hfa_end_centered_df %>%
  group_by(subject, trial_numeric) %>%
  filter(trial_time >= attack_time) %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died, elec_id, distance_to_ghost, power) %>%
  rowwise() %>%
  mutate(attack_length = trial_length - attack_time) %>%
  mutate(attack_end_time = -1* attack_length) %>%
  ungroup() %>%
  arrange(desc(attack_length)) %>%
  mutate(elec_trial_id = factor(paste0(elec_id, "_", trial_numeric))) %>%
  mutate(distance_to_ghost_scaled = scale(distance_to_ghost)[,1]) %>%
  mutate(died = if_else(died == 1, "attack", "chase"))


# Fit the model
attack_died_hfa_model <- brm(
  formula = power ~ died*end_time + (1 + end_time | subject/elec_id),
  data = attack_duration_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


summary(attack_died_hfa_model)

# save full model #
save(attack_died_hfa_model, file = path(here(), "results", "attack_hc_hfa_trial_time_model_brms.RData"))


```
