---
title: "Theta Ghost Attack"
output: html_document
date: "2024-10-30"
---

```{r setup, include=FALSE}
## libraries ##
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(lmtest)
library(blme)
library(scales)
library(ggthemr)
library(RColorBrewer)
library(broom.mixed)
library(brms)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))
source(path(here(), "R", 'separate_mfg_sfg.R'))

## plotting helpers ##
ggthemr("light")
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

```

# Pre vs Post Turn Theta Drop

In our previous analyses, we found that theta is elevated during approach compared to avoidance in the limbic regions, but not the MFG. This was found in conflict trials (with a ghost), but attack-free trials (ghost stayed in its "bob" pattern). Here we test whether theta still drops post turn, when turning to avoid is driven by the onset of a ghost attack.

```{r load-data}


## theta ##
# ieeg limbic data #
cing_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_cing_all_subs_logged_iti_onset.csv"))
ofc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_ofc_all_subs_logged_iti_onset.csv"))
amyg_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_amyg_all_subs_logged_iti_onset.csv"))
hc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_hc_all_subs_logged_iti_onset.csv"))
dlpfc_theta_data <- read_csv( path(here(), "munge", "theta_ieeg_dlpfc_all_subs_logged_iti_onset.csv"))

# separate dlpfc into sfg and mfg
dlpfc_theta_data <- dlpfc_theta_data %>%
  mutate(electrode = gsub("_.*", "", electrode))
dlpfc_theta_data <- separate_mfg_sfg(dlpfc_theta_data)
sfg_theta_data <- dlpfc_theta_data %>% filter(sfg == 1) %>% select(-sfg, -mfg)
mfg_theta_data <- dlpfc_theta_data %>% filter(mfg == 1) %>% select(-sfg, -mfg)


# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))


# add ITI to behavioral df
behavior_iti_df <- all_subs_g_dist %>% 
  select(subject, trial_numeric, trial_time) %>%
  filter(trial_time < 1) %>%
  mutate(trial_time = round(trial_time - 1, 2))

all_subs_dist <- full_join(all_subs_g_dist, behavior_iti_df)


```

```{r merge-ieeg-theta-data-behave-data}

# prep theta data #
cing_data <- cing_theta_data %>% 
  mutate(freq = "theta") %>%
  mutate(region = "Ant. Cingulate") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

ofc_data <- ofc_theta_data %>% 
  mutate(freq = "theta") %>%
  mutate(region = "OFC") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

hc_data <- hc_theta_data %>% 
  mutate(freq = "theta") %>%
  mutate(region = "Hippocampus") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

amyg_data <- amyg_theta_data %>% 
  mutate(freq = "theta") %>%
  mutate(region = "Amygdala") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

mfg_data <- mfg_theta_data %>%
  mutate(freq = "theta") %>%
  mutate(region = "MFG") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode))

# bind ieeg data #
ieeg_theta_data <- bind_rows(cing_data, ofc_data, hc_data, amyg_data, mfg_data)

# crop time 
ieeg_theta_data <- ieeg_theta_data %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)


# bind with behavioral data #
ieeg_theta_behave_df <- inner_join(all_subs_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               ieeg_theta_data %>% mutate(trial_time = round(trial_time, 2)))

```


```{r read-in-attack-tables}

## load and compile attack tables ##
for(sub in unique(all_subs_dist$subject)){
  
  tmp <- read_csv(path(here(), "data", "ieeg_behave", paste0(sub, "_attack_events.csv")))
  tmp <- tmp %>%
    mutate(subject = sub)
  
  if(exists("attack_events")){
    attack_events <- bind_rows(attack_events, tmp)
  } else {
    attack_events <- tmp
  }
  
}

## modify to get trials of interest ##
attack_events <- attack_events %>%
  mutate(trial_numeric = neural_trial_numeric + 1) %>%
  mutate(attacks_ids = paste0(subject, "_", trial_numeric))


```


```{r shift-to-attack}

# merge attack df
ieeg_attack_theta_df <- left_join(ieeg_theta_behave_df, attack_events %>% rename(attack_begin = event) %>% select(subject, trial_numeric, sample, attack_begin))
ieeg_attack_theta_df <- ieeg_attack_theta_df %>%
  mutate(attack_begin = if_else(is.na(attack_begin), 0, 1)) %>%
  group_by(subject, trial_numeric) %>%
  mutate(attacked = if_else(sum(attack_begin) != 0, 1, 0)) %>%
  ungroup()

# shift to center around turnaround  #
attack_theta_turn_centered_df <- ieeg_attack_theta_df %>%
  filter(attacked == 1) %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  # shift the time so that time 0 is the start of movement onset
  group_by(elec_id, trial_numeric, subject, freq, region) %>%
  mutate(event = if_else(last_away == away_choice & away_choice != 0, 1, 0)) %>%
  mutate(event = replace(event, is.na(event), 0)) %>%
  # filter time so that time 0 is when the person turnaround for the final time
  mutate(turnaround_time = if_else(event == 1, trial_time, 0)) %>%
  mutate(turnaround_time = max(turnaround_time)) %>%
  filter(turnaround_time != 0) %>%
  mutate(time = trial_time - turnaround_time) %>%
  ungroup() 



```

```{r sig-test-df-prep-function}


create_attack_df <- function(behave_df){

  # filter between 1.5 before and after turn, and create approach, avoid condition, average across trial
  attack_df <- behave_df %>%
    mutate(time = round(time, 2)) %>%
    filter(time <= 1.5 & time >= -1.5) %>%
    mutate(attack = if_else(time <=0, "Pre-Turn", "Post-Turn")) %>%
    group_by(elec_id, attack, trial_numeric) %>%
    mutate(trial_theta = mean(power)) %>%
    select(trial_theta, elec_id, trial_numeric, subject, attack) %>%
    distinct()  
    
  return(attack_df)
  
}

create_attack_died_df <- function(behave_df){

  # filter between 1.5 before and after turn, and create approach, avoid condition, average across trial
  attack_df <- behave_df %>%
    mutate(time = round(time, 2)) %>%
    filter(time <= 1.5 & time >= -1.5) %>%
    mutate(attack = if_else(time <=0, "Pre-Turn", "Post-Turn")) %>%
    group_by(elec_id, attack, trial_numeric, died) %>%
    mutate(trial_theta = mean(power)) %>%
    select(trial_theta, elec_id, trial_numeric, subject, attack, died) %>%
    distinct()  
    
  return(attack_df)
  
}


```


```{r create-roi-attack-dfs}

# create df for turn during attack
hc_attack_plot_df <- create_attack_df(attack_theta_turn_centered_df %>% filter(region == "Hippocampus"))
amyg_attack_plot_df <- create_attack_df(attack_theta_turn_centered_df %>% filter(region == "Amygdala"))
ofc_attack_plot_df <- create_attack_df(attack_theta_turn_centered_df %>% filter(region == "OFC"))
cing_attack_plot_df <- create_attack_df(attack_theta_turn_centered_df %>% filter(region == "Ant. Cingulate"))
mfg_attack_plot_df <- create_attack_df(attack_theta_turn_centered_df %>% filter(region == "MFG"))

# create df for turn during attack, by chase or strike
hc_attack_death_plot_df <- create_attack_died_df(attack_theta_turn_centered_df %>% filter(region == "Hippocampus"))
amyg_attack_death_plot_df <- create_attack_died_df(attack_theta_turn_centered_df %>% filter(region == "Amygdala"))
ofc_attack_death_plot_df <- create_attack_died_df(attack_theta_turn_centered_df %>% filter(region == "OFC"))
cing_attack_death_plot_df <- create_attack_died_df(attack_theta_turn_centered_df %>% filter(region == "Ant. Cingulate"))
mfg_attack_death_plot_df <- create_attack_died_df(attack_theta_turn_centered_df %>% filter(region == "MFG"))



```

## Attack Models

```{r brms-attack}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores(), 
        brms.backend = "cmdstanr"  # Use cmdstanr backend for better performance
)

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)

## Hippocampus
# Fit the model
hc_model <- brm(
  formula = trial_theta ~ attack + (1 + attack | subject/elec_id),
  data = hc_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(hc_model)
# save full model #
save(hc_model, file = path(here(), "results", "attack_hc_theta_model_brms.RData"))

## Amygdala
# Fit the model
amyg_model <- brm(
  formula = trial_theta ~ attack + (1 + attack | subject/elec_id),
  data = amyg_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(amyg_model)
# save full model #
save(amyg_model, file = path(here(), "results", "attack_amyg_theta_model_brms.RData"))

## OFC
# Fit the model
ofc_model <- brm(
  formula = trial_theta ~ attack + (1 + attack | subject/elec_id),
  data = ofc_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(ofc_model)
# save full model #
save(ofc_model, file = path(here(), "results", "attack_ofc_theta_model_brms.RData"))

## ACC
# Fit the model
cing_model <- brm(
  formula = trial_theta ~ attack + (1 + attack | subject/elec_id),
  data = cing_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(cing_model)
# save full model #
save(cing_model, file = path(here(), "results", "attack_cing_theta_model_brms.RData"))


## MFG
# Fit the model
mfg_model <- brm(
  formula = trial_theta ~ attack + (1 + attack | subject/elec_id),
  data = mfg_attack_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(mfg_model)
# save full model #
save(mfg_model, file = path(here(), "results", "attack_mfg_theta_model_brms.RData"))


```

```{r brms-attack-died}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores(), 
        brms.backend = "cmdstanr"  # Use cmdstanr backend for better performance
)

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)

## Hippocampus
# Fit the model
hc_died_model <- brm(
  formula = trial_theta ~ attack*died + (1 + attack + died | subject/elec_id),
  data = hc_attack_death_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(hc_died_model)
# save full model #
save(hc_died_model, file = path(here(), "results", "attack_died_hc_theta_model_brms.RData"))

## Amygdala
# Fit the model
amyg_died_model <- brm(
  formula = trial_theta ~ attack*died + (1 + attack*died  | subject/elec_id),
  data = amyg_attack_death_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(amyg_died_model)
# save full model #
save(amyg_died_model, file = path(here(), "results", "attack_died_amyg_theta_model_brms.RData"))

## OFC
# Fit the model
ofc_died_model <- brm(
  formula = trial_theta ~ attack*died + (1 + attack*died  | subject/elec_id),
  data = ofc_attack_death_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(ofc_died_model)
# save full model #
save(ofc_died_model, file = path(here(), "results", "attack_died_ofc_theta_model_brms.RData"))

## ACC
# Fit the model
cing_died_model <- brm(
  formula = trial_theta ~ attack*died + (1 + attack + died  | subject/elec_id),
  data = cing_attack_death_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(cing_died_model)
# save full model #
save(cing_died_model, file = path(here(), "results", "attack_died_cing_theta_model_brms.RData"))


## MFG
# Fit the model
mfg_died_model <- brm(
  formula = trial_theta ~ attack*died + (1 + attack*died  | subject/elec_id),
  data = mfg_attack_death_plot_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)

summary(mfg_died_model)
# save full model #
save(mfg_died_model, file = path(here(), "results", "attack_died_mfg_theta_model_brms.RData"))


```

```{r}

amyg_attack_time <- attack_theta_turn_centered_df %>% 
  filter(region == "Amygdala") %>%
  filter(time >= 0) %>%
  select(subject, elec_id, died, time, region, power) %>%
  distinct()

amyg_time_model <- brm(
  formula = power ~ time*died + (1 + time*died  | subject/elec_id),
  data = amyg_attack_time,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


save(amyg_time_model, file = path(here(), "results", "attack_time_amyg_theta_model_brms.RData"))

```

```{r}

# Hippocampus (simple model is best)
died_model <- loo(hc_died_model)
attack_model <- loo(hc_model)
loo_compare(attack_model, died_model)


# Amygdala (no difference)
died_model <- loo(amyg_died_model)
attack_model <- loo(amyg_model)
loo_compare(died_model, attack_model)

# OFC ( simple model is wayyy better)
died_model <- loo(ofc_died_model)
attack_model <- loo(ofc_model)
loo_compare(died_model, attack_model)

# ACC (no difference)
died_model <- loo(cing_died_model)
attack_model <- loo(cing_model)
loo_compare(died_model, attack_model)

# MFG (no difference)
died_model <- loo(mfg_died_model)
attack_model <- loo(mfg_model)
loo_compare(died_model, attack_model)



```



```{r}


## MFG
load(path(here(), "results", "attack_mfg_theta_model_brms.RData"))
lower_ci <- summary(mfg_model)$fixed[2, 3]
upper_ci <- summary(mfg_model)$fixed[2, 4]
mfg_attack_plot_df <- mfg_attack_plot_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## HC
load(path(here(), "results", "attack_hc_theta_model_brms.RData"))
lower_ci <- summary(hc_model)$fixed[2, 3]
upper_ci <- summary(hc_model)$fixed[2, 4]
hc_attack_plot_df <- hc_attack_plot_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## Amygdala
load(path(here(), "results", "attack_amyg_theta_model_brms.RData"))
lower_ci <- summary(amyg_model)$fixed[2, 3]
upper_ci <- summary(amyg_model)$fixed[2, 4]
amyg_attack_plot_df <- amyg_attack_plot_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## OFC
load(path(here(), "results", "attack_ofc_theta_model_brms.RData"))
lower_ci <- summary(ofc_model)$fixed[2, 3]
upper_ci <- summary(ofc_model)$fixed[2, 4]
ofc_attack_plot_df <- ofc_attack_plot_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))

## CING
load(path(here(), "results", "attack_cing_theta_model_brms.RData"))
lower_ci <- summary(cing_model)$fixed[2, 3]
upper_ci <- summary(cing_model)$fixed[2, 4]
cing_attack_plot_df <- cing_attack_plot_df %>%
  mutate(pvalue = if_else(lower_ci <= 0 & upper_ci >= 0,  "n.s.", "***"))


```


### Plot Attack Theta Power


```{r plotting-functions}

plot_pre_post_attack <- function(attack_test_df, roi) {
  
  
 attack_elec_test_df <- attack_test_df %>%
    group_by(elec_id, attack) %>%
    mutate(elec_theta = mean(trial_theta)) %>%
    select(-trial_theta, -trial_numeric) %>%
    distinct()%>%
    mutate(attack = factor(attack, levels = c("Pre-Turn", "Post-Turn"), labels =  c("Pre-\nTurn", "Post-\nTurn")))

 
 
  attack_sub_test_df <-  attack_elec_test_df %>%
      group_by(subject, attack) %>%
      mutate(sub_theta = mean(elec_theta)) %>%
      select(-elec_theta, -elec_id) %>%
      distinct() 
  
  pval_df <- attack_sub_test_df %>%
      ungroup() %>%
      select(pvalue) %>%
      distinct() 
    
    attack_plot <- attack_sub_test_df %>%
      ggplot(.) +
      geom_jitter(data = attack_elec_test_df, aes(x = attack, fill = attack, y = elec_theta), width = .3, size = .75, alpha = .5, shape = 21, color = "#2D2327") +
      geom_boxplot(aes(x = attack, y = sub_theta, fill = attack), color = "#2D2327", outlier.size = .5) +
      geom_jitter(aes(x = attack, fill = attack, y = sub_theta), color = "#2D2327", alpha = .9, width = .1, size = 1, shape = 17) +
      geom_line(aes(x = attack, y = sub_theta, group = subject), size = .25, alpha = .9, width = .1, color = "#2D2327") +
      theme(panel.background = element_rect(fill = "white")) +
      scale_fill_manual(values = c("#2c75b3", "#c2383a")) +
      scale_color_manual(values = c("#2c75b3", "#c2383a")) +
      ggsignif::geom_signif(data = pval_df, manual = T, aes(y_position=c(1.8), xmin= c(1), xmax = c(2), annotations = pvalue),
                  family = "Gill Sans", color = "#2D2327", textsize = 3, vjust =-.5) +
      theme(panel.background = element_rect(fill = "white"), 
            legend.position = "none",
            axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8.5),
            axis.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8.5),
            plot.subtitle = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
            plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8.5, hjust = .5)) +
      labs(y = "Average theta power (z - score)", x = "", fill = "", color = "") +
      ggtitle(roi) +
      ylim(-2, 2)
  
  return(attack_plot)

}


```



## Amygdala

```{r plot-amyg, fig.width = 2, fig.height = 2.7, warning = F}

# create plot
amyg_plot <- plot_pre_post_attack(amyg_attack_plot_df, "Amygdala")

# print plot
amyg_plot

# save plot
ggsave(path(here(), "figures", "attack", "figure6_amyg_attack_theta_plot.png"), plot = amyg_plot, width = 2, height = 2.7)

```

## Hippocampus

```{r plot-both-hc, fig.width = 2, fig.height = 2.7, warning = F}


# create plot
hc_plot <- plot_pre_post_attack(hc_attack_plot_df, "Hippocampus\nAttack Trials")

# print plot
hc_plot

# save plot
ggsave(path(here(), "figures", "attack", "figure6_hc_attack_theta_plot.png"), plot = hc_plot, width = 1.5, height = 2.7)

```

## OFC

```{r plot-ofc, fig.width = 2, fig.height = 2.7, warning = F}

# create plot
ofc_plot <- plot_pre_post_attack(ofc_attack_plot_df, "OFC\nAttack Trials")

# print plot
ofc_plot

# save plot
ggsave(path(here(), "figures", "attack", "figure6_ofc_attack_theta_plot.png"), plot = ofc_plot, width = 1.5, height = 2.7)

```


## Anterior Cingulate

```{r plot-cing, fig.width = 2, fig.height = 2.7, warning = F}

# create plot
cing_plot <- plot_pre_post_attack(cing_attack_plot_df, "Ant. Cingulate")

# print plot
cing_plot

# save plot
ggsave(path(here(), "figures", "attack", "figure6_cing_attack_theta_plot.png"), plot = cing_plot, width = 2, height = 2.7)

```


## MFG

```{r plot-mfg, fig.width = 2, fig.height = 2.7, warning = F}

# create plot
mfg_plot <- plot_pre_post_attack(mfg_attack_plot_df, "MFG")

# print plot
mfg_plot

# save plot
ggsave(path(here(), "figures", "attack", "figure6_mfg_attack_theta_plot.png"), plot = mfg_plot, width = 2, height = 2.7)

```

